### 2019-12-17 project-report.tex
Initial Overleaf Import

\documentclass{article}
\usepackage[utf8]{inputenc}

\title{SynthStackSearch}
\author{Amir Salimi}
\date{December 2019}

\usepackage{float}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{todonotes}
\usepackage{etoolbox}

\begin{document}
\maketitle

\section{Introduction}
\subsection{Purpose of this document}
The purpose of this document is to give a summary of what has been done for this project so far and what needs to be done in the future. Also, to facilitate setting of milestones for what should be done before the up-coming NIME paper deadline; taking into account Dr.Hindle's purported exile on Janurary 1st. The bulk of the paper should be done within the next 2-3 weeks and the focus should be on improvements from then on. 
\subsection{Purpose of project}
The purpose of this project is to synthetically generate high-quality and novel one-shot drum samples of various categories. Each category of drum being defined by example; using numerous pre-recorded drum samples as a reference for the common characteristics of the group.

\subsection{Motivation: Why is this project useful?}
\todo[inline]{Beyond personal reasons, literature review is needed to provide a good response to this question}

\subsection{Dataset}
We have thousands of royalty free (but not public domain) short (under 1 sec) samples organized into different categories. Most of these categories are drums (kicks, snares, hats, shakers, etc). But there are non-drum categories such as short piano and guitar samples as well. The main sources for our dataset are:
\begin{itemize}
    \item personal library: not share-able
    \item Music Radar royalty free packs automatically downloaded, chopped up (if appropriate) and separated into different groups (see the "getting\_data" section of the project code for scripts, written in shell). The data is not share-able but the scripts are.
    \item  sampleswap.org: a source for 8 gigabytes of public domain sounds. Can be downloaded entirely for 30 bucks and shared freely thereafter\todo[]{(Not used yet)}
\end{itemize}

\todo[inline, color=green!40]{Note: While royalty free audio is not necessarily legal to share, the corresponding image spectrums are}

\section{Implementation}
\subsection{Design}
Towards our goal of generating original audio, we assumed that there are at least 2 major components needed:
\begin{itemize}
    \item A flexible, deterministic, and tractable generator which can create audio
    \item An ear that returns an evaluation of an audio sample; used to determine whether the audio sample fulfills the requirements. 
\end{itemize}

These components are designed with modularity and parallelizability in mind. This allows each component to be debugged, modified and improved without affecting the other components. More importantly, greatly increasing the ease of scalability and speed of experiments.
The major and minor components as well as the code that glues the project together will be discussed further in this document. 
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{images/SSS_gen.png}
\caption{Generation Pipeline}
\label{fig:SSS generator}
\end{figure}

\subsection{The Generator}
We used the python based Pippi library for our generator implementation\footnote{https://github.com/luvsound/pippi}. This library uses a C back-end and focuses on fast offline generation. We define a Synth as the smallest unit of sound generation. A single Synth can be fairly expressive on its own, but we also allow a combination of Synths, which we call a Synth Stack. Each Synth takes in multiple parameters (parameter-set) and generates a sound. If the stack size is larger than 1, the combination of these individual parameter-sets is treated as the parameter-set for the stack.

\subsection{The Ear}
The most challenging and important component of the project; the ear can be any method of evaluating a piece of audio. The most basic representation of a piece of digital audio is via list of numbers and a sampling-rate. For simplicity, we fix the sampling rate to 41,000 per second across all components of this project. An array representation of audio is the representation of the audio within the time domain. More commonly, the frequency domain is used for MIR tasks.
\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{images/SSS_ear.png}
\caption{Evaluation Using the Ear}
\label{fig:SSS generator}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=0.5\textwidth]{images/specplot.png}
\caption{Mel-spectrum representation of a randomly generated sample}
\label{fig:SSS generator}
\end{figure}
All we require from the ear is to give us probabilities of an audio sample belonging to various sound (drum and none-drum) categories. It should be self-evident that these probabilities should sum up to 1.\\

We have implemented several methods of feature extraction thus far and successfully separated different drum categories in interesting ways, visualized in the "interactive\_separation\_graph.ipynb" notebook. A common pitfall of most feature extraction methods implemented is that they do not consider the temporal trends within the audio, making them highly susceptible to errors when evaluating audio that should not belong to any of the categories.\\
\todo[inline, color=green!40]{
Sanity Check: If a drum sample is reversed or chopped up, its likelihood of being labeled the same should change.}

There are two interconnected temporal trends to consider: 
\begin{itemize}
    \item Change in amplitude within each frequency bin. Harder to measure and utilize and possibly not as important for our purposes, considering the short length of our samples.
    \item Overall amplitude change within a sample. Closely linked to ADSR. 
\end{itemize}{}

Temporal trends are can be deduced from a spectrum representation of sound (at least visually by a human). A convolution net trained on our drum dataset led to an ear good enough to continue to the next stage of the project. The current model does an adequate job of rejecting junk data and semi-robustly rejects samples with inappropriate wave-shapes,\todo[color=red!40]{but leaves much room for improvements}.
\begin{figure}[H]
\centering
\includegraphics[width=0.8\linewidth]{images/cnn_ear.png}
\caption{CNN ear working well on a test set}
\label{fig:ok ear}
\end{figure}

\subsection{Generator+Ear}
Once we have a generator and an ear, we can quickly generate a large dataset where each data item is a random parameter-set, the ear score of the parameter-set and the corresponding rankings for each category. The rankings are derived from the probability scores. For example, the category with the highest probability will have the rank of 1, second highest would rank 2nd, and the lowest probability will have the rank of n (assuming n categories).\\
Important to highlight is that thus far we have only used 1 Synth to generate our sounds, but our generator has the capability to use larger Synth Stacks, and the pipelines are written with that possibility in mind.\\
\todo[inline]{A seen in Figure \ref{fig:rank portions}, there is a bias in random generation towards making higher ranking hats and kicks and lower ranking shakers, claps. Is this bias because of Synth structure or a problem with the ear?}
\begin{figure}[h!]
\centering
\includegraphics[width=1\linewidth]{images/random_ranks.png}
\caption{Figure showing proportions of categorical ranks for around 50,000 randomly generated sounds. Only showing ranks 1-5. About 90\% received the rank of 1 (blue portion of the bar) for the "synth" category, meaning that the ear correctly gave the highest probability to the sound being from a synth combination. We are interested in the small percentages of random generations that trick the ear due to coincidentally being similar to actual drums (i.e those who received a rank of 1) }
\todo[inline, color=green!30]{When looking for the best sounds of each category, could use ranks 2 and 3 etc. as well, however:
\unexpanded{\unexpanded{
\begin{itemize}
    \item We must figure out how to penalize their parameters
    \item The task requires even more confidence in ear,
    \item Generation is fast enough that we don't need to use ranks higher than 1. We have more than enough data if we don't want to deal with this task.
\end{itemize} 
}}}

\label{fig:rank portions}
\end{figure}
\section{Novel Generations}
\subsection{Goal}
 Given a category, our aim is to use random generations to guide an algorithm towards novel generation of drums for that category.

\subsection{Guided Generation Attempts}

\subsubsection{Multivariate Normal}
Some success and extremely fast and scalable once the parameter space is calculated. Currently our parameters are array indices mapping to different values for Synth components. This makes the assumption that our discrete parameter space is normally distributed or differentiable in-appropriate and prone to errors. \todo[color=green!40]{provide example as proof. e.g: bimodal parameter}

\subsubsection{Evolutionary Search}
Implemented evolutionary search using DEAP \citep{DEAP_JMLR2012}. A parameter set is assumed to be an individual with each parameter being its genes. To measure an individuals fitness, we use the formula $fitness=score-rank$. As generations evolve, a Hall-of-Fame list with a fixed size tracks the best individuals to ever live in any given generation, updating itself after each batch of off-springs is evaluated.\\
To ensure diversity of the HOF individuals, the fitness score should also consider some measure of uniqueness. A weighted minkowski distance \footnote{https://docs.scipy.org/doc/scipy/reference/generated/scipy.spatial.distance.minkowski.html} between the genes of an offspring and the HOF individuals may be a good measurement.\todo[color=orange!40]{Medium Priority} \\
A generation of $N$ individuals are initialized(randomly or using already existing ranked parameters). To create the offspring generation, each generation goes through mutations and in-place gene crossovers. The new generation consists of the top 80\% of the offspring generation and 20\% new individuals to quicken gene diversity. If the new individuals are coming directly from previously measured high scoring parameter sets, we ensure that they cannot be directly added to HOF without going through mutations and crossovers first.

\section{Priorities}
\subsection{Highest Priorities}
\subsubsection{Lit Review}
Extremely lacking at the moment. A few hours spent on the linguistics research was not very fruitful. Will revisit and further explore papers related to project magenta, WaveGans and adversarial audio generation in the upcoming days. \\
Also necessary is to search for related NIME papers to help with methodology improvements, paper motivation and guiding the writing process.  
\subsubsection{Ear improvements}
Great potential for improvements as well as great benefits for improvements make this the highest priority in terms of programming. A better ear means better generated sounds and more confidence in our measurements.

Relevant tasks:
\begin{itemize}
    \item Proper envelope detection
    \item LSTM ear
    \item Dealing with, and necessity of, a junk/noise class
\end{itemize}
\subsection{Medium Priorities}
\subsubsection{Search Improvements}
Search works but is highly dependent on the ear.\\ 
How well evo search work for each category? How to measure it "working"
\subsubsection{Using Stacks of size larger than 1}
Single stacks are powerful, but larger would be nice. 
\subsubsection{AutoEncoder Networks}
Implement variational auto-encoders for drum generation as an alternative to our method. 
\subsubsection{Generated Drums Survey}
Powered by diffrent music. All we need is good generated drums.
\subsection{Low Priorities}
\subsubsection{SampleSwap}
Sign up
\subsubsection{Notebook Cleanups}
Cleanup notebooks, add them to the report
\bibliographystyle{plain}
\bibliography{references}
\end{document}

### 2019-12-30 Lit_Terms_Suppliments.tex
Updates from Overleaf

\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Terminology and Supplements}
\date{December 2019}
\usepackage{float}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{todonotes}
\usepackage{etoolbox}
\usepackage{csquotes}

\begin{document}
\maketitle
\section{Literature review}
\subsection{Parametric and unit-selective Speech Synthesis \cite{zen2009statistical}}
According this paper:
\blockquote[\cite{zen2009statistical}]{
Statistical parametric synthesis might be most simply described as generating the average of some sets of similarly sounding speech  segments.    This  contrasts  directly  with  the  target  in unit-selection synthesis that retains natural unmodified speech units}
Each method has its own advantages. The quality gap of synthesized speech between these methods is domain dependent.\cite{zen2009statistical}

\cite{esling2018generative}

\subsection{Future tasks and other thoughts}
\subsubsection{Data}
Could drum data retrieval become its own project/paper? Using the field of automatic drum transcription, cutting loops up and other relevant fields. Nsynth \cite{nsynth2017} database doesn't have many percussion sounds as the emphasis is on pitches and notes. 
\section{Terminology and Measurements}

\bibliographystyle{plain}
\bibliography{references}
\end{document}

### 2019-12-30 NIME_PAPER/SSS.tex
Updates from Overleaf

--- 2019-12-17 project-report.tex
@@
-\documentclass{article}
+\documentclass{nime-alternate} % Uncomment when publishing final version
+% Uncomment only one of the ones below
+\usepackage{anonymize} 		   %Uncomment this line to publish
+% \usepackage[blind]{anonymize}%Uncomment this line for blind review
 \usepackage[utf8]{inputenc}
-
-\title{SynthStackSearch}
-\author{Amir Salimi}
-\date{December 2019}
 
@@
 \usepackage{etoolbox}
+\usepackage[inline]{enumitem}
+\begin{document}
 
-\begin{document}
+% --- Author Metadata here. See Template---
+\conferenceinfo{NIME'20,}{July 21-25, 2020, Royal Birmingham Conservatoire, ~~~~~~~~~~~~ Birmingham City University, Birmingham, United Kingdom.}
+\title{SSS}
+
+\label{key}
+\numberofauthors{2} 
+\author{
+\alignauthor
+\anonymize{Amir Salimi}\\
+       \affaddr{\anonymize{Department of Computing Science}}\\
+       \affaddr{\anonymize{University of Alberta}}\\
+       \affaddr{\anonymize{Edmonton,AB,Alberta}}\\
+       \email{\anonymize{asalimi@ualberta.ca}}
+\alignauthor
+\anonymize{Abram Hindle}\\
+       \affaddr{\anonymize{Department of Computing Science}}\\
+       \affaddr{\anonymize{University of Alberta}}\\
+       \affaddr{\anonymize{Edmonton,AB,Alberta}}\\
+       \email{\anonymize{abram.hindle@ualberta.ca}}
+}
+
 \maketitle
 
-\section{Introduction}
-\subsection{Purpose of this document}
-The purpose of this document is to give a summary of what has been done for this project so far and what needs to be done in the future.
-Also, to facilitate setting of milestones for what should be done before the up-coming NIME paper deadline; taking into account Dr.Hindle's purported exile on Janurary 1st.
-The bulk of the paper should be done within the next 2-3 weeks and the focus should be on improvements from then on.
-\subsection{Purpose of project}
-The purpose of this project is to synthetically generate high-quality and novel one-shot drum samples of various categories.
-Each category of drum being defined by example; using numerous pre-recorded drum samples as a reference for the common characteristics of the group.
+\begin{abstract}
+With generation of novel, high quality, one shot percussive sounds as our end goal, we implemented a set of modular software components utilized to form a pipeline for guided generation of sounds.
+The most crucial of these components are a "virtual ear" capable of evaluating generated sounds and an efficient, tractable "virtual synthesizer" capable of generating a wide range of sounds.\\
+We can implement and utilize our components in various ways leading to different outcomes; hence, here first discuss our various methods of implementation, evaluation, and limitation of these components.
+Next, we discuss three methodologies utilized for the creation of percussive sounds and their efficiencies:  \begin {enumerate*} [label=\itshape\alph*\upshape)]
+\item random generation \item multivariate distribution sampling and \item evolutionary search.
+\end {enumerate*} 
+\end{abstract}
 
-\subsection{Motivation: Why is this project useful?}
-\todo[inline]{Beyond personal reasons, literature review is needed to provide a good response to this question}
+\keywords{MIR,drums,generation,search}
 
-\subsection{Dataset}
-We have thousands of royalty free (but not public domain) short (under 1 sec) samples organized into different categories.
-Most of these categories are drums (kicks, snares, hats, shakers, etc).
-But there are non-drum categories such as short piano and guitar samples as well.
-The main sources for our dataset are:
-\begin{itemize}
-    \item personal library: not share-able
-    \item Music Radar royalty free packs automatically downloaded, chopped up (if appropriate) and separated into different groups (see the "getting\_data" section of the project code for scripts, written in shell).
-The data is not share-able but the scripts are.
-    \item  sampleswap.org: a source for 8 gigabytes of public domain sounds. Can be downloaded entirely for 30 bucks and shared freely thereafter\todo[]{(Not used yet)}
-\end{itemize}
-
-\todo[inline, color=green!40]{Note: While royalty free audio is not necessarily legal to share, the corresponding image spectrums are}
+% See template for CCS classification. 
+\ccsdesc[500]{Applied computing~Sound and music computing}
+\ccsdesc[300]{Information systems~Music retrieval}
+\printccsdesc
 
@@
 A convolution net trained on our drum dataset led to an ear good enough to continue to the next stage of the project.
-The current model does an adequate job of rejecting junk data and semi-robustly rejects samples with inappropriate wave-shapes,\todo[color=red!40]{but leaves much room for improvements}.
+The current model does an adequate job of rejecting junk data and semi-robustly rejects samples with inappropriate wave-shapes.
 \begin{figure}[H]
@@
 This makes the assumption that our discrete parameter space is normally distributed or differentiable in-appropriate and prone to errors.
-\todo[color=green!40]{provide example as proof.
-e.g: bimodal parameter}
 
@@
 To ensure diversity of the HOF individuals, the fitness score should also consider some measure of uniqueness.
-A weighted minkowski distance \footnote{https://docs.scipy.org/doc/scipy/reference/generated/scipy.spatial.distance.minkowski.html} between the genes of an offspring and the HOF individuals may be a good measurement.\todo[color=orange!40]{Medium Priority} \\
+A weighted minkowski distance \footnote{https://docs.scipy.org/doc/scipy/reference/generated/scipy.spatial.distance.minkowski.html} between the genes of an offspring and the HOF individuals may be a good measurement.\\
 A generation of $N$ individuals are initialized(randomly or using already existing ranked parameters).
@@
 If the new individuals are coming directly from previously measured high scoring parameter sets, we ensure that they cannot be directly added to HOF without going through mutations and crossovers first.
-
-\section{Priorities}
-\subsection{Highest Priorities}
-\subsubsection{Lit Review}
-Extremely lacking at the moment.
-A few hours spent on the linguistics research was not very fruitful.
-Will revisit and further explore papers related to project magenta, WaveGans and adversarial audio generation in the upcoming days.
-\\
-Also necessary is to search for related NIME papers to help with methodology improvements, paper motivation and guiding the writing process.  
-\subsubsection{Ear improvements}
-Great potential for improvements as well as great benefits for improvements make this the highest priority in terms of programming.
-A better ear means better generated sounds and more confidence in our measurements.
-
-Relevant tasks:
-\begin{itemize}
-    \item Proper envelope detection
-    \item LSTM ear
-    \item Dealing with, and necessity of, a junk/noise class
-\end{itemize}
-\subsection{Medium Priorities}
-\subsubsection{Search Improvements}
-Search works but is highly dependent on the ear.\\ 
-How well evo search work for each category? How to measure it "working"
-\subsubsection{Using Stacks of size larger than 1}
-Single stacks are powerful, but larger would be nice. 
-\subsubsection{AutoEncoder Networks}
-Implement variational auto-encoders for drum generation as an alternative to our method. 
-\subsubsection{Generated Drums Survey}
-Powered by diffrent music. All we need is good generated drums.
-\subsection{Low Priorities}
-\subsubsection{SampleSwap}
-Sign up
-\subsubsection{Notebook Cleanups}
-Cleanup notebooks, add them to the report
-\bibliographystyle{plain}
-\bibliography{references}
 \end{document}

### 2019-12-31 NIME_PAPER/SSS.tex
abstract, half an intro

@@
 \begin{abstract}
-With generation of novel, high quality, one shot percussive sounds as our end goal, we implemented a set of modular software components utilized to form a pipeline for guided generation of sounds.
-The most crucial of these components are a "virtual ear" capable of evaluating generated sounds and an efficient, tractable "virtual synthesizer" capable of generating a wide range of sounds.\\
-We can implement and utilize our components in various ways leading to different outcomes; hence, here first discuss our various methods of implementation, evaluation, and limitation of these components.
-Next, we discuss three methodologies utilized for the creation of percussive sounds and their efficiencies:  \begin {enumerate*} [label=\itshape\alph*\upshape)]
-\item random generation \item multivariate distribution sampling and \item evolutionary search.
+With the generation of novel, high quality, one shot percussive sounds as our end goal, we implemented a set of modular software components utilized to form a pipeline for guided generation of sounds.
+The most crucial of these components are a "virtual ear" capable of evaluating a sounds proximity to different drum types and an efficient, tractable "virtual synthesizer" with a rich set of parameters and DSP methods capable of generating a wide range of sounds.\\
+Following the Unix Philosophy \cite{gancarz2003linux}, we designed our software such that we can utilize our components in various ways leading to different outcomes; hence, in order to established an adequate level of confidence in our components, we discuss the implementation, limitations, and evaluations of the "virtual synthesizer" and "virtual ear".
+Next, we present our findings and assessments in regards to the three different methodologies utilized for the generative process of percussive sounds:  \begin {enumerate*} [label=(\roman*)]
+\item random generation \item multivariate distribution sampling and \item evolutionary search.\\
 \end {enumerate*} 
+Finally, we observed a general lack of copyright-free percussive sample-packs as well as a lack of unified approach for obtaining such a data-set by fellow researchers \cite{aouameur2019neural,ramires2019timbfeat}.
+We aim to ameliorate this issue by presenting a copyright free sample-pack of categorized percussion sounds.
+Furthermore, we have included in our project source code \footnote{\url{https://github.com/imilas/Synths_Stacks_Search}} a set of scripts to further expand the sample pack via royalty free sources.
+\keywords{drum, percussion, synthesis, MIR, ML, genetic, search}
 \end{abstract}
-
-\keywords{MIR,drums,generation,search}
-
 % See template for CCS classification. 
 \ccsdesc[500]{Applied computing~Sound and music computing}
-\ccsdesc[300]{Information systems~Music retrieval}
+\ccsdesc[500]{Information systems~Music retrieval}
 \printccsdesc
 
+\section{Introduction}
+The rise of Digital Audio Workstations (DAW) \cite{leider2004digital} and Virtual Studio Technology (VST) based plug-ins \cite{tanev2013virtual} have rapidly transformed the sonic and material landscape of music production in the recent years.
+Coupled with this rise in popularity is a vast array of commercial products and services dedicated to satiating the need of amateur and professional music producers for unique sounds; most commonly via audio samples: one-shot drum samples, long sustained notes (commonly refered to as pads or textures), percussive or melodic loops etc.
+Two notable examples of these commercial services are \textit{loopmasters}\footnote{loopmasters.com} and \textit{splice.com}\footnote{splice.com}.
+Furthermore VST plug-ins can emulate complex audio synthesizers or effects, which some producers may find daunting to work with from scratch.
+In many cases, VST plug-in vendors or unaffiliated enthusiasts may sell additional presets for these plugins, targeted towards producers who do not have the time or interest in creating their own.\\
 \section{Implementation}
@@
 If the new individuals are coming directly from previously measured high scoring parameter sets, we ensure that they cannot be directly added to HOF without going through mutations and crossovers first.
+
+\bibliographystyle{abbrv}
+    \bibliography{nime-references} 
 \end{document}

### 2019-12-31 NIME_PAPER/SSS.tex
methodology and related work

@@
 \end {enumerate*} 
-Finally, we observed a general lack of copyright-free percussive sample-packs as well as a lack of unified approach for obtaining such a data-set by fellow researchers \cite{aouameur2019neural,ramires2019timbfeat}.
-We aim to ameliorate this issue by presenting a copyright free sample-pack of categorized percussion sounds.
+Additionally, as we observed a general lack of copyright-free percussive sample-packs as well as a lack of unified approach for obtaining such a data-set by fellow researchers \cite{aouameur2019neural,ramires2019timbfeat}, we aim to ameliorate the issue by presenting a copyright free sample-pack of categorized percussion sounds.
 Furthermore, we have included in our project source code \footnote{\url{https://github.com/imilas/Synths_Stacks_Search}} a set of scripts to further expand the sample pack via royalty free sources.
@@
 \section{Introduction}
+\subsection{Motivation}
 The rise of Digital Audio Workstations (DAW) \cite{leider2004digital} and Virtual Studio Technology (VST) based plug-ins \cite{tanev2013virtual} have rapidly transformed the sonic and material landscape of music production in the recent years.
@@
 Two notable examples of these commercial services are \textit{loopmasters}\footnote{loopmasters.com} and \textit{splice.com}\footnote{splice.com}.
-Furthermore VST plug-ins can emulate complex audio synthesizers or effects, which some producers may find daunting to work with from scratch.
+Furthermore VST plug-ins can emulate complex audio synthesizers and effects, which some producers may find daunting to work with from scratch.
 In many cases, VST plug-in vendors or unaffiliated enthusiasts may sell additional presets for these plugins, targeted towards producers who do not have the time or interest in creating their own.\\
+
+\subsection{Methodology and Related Work}
+Numerous deep, Neural Network models have been proposed and utilized for the purpose of signal generation in recent years.
+WaveGans and WaveNet have been subject to significant improvements and experiments since their proposal \cite{nsynth2017} and Variational AutoEncoders (VAE's) have been utilized for generation of short percussive samples by \cite{aouameur2019neural,ramires2019timbfeat}.
+In this work however, we opt to use digital signal processing methods to create a virtual synthesizer for the generation of audio signals, as it meets several unique requirements:
+\begin{enumerate}[label=\roman*]
+  \item Fast, offline rendering of audio with no relience on GPU, currently not possible with state of the art models such as parallel WaveGan \cite{yamamoto2019parallel} and parallell WaveNet \cite{oord2017parallel}.
+  \item Rendering at high sampling rates with little performance issues: A significant number of untrained ears can detect a change in quality between sampling rates of 192 khz and 44.1 khz \cite{reiss2016meta}, with a dramatic increase following extensive training.
+Thus we can assume that most producers would prefer their audio samples to have as high of a resolution as possible.
+However, most commonly to speed up performance, the standard sampling rate in most audio generation work neural networks appears to be 24 khz or less \cite{yamamoto2019parallel,oord2017parallel,aouameur2019neural,ramires2019timbfeat}
+  \item Neural networks are often viewed as unexplainable black box solutions.
+Some models such as VAE's can learn an underlying latent space of parameters and capture the "essence" of the different labels in a dataset.
+However, these spaces are learned in an unsupervised manner and must be manually analysed, perhaps extensively, before they can be understood \cite{esling2018generative}.
+The use of a virtual synthesizer for audio generation makes our parameters readily understandable and easily modifiable.
+\end{enumerate}
+
 \section{Implementation}

### 2020-01-01 NIME_PAPER/SSS.tex
Updates from Overleaf

@@
 The most crucial of these components are a "virtual ear" capable of evaluating a sounds proximity to different drum types and an efficient, tractable "virtual synthesizer" with a rich set of parameters and DSP methods capable of generating a wide range of sounds.\\
-Following the Unix Philosophy \cite{gancarz2003linux}, we designed our software such that we can utilize our components in various ways leading to different outcomes; hence, in order to established an adequate level of confidence in our components, we discuss the implementation, limitations, and evaluations of the "virtual synthesizer" and "virtual ear".
+We aimed to design our software such that we can utilize our components in various experimental ways; hence, in order to established an adequate level of confidence in our components, we discuss the implementation, limitations, and evaluations of the "virtual synthesizer" and "virtual ear".
 Next, we present our findings and assessments in regards to the three different methodologies utilized for the generative process of percussive sounds:  \begin {enumerate*} [label=(\roman*)]
@@
 \section{Introduction}
-\subsection{Motivation}
+\subsection{Background and Motivation}
 The rise of Digital Audio Workstations (DAW) \cite{leider2004digital} and Virtual Studio Technology (VST) based plug-ins \cite{tanev2013virtual} have rapidly transformed the sonic and material landscape of music production in the recent years.
@@
 Two notable examples of these commercial services are \textit{loopmasters}\footnote{loopmasters.com} and \textit{splice.com}\footnote{splice.com}.
-Furthermore VST plug-ins can emulate complex audio synthesizers and effects, which some producers may find daunting to work with from scratch.
-In many cases, VST plug-in vendors or unaffiliated enthusiasts may sell additional presets for these plugins, targeted towards producers who do not have the time or interest in creating their own.\\
+Furthermore VST plug-ins can emulate complex audio synthesizers and effects, which some producers may find daunting or time consuming to work with from scratch.
+In many cases, VST plug-in vendors or unaffiliated enthusiasts sell additional presets for these plugins, targeted towards producers who do not have the time or interest in creating their own.
+Once a preset is loaded in a VST plug-in, the GUI of the plug-in is updated.
+Users may modify any loaded preset until their desired sound is observed.\\
+Our work is motivated by the idea of finding new, convenient methods for the expansion of a music producer's library of sounds.
+Primarily with generation of novel, one-shot audio samples but also with automated search and creation of presets for virtual synthesizers that a producer might find  interesting.
+Using the generation of short, percussive audio samples as a starting point, this project is a proof of concept for promising avenues towards our motivational goal.\\
 
-\subsection{Methodology and Related Work}
-Numerous deep, Neural Network models have been proposed and utilized for the purpose of signal generation in recent years.
-WaveGans and WaveNet have been subject to significant improvements and experiments since their proposal \cite{nsynth2017} and Variational AutoEncoders (VAE's) have been utilized for generation of short percussive samples by \cite{aouameur2019neural,ramires2019timbfeat}.
-In this work however, we opt to use digital signal processing methods to create a virtual synthesizer for the generation of audio signals, as it meets several unique requirements:
+\subsection{Methodology}
+Towards our goal of generating original audio, we found the proper implementation of 2 major components to be crucial:
+\begin{itemize}
+    \item \textit{Virtual Synthesizer}:A flexible, deterministic, and tractable generator which can create audio.
+The core of our implementation made use of pippi, \footnote{https://github.com/luvsound/pippi} a fast, offline focused python DSP library with a C backend.
+We additionally used the scipy \cite{jones2001scipy} library a few audio effects that we found lacking in pippi.
+    \item \textit{Virtual Ear}: An ear that returns an evaluation of an audio sample; estimating the effectiveness of an audio sample's fulfillment of a producers requirements.
+The implementation and training of the ear guides the generation process towards a desired path.\\
+\end{itemize}
+Following the Unix Philosophy \cite{gancarz2003linux}, our components are designed with modularity and parallelizability in mind.
+This allows each component to be debugged, modified and improved without requiring modifications in other components; additionally, increasing the scalability and speed of experiments.
+Section \ref{impl} contains further discussion of the components as well as the code that glues the project together can be found in .\\ 
+While the main focus of this project is the generation of novel percussive sounds, our methodology indicates promising results with regards to creation of new presets for any virtual synth without the need for a-priori knowledge of the functions of its parameters (i.e the effect of parameter modulation on the sonic output).
+We also demonstrate the viability of a few lesser explored avenues for the purposes of audio synthesis and Music Information Retrieval (MIR), notably:
+\begin{enumerate}[label=\roman*]
+\item Heuristic search methods for the creation of new presets for virtual synthesizers.
+More concretely, we observed that given a virtual ear which could reliably score pieces of audio based on its resemblance to a desired category (e.g:kicks,snares,piano), we were able to rapidly search the parameters of a virtual synthesizer and create numerous parameter-sets (i.e presets) which resemble our desired category of sounds.
+\item The viability of virtual synthesizers based on Digital Signal Processing (DSP) methods for fast, unsupervised creation of novel audio, discussed in more detail in section \ref{related}. \\
+\end{enumerate}
+
+\subsection{Related Work and Contradistinctions}
+\label{related}
+Numerous deep, neural network models have been proposed and utilized for the purpose of signal generation in recent years.
+WaveGans and WaveNet have been subject to significant improvements and experiments since their proposal \cite{nsynth2017} and recently, Variational AutoEncoders (VAE's) have been utilized for generation of short percussive samples \cite{aouameur2019neural,ramires2019timbfeat}.
+In this work however, we opt to use digital signal processing methods to create a virtual synthesizer for the generation of audio signals, as it provides several unique advantages:
 \begin{enumerate}[label=\roman*]
   \item Fast, offline rendering of audio with no relience on GPU, currently not possible with state of the art models such as parallel WaveGan \cite{yamamoto2019parallel} and parallell WaveNet \cite{oord2017parallel}.
-  \item Rendering at high sampling rates with little performance issues: A significant number of untrained ears can detect a change in quality between sampling rates of 192 khz and 44.1 khz \cite{reiss2016meta}, with a dramatic increase following extensive training.
-Thus we can assume that most producers would prefer their audio samples to have as high of a resolution as possible.
-However, most commonly to speed up performance, the standard sampling rate in most audio generation work neural networks appears to be 24 khz or less \cite{yamamoto2019parallel,oord2017parallel,aouameur2019neural,ramires2019timbfeat}
+  \item Rendering at high sampling rates with little performance issues: Commonly, likely to speed up performance, the standard sampling rate in most audio generation work with neural networks appears to be under 24 khz.
+However, a significant number of untrained human ears can detect a change in quality of audio between sampling rates of 192 khz and the industry standard of 44.1 khz \cite{reiss2016meta}, with a dramatic increase in quality detection after training.
+Therefore we can safely assume that most producers would prefer their audio samples have sampling rates of 44.1 khz or higher.
+\cite{yamamoto2019parallel,oord2017parallel,aouameur2019neural,ramires2019timbfeat}
   \item Neural networks are often viewed as unexplainable black box solutions.
@@
 \section{Implementation}
+\label{impl}
 \subsection{Design}
-Towards our goal of generating original audio, we assumed that there are at least 2 major components needed:
-\begin{itemize}
-    \item A flexible, deterministic, and tractable generator which can create audio
-    \item An ear that returns an evaluation of an audio sample; used to determine whether the audio sample fulfills the requirements. 
-\end{itemize}
 
-These components are designed with modularity and parallelizability in mind.
-This allows each component to be debugged, modified and improved without affecting the other components.
-More importantly, greatly increasing the ease of scalability and speed of experiments.
-The major and minor components as well as the code that glues the project together will be discussed further in this document. 
 \begin{figure}[H]

### 2020-01-01 NIME_PAPER/SSS.tex
Updates from Overleaf

@@
     \item \textit{Virtual Ear}: An ear that returns an evaluation of an audio sample; estimating the effectiveness of an audio sample's fulfillment of a producers requirements.
-The implementation and training of the ear guides the generation process towards a desired path.\\
+The implementation and training of the ear guides the generation process towards a desired path.
+We used a labeled set of percussive and non-percussive audio files as training data to try a few different implementations of an ear, settling on a combination of a Convolutional Neural Net (CNN) model and a custom envelope detection algorithm as our "virtual drum detector ear".
+\\
 \end{itemize}
@@
   \item Fast, offline rendering of audio with no relience on GPU, currently not possible with state of the art models such as parallel WaveGan \cite{yamamoto2019parallel} and parallell WaveNet \cite{oord2017parallel}.
-  \item Rendering at high sampling rates with little performance issues: Commonly, likely to speed up performance, the standard sampling rate in most audio generation work with neural networks appears to be under 24 khz.
+  \item Rendering at high sampling rates with little performance issues: Performance speed being a common issue, the standard sampling rate in most audio generation work utilizing neural networks appears to be under 24 khz \cite{yamamoto2019parallel,oord2017parallel,aouameur2019neural,ramires2019timbfeat}.
 However, a significant number of untrained human ears can detect a change in quality of audio between sampling rates of 192 khz and the industry standard of 44.1 khz \cite{reiss2016meta}, with a dramatic increase in quality detection after training.
 Therefore we can safely assume that most producers would prefer their audio samples have sampling rates of 44.1 khz or higher.
-\cite{yamamoto2019parallel,oord2017parallel,aouameur2019neural,ramires2019timbfeat}
   \item Neural networks are often viewed as unexplainable black box solutions.
@@
 The use of a virtual synthesizer for audio generation makes our parameters readily understandable and easily modifiable.
+\\
+
 \end{enumerate}
-
+Automatic programming of virtual synthesizers has also been a topic of interest.
+In early 2000s, Interactive Genetic Algorithms (IGA's) were utilized for the generation of new sounds with various sound-engines \cite{johnson1999exploring,dahlstedt2001creating}.
+More recent work by Yee-King et al.
+\cite{yee2018automatic} used LSTM and genetic algorithms to find the exact parameters used to create a group of sounds.
+The sounds approximated were made by the same virtual synthesizer, not an external source, making the eventual replication certain, even with random search.
+Feature matching also appears to not be concerned with the envelope of the sounds, but rather the frequency content within arbitrary time windows.
+Yet another recent, impressive work by Esling et al.
+used a large dataset of over 10,000 presets for a commercial VST synthesizer to learn a latent parameter space which can be sampled for creation of new audio.
+As stated before, our work presents a rapid approximation of percussion sounds with no previous knowledge about the sonic capabilities of our virtual synthesizer.
 \section{Implementation}

### 2020-01-01 NIME_PAPER/paper.tex
Updates from Overleaf

--- 2020-01-01 NIME_PAPER/SSS.tex
@@
 \conferenceinfo{NIME'20,}{July 21-25, 2020, Royal Birmingham Conservatoire, ~~~~~~~~~~~~ Birmingham City University, Birmingham, United Kingdom.}
-\title{SSS}
+\title{Rapid, Unsupervised Generation of Novel Percussive Sounds With A Tractable Virtual Synthesizer}
 
@@
 \section{Introduction}
+\subsection{Terminology}
+Will define terms such as VSTs, audio effects, Synthesizers, paramters and presets here. I throw these terms around a lot and I think some might be confused by their meaning.
 \subsection{Background and Motivation}
@@
 
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.9\textwidth]{images/SSS_gen.png}
-\caption{Generation Pipeline}
-\label{fig:SSS generator}
-\end{figure}
+% \begin{figure}[H]
+% \centering
+% \includegraphics[width=0.9\textwidth]{images/SSS_gen.png}
+% \caption{Generation Pipeline}
+% \label{fig:SSS generator}
+% \end{figure}
 
@@
 More commonly, the frequency domain is used for MIR tasks.
-\begin{figure}[H]
-\centering
-\includegraphics[width=\textwidth]{images/SSS_ear.png}
-\caption{Evaluation Using the Ear}
-\label{fig:SSS generator}
-\end{figure}
+% \begin{figure}[H]
+% \centering
+% \includegraphics[width=\textwidth]{images/SSS_ear.png}
+% \caption{Evaluation Using the Ear}
+% \label{fig:SSS generator}
+% \end{figure}
 
-\begin{figure}[h!]
-\centering
-\includegraphics[width=0.5\textwidth]{images/specplot.png}
-\caption{Mel-spectrum representation of a randomly generated sample}
-\label{fig:SSS generator}
-\end{figure}
+% \begin{figure}[h!]
+% \centering
+% \includegraphics[width=0.5\textwidth]{images/specplot.png}
+% \caption{Mel-spectrum representation of a randomly generated sample}
+% \label{fig:SSS generator}
+% \end{figure}
 All we require from the ear is to give us probabilities of an audio sample belonging to various sound (drum and none-drum) categories.

### 2020-01-01 NIME_PAPER/paper.tex
Updates from Overleaf

@@
 The most crucial of these components are a "virtual ear" capable of evaluating a sounds proximity to different drum types and an efficient, tractable "virtual synthesizer" with a rich set of parameters and DSP methods capable of generating a wide range of sounds.\\
-We aimed to design our software such that we can utilize our components in various experimental ways; hence, in order to established an adequate level of confidence in our components, we discuss the implementation, limitations, and evaluations of the "virtual synthesizer" and "virtual ear".
+We aimed to design our software such that we can utilize our components in various experimental ways; hence, in order to established an adequate level of confidence in our components, we discuss the implementation, limitations, and evaluations of the \textit{virtual synthesizer} and \textit{virtual ear}.
 Next, we present our findings and assessments in regards to the three different methodologies utilized for the generative process of percussive sounds:  \begin {enumerate*} [label=(\roman*)]
@@
 In many cases, VST plug-in vendors or unaffiliated enthusiasts sell additional presets for these plugins, targeted towards producers who do not have the time or interest in creating their own.
-Once a preset is loaded in a VST plug-in, the GUI of the plug-in is updated.
-Users may modify any loaded preset until their desired sound is observed.\\
+Users may modify any loaded preset until their desired sound is reached.\\
 Our work is motivated by the idea of finding new, convenient methods for the expansion of a music producer's library of sounds.

### 2020-01-01 NIME_PAPER/paper.tex
Updates from Overleaf

@@
 With the generation of novel, high quality, one shot percussive sounds as our end goal, we implemented a set of modular software components utilized to form a pipeline for guided generation of sounds.
-The most crucial of these components are a "virtual ear" capable of evaluating a sounds proximity to different drum types and an efficient, tractable "virtual synthesizer" with a rich set of parameters and DSP methods capable of generating a wide range of sounds.\\
+The most crucial of these components are a "virtual ear" capable of evaluating a sound's proximity to different drum types and an efficient, tractable "virtual synthesizer" with a rich set of parameters capable of generating a wide range of sounds.\\
 We aimed to design our software such that we can utilize our components in various experimental ways; hence, in order to established an adequate level of confidence in our components, we discuss the implementation, limitations, and evaluations of the \textit{virtual synthesizer} and \textit{virtual ear}.
@@
 The rise of Digital Audio Workstations (DAW) \cite{leider2004digital} and Virtual Studio Technology (VST) based plug-ins \cite{tanev2013virtual} have rapidly transformed the sonic and material landscape of music production in the recent years.
-Coupled with this rise in popularity is a vast array of commercial products and services dedicated to satiating the need of amateur and professional music producers for unique sounds; most commonly via audio samples: one-shot drum samples, long sustained notes (commonly refered to as pads or textures), percussive or melodic loops etc.
+Coupled with this rise in popularity is a vast array of commercial products and services dedicated to satiating the need of amateur and professional music producers for unique sounds; most commonly via audio samples: one-shot drum samples, long sustained notes (commonly referred to as pads or textures), and loops(percussive or melodic) are common deliverables.
 Two notable examples of these commercial services are \textit{loopmasters}\footnote{loopmasters.com} and \textit{splice.com}\footnote{splice.com}.
-Furthermore VST plug-ins can emulate complex audio synthesizers and effects, which some producers may find daunting or time consuming to work with from scratch.
+Furthermore, VST plug-ins can emulate complex audio synthesizers and effects, which some producers may find daunting or time consuming to work with from scratch.
 In many cases, VST plug-in vendors or unaffiliated enthusiasts sell additional presets for these plugins, targeted towards producers who do not have the time or interest in creating their own.
-Users may modify any loaded preset until their desired sound is reached.\\
+Producers may further modify these presets until their desired sound is reached.\\
 Our work is motivated by the idea of finding new, convenient methods for the expansion of a music producer's library of sounds.
@@
 \cite{yee2018automatic} used LSTM and genetic algorithms to find the exact parameters used to create a group of sounds.
-The sounds approximated were made by the same virtual synthesizer, not an external source, making the eventual replication certain, even with random search.
+The sounds approximated were made by the same virtual synthesizer, not an external source; making the eventual replication certain, even with random search.
 Feature matching also appears to not be concerned with the envelope of the sounds, but rather the frequency content within arbitrary time windows.

### 2020-01-01 NIME_PAPER/paper.tex
Updates from Overleaf

@@
 Yet another recent, impressive work by Esling et al.
-used a large dataset of over 10,000 presets for a commercial VST synthesizer to learn a latent parameter space which can be sampled for creation of new audio.
+used a large dataset of over 10,000 presets for a commercial VST synthesizer to learn a latent parameter space which can be sampled for creation of new audio \cite{esling2019universal}.
 As stated before, our work presents a rapid approximation of percussion sounds with no previous knowledge about the sonic capabilities of our virtual synthesizer.

### 2020-01-01 NIME_PAPER/paper.tex
Updates from Overleaf

@@
 \conferenceinfo{NIME'20,}{July 21-25, 2020, Royal Birmingham Conservatoire, ~~~~~~~~~~~~ Birmingham City University, Birmingham, United Kingdom.}
-\title{Rapid, Unsupervised Generation of Novel Percussive Sounds With A Tractable Virtual Synthesizer}
+\title{Rapid, (semi-?)Supervised Generation of Novel Percussive Sounds With A Tractable Virtual Synthesizer}
 
@@
 
+\todo[inline, color=green!30]{I think it might be worthwhile to point out that our work has great potential for live performances, especially compared to other work, would that be appropriate for a scientific paper?
+should it be done here or in related work?}
 \subsection{Methodology}

### 2020-01-01 NIME_PAPER/paper.tex
Updates from Overleaf

@@
 
-\todo[inline, color=green!30]{I think it might be worthwhile to point out that our work has great potential for live performances, especially compared to other work, would that be appropriate for a scientific paper?
+\todo[inline, color=green!30]{I think it might be worthwhile to point out the potential in our work for live performance, compared to other works which use 3rd party VSTs, require pre-training and user interaction, would that be appropriate for a scientific paper?
 should it be done here or in related work?}

### 2020-01-01 NIME_PAPER/paper.tex
Updates from Overleaf

@@
 \subsection{Terminology}
-Will define terms such as VSTs, audio effects, Synthesizers, paramters and presets here. I throw these terms around a lot and I think some might be confused by their meaning.
+I'd like to define terms such as VSTs, audio effects, Synthesizers, paramters and presets here. I throw these terms around a lot and I think some might be confused by their meaning.
 \subsection{Background and Motivation}
@@
     \item \textit{Virtual Ear}: An ear that returns an evaluation of an audio sample; estimating the effectiveness of an audio sample's fulfillment of a producers requirements.
-The implementation and training of the ear guides the generation process towards a desired path.
-We used a labeled set of percussive and non-percussive audio files as training data to try a few different implementations of an ear, settling on a combination of a Convolutional Neural Net (CNN) model and a custom envelope detection algorithm as our "virtual drum detector ear".
+The ear's evalutations guides the generation process towards a desired path, making the implementation and training of the ear crucial to the sounds which are generated.
+A particularly effective implementation was done by using a labeled set of percussive and non-percussive audio files to train a custom model (combination of a simple Convolutional Neural Net (CNN) and a custom envelope estimation algorithm), giving us a "virtual drum detector ear".
 \\
@@
 Following the Unix Philosophy \cite{gancarz2003linux}, our components are designed with modularity and parallelizability in mind.
-This allows each component to be debugged, modified and improved without requiring modifications in other components; additionally, increasing the scalability and speed of experiments.
-Section \ref{impl} contains further discussion of the components as well as the code that glues the project together can be found in .\\ 
+This allows each component to be debugged, modified and improved without requiring modifications in other components; while additionally increasing the scalability and speed of experiments.
+Section \ref{impl} contains further discussion of the components as well as the code that glues the project together.\\ 
 While the main focus of this project is the generation of novel percussive sounds, our methodology indicates promising results with regards to creation of new presets for any virtual synth without the need for a-priori knowledge of the functions of its parameters (i.e the effect of parameter modulation on the sonic output).
@@
 The sounds approximated were made by the same virtual synthesizer, not an external source; making the eventual replication certain, even with random search.
-Feature matching also appears to not be concerned with the envelope of the sounds, but rather the frequency content within arbitrary time windows.
+Since this work more focused on pads and textures rather than drums, feature matching in this also appears to not be concerned with the envelope of the sounds, but rather the frequency content within arbitrary time windows.
 Yet another recent, impressive work by Esling et al.
 used a large dataset of over 10,000 presets for a commercial VST synthesizer to learn a latent parameter space which can be sampled for creation of new audio \cite{esling2019universal}.
-As stated before, our work presents a rapid approximation of percussion sounds with no previous knowledge about the sonic capabilities of our virtual synthesizer.
+As stated before, our work presents a rapid approximation of percussion sounds with no previous knowledge about the sonic capabilities of our virtual synthesizer, exploring the actual parameter space rather than its latent representation.
 \section{Implementation}

### 2020-01-02 NIME_PAPER/paper.tex
Updates from Overleaf

@@
 \label{impl}
-\subsection{Design}
-
 % \begin{figure}[H]
@@
 
-\subsection{The Generator}
-We used the python based Pippi library for our generator implementation\footnote{https://github.com/luvsound/pippi}.
-This library uses a C back-end and focuses on fast offline generation.
-We define a Synth as the smallest unit of sound generation.
-A single Synth can be fairly expressive on its own, but we also allow a combination of Synths, which we call a Synth Stack.
-Each Synth takes in multiple parameters (parameter-set) and generates a sound.
-If the stack size is larger than 1, the combination of these individual parameter-sets is treated as the parameter-set for the stack.
+\subsection{Virtual Synthesizer}
+We used the python based Pippi library for sound generation\footnote{https://github.com/luvsound/pippi}.
+This library uses a C back-end and focuses on fast offline generation of audio signals.
+In our implementation, a synthesizer can have any number of submodules.
+We call this number the \textit{stack size}.
+See table \ref{table:1} for the range of parameters each submodule can take.
+We call the sets of parameters that characterize a Synth's submodules a \textit{program} (analogous to a preset).
+Each submodule can make an audio signal with the length of 0.1-1 second.
+If a Synth has a stack size of more than 1, these audio signals are overlapped and the total amplitude is normalized.\\
+\begin{table}
+\begin{tabular}{ |c|c|c| } 
+\hline
+Parameters & Value Range & notes and constraints\\
+\hline \hline
+Attack & 0-3 & A-D-S-R values relative\\
+Decay & 0-3 & relative to A-S-R\\
+Sustain & 0-3 & relative to A-D-R\\
+Release & 0-3 & relative to A-D-S\\
+OSC type & sine,square,saw & tone type\\
+IsNoise & boolean & whether to generate noise\\
+Sample Length & 0-1 second & - \\
+StartTime & 0-1 second & Length+Start<1\\
+Amplitude & 0.1-1 & 1 = max amplitude\\
+Pitches(notes) & list of pitches &  range of C0(16.35hz) to B9 \\
+HP filter Cuttoff & 0-20000 & -\\
+LP filter Cuttoff & HP-20000 & never lower than HP cutoff\\
+Filter Order & 4,8,16 & butterworth filter order \\
+\hline
+\end{tabular}
+\caption{Synthesizer Submodule Parameters}
+\label{table:1}
+\end{table}
+\begin{figure}[h!]
+\centering
+\includegraphics[width=0.5\textwidth]{images/specplot.png}
+\caption{Mel-spectrum representation of a randomly generated sample. Bigger stacks give us more complex signals, but we find that ever stacks of size 1 can be powerful with the right parameters. }
+\label{fig:spectrum grid}
+\end{figure}
 
@@
 
-% \begin{figure}[h!]
-% \centering
-% \includegraphics[width=0.5\textwidth]{images/specplot.png}
-% \caption{Mel-spectrum representation of a randomly generated sample}
-% \label{fig:SSS generator}
-% \end{figure}
 All we require from the ear is to give us probabilities of an audio sample belonging to various sound (drum and none-drum) categories.

### 2020-01-02 NIME_PAPER/paper.tex
Updates from Overleaf

@@
 \usepackage[inline]{enumitem}
+\usepackage{subcaption}
+
 \begin{document}
@@
 \subsection{Terminology}
-I'd like to define terms such as VSTs, audio effects, Synthesizers, paramters and presets here. I throw these terms around a lot and I think some might be confused by their meaning.
+\todo[inline,color=green!30]{I'd like to define terms such as VSTs, audio effects, Synthesizers, paramters and presets here.
+I throw these terms around a lot and I think some might be confused by their meaning.
+Is this the appropriate place for that?
+I'd like the read to know these definionts before reading the intro.
+I can try to keep it brief and engaging}
 \subsection{Background and Motivation}
@@
 Numerous deep, neural network models have been proposed and utilized for the purpose of signal generation in recent years.
-WaveGans and WaveNet have been subject to significant improvements and experiments since their proposal \cite{nsynth2017} and recently, Variational AutoEncoders (VAE's) have been utilized for generation of short percussive samples \cite{aouameur2019neural,ramires2019timbfeat}.
+WaveGans and WaveNet have been subject to significant improvements and experiments since their proposal \cite{nsynth2017}\colorbox{green!=40}{will add more references} and recently, Variational AutoEncoders (VAE's) have been utilized for generation of short percussive samples \cite{aouameur2019neural,ramires2019timbfeat}.
 In this work however, we opt to use digital signal processing methods to create a virtual synthesizer for the generation of audio signals, as it provides several unique advantages:
@@
 As stated before, our work presents a rapid approximation of percussion sounds with no previous knowledge about the sonic capabilities of our virtual synthesizer, exploring the actual parameter space rather than its latent representation.
-\section{Implementation}
-\label{impl}
-% \begin{figure}[H]
-% \centering
-% \includegraphics[width=0.9\textwidth]{images/SSS_gen.png}
-% \caption{Generation Pipeline}
-% \label{fig:SSS generator}
-% \end{figure}
-
-\subsection{Virtual Synthesizer}
-We used the python based Pippi library for sound generation\footnote{https://github.com/luvsound/pippi}.
-This library uses a C back-end and focuses on fast offline generation of audio signals.
-In our implementation, a synthesizer can have any number of submodules.
-We call this number the \textit{stack size}.
-See table \ref{table:1} for the range of parameters each submodule can take.
-We call the sets of parameters that characterize a Synth's submodules a \textit{program} (analogous to a preset).
-Each submodule can make an audio signal with the length of 0.1-1 second.
-If a Synth has a stack size of more than 1, these audio signals are overlapped and the total amplitude is normalized.\\
-\begin{table}
-\begin{tabular}{ |c|c|c| } 
+\begin{table}[h!]
+\centering
+\resizebox{\columnwidth}{!}{\begin{tabular}{ |c|c|c| } 
 \hline
@@
 \hline
-\end{tabular}
+\end{tabular}}
 \caption{Synthesizer Submodule Parameters}
@@
 \end{table}
+
+\section{Implementation}
+\label{impl}
+
+\subsection{Virtual Synthesizer}
+We used the python based Pippi library for sound generation\footnote{https://github.com/luvsound/pippi}.
+This library uses a C back-end and focuses on fast offline generation of audio signals.
+In our implementation, a synthesizer can have any number of submodules.
+We call this number the \textit{stack size}.
+See table \ref{table:1} for the range of parameters each submodule can take.
+We call the sets of parameters that characterize a Synth's submodules a \textit{program} (analogous to a preset).
+Each submodule can make an audio signal with the length of 0.1-1 second.
+If a Synth has a stack size of more than 1, these audio signals are overlapped and the total amplitude is normalized.\\
+
 \begin{figure}[h!]
 \centering
-\includegraphics[width=0.5\textwidth]{images/specplot.png}
-\caption{Mel-spectrum representation of a randomly generated sample. Bigger stacks give us more complex signals, but we find that ever stacks of size 1 can be powerful with the right parameters. }
-\label{fig:spectrum grid}
+\begin{subfigure}[b]{\linewidth}
+\includegraphics[width=0.3\linewidth]{example-image-a}
+\includegraphics[width=0.3\linewidth]{example-image-b}
+\includegraphics[width=0.3\linewidth]{example-image-c}
+\caption{64 stack}\label{fig:64stack}
+\setcounter{subfigure}{0}%
+\end{subfigure}
+
+\begin{subfigure}[b]{\linewidth}
+\includegraphics[width=0.3\linewidth]{example-image-a}
+\includegraphics[width=0.3\linewidth]{example-image-b}
+\includegraphics[width=0.3\linewidth]{example-image-c}
+\caption{8 stacks}\label{fig:8stacl}
+\setcounter{subfigure}{1}%
+\end{subfigure}
+
+\begin{subfigure}[b]{\linewidth}
+\includegraphics[width=0.3\linewidth]{images/specplot.png}
+\includegraphics[width=0.3\linewidth]{images/specplot.png}
+\includegraphics[width=0.3\linewidth]{images/specplot.png}
+\caption{1 stack}\label{fig:1stack}
+\setcounter{subfigure}{2}%
+\end{subfigure}
+\caption{Examples of mel-spectrum representations of randomly generated samples.
+Bigger stacks give us more complex signals, but we find that even stacks of size 1 can be powerful with the right parameters.
+\colorbox{green!=40}{update this with actual spectrums}}
+\label{fig:stackspectrums}
 \end{figure}
@@
 \subsection{The Ear}
-The most challenging and important component of the project; the ear can be any method of evaluating a piece of audio.
-The most basic representation of a piece of digital audio is via list of numbers and a sampling-rate.
-For simplicity, we fix the sampling rate to 41,000 per second across all components of this project.
-An array representation of audio is the representation of the audio within the time domain.
-More commonly, the frequency domain is used for MIR tasks.
+We defined an ear as any method of evaluating a piece of audio, capable of "listening" to a piece of audio and giving it a score (or a list of scores) based on how well it satisfies certain criteria.
+Since in this work we are mainly focused on percussive generation, what we require from the ear is to give us probabilities of an audio sample belonging to various sound (drum and none-drum) categories.
+As our synthesizer outputs are deterministic for all programs, allowing us to associate the categorical probabilities of each sound with the program that generated it; navigating our synthesis towards parameters which give us the desired sonic output.\\
 % \begin{figure}[H]
@@
 % \end{figure}
-
-All we require from the ear is to give us probabilities of an audio sample belonging to various sound (drum and none-drum) categories.
-It should be self-evident that these probabilities should sum up to 1.\\
-
-We have implemented several methods of feature extraction thus far and successfully separated different drum categories in interesting ways, visualized in the "interactive\_separation\_graph.ipynb" notebook.
+%  The most basic representation of a piece of digital audio is via list of numbers and a sampling-rate.
+For simplicity, we fix the sampling rate to 41,000 per second across all components of this project.
+An array representation of audio is the representation of the audio within the time domain.
+More commonly, the frequency domain is used for MIR tasks.
+We have implemented several methods of feature extraction and successfully separated different drum categories in interesting ways. 
+\todo[inline, color=green!30]{is this the right place to show off some t-sne graphs of how various feature extraction methods seperated drum categories?}
 A common pitfall of most feature extraction methods implemented is that they do not consider the temporal trends within the audio, making them highly susceptible to errors when evaluating audio that should not belong to any of the categories.\\
-\todo[inline, color=green!40]{
-Sanity Check: If a drum sample is reversed or chopped up, its likelihood of being labeled the same should change.}
-
+Analysis of the frequency content of a piece of audio using windowing functions is a common MIR procedure.
+Care must be taking such that information critical to percussion categorization such as envelope and temporal changes are not lost in this process.
+For example, we do not want a reversed kick sample to be labeled as a kick, or even a drum, even if it has the correct frequency content.
 There are two interconnected temporal trends to consider:
@@
     \item Change in amplitude within each frequency bin. Harder to measure and utilize and possibly not as important for our purposes, considering the short length of our samples.
-    \item Overall amplitude change within a sample. Closely linked to ADSR. 
+    \item Overall amplitude change within a sample. Closely linked to ADSR\\. 
 \end{itemize}{}
-
-Temporal trends are can be deduced from a spectrum representation of sound (at least visually by a human).
-A convolution net trained on our drum dataset led to an ear good enough to continue to the next stage of the project.
-The current model does an adequate job of rejecting junk data and semi-robustly rejects samples with inappropriate wave-shapes.
+Temporal trends may be deduced from a spectrum representation of sound.
+A convolution net trained on our drum dataset, combined with an algorithm ADSR extraction algorithm led to an ear which can reliably reject junk data and samples with inappropriate wave-shapes.
+\todo[inline,color=green!30]{This paragraph is lying, I haven't done the ADSR algorithm part yet.
+Highest priority after writing this paper.}
 \begin{figure}[H]
@@
 \includegraphics[width=0.8\linewidth]{images/cnn_ear.png}
-\caption{CNN ear working well on a test set}
+\caption{Model working well on a test set}
 \label{fig:ok ear}
 \end{figure}
-
-\subsection{Generator+Ear}
-Once we have a generator and an ear, we can quickly generate a large dataset where each data item is a random parameter-set, the ear score of the parameter-set and the corresponding rankings for each category.
-The rankings are derived from the probability scores.
-For example, the category with the highest probability will have the rank of 1, second highest would rank 2nd, and the lowest probability will have the rank of n (assuming n categories).\\
-Important to highlight is that thus far we have only used 1 Synth to generate our sounds, but our generator has the capability to use larger Synth Stacks, and the pipelines are written with that possibility in mind.\\
-\todo[inline]{A seen in Figure \ref{fig:rank portions}, there is a bias in random generation towards making higher ranking hats and kicks and lower ranking shakers, claps.
-Is this bias because of Synth structure or a problem with the ear?}
+\todo[inline,color=green!30]{ will add f-measure calculations and other confidence inducing graphs (for example I have a grid of spectrums with the ear's guess vs the actual label under each spectrum, I can colorize the grid depending on whether the guess was correct or not).
+Code in the notebooks.
+After updating ear, I will make them look presentable and add them.}
+\subsection{How Can The Synth and Ear Interact?}
+With our Synth and Ear in place, we can quickly generate programs for our Synth, create the corresponding audio sample and get the scores for the audio sample.
+If the ear returns a vector of categorical probabilities, we can assign categorical ranks to the audio sample.
+For example, the category with the highest probability will have the rank of 1, second highest would rank 2nd, and the lowest probability will have the rank of n (assuming n categories).\textbf{
+But how can we use this to create percussion sounds?}\\\\
+We utilize our tools in three different methods of generation, with their specific imlpementation discussed in section \ref{gens}.
+\begin {enumerate} [label=(\roman*)]
+\item Random Generation: We randomly create a drum programs until a sound belonging to our category is produced. We hypothesize that due to the speed of our experiments, it is a viable approach.
+\item Multivariate Distribution Sampling: We attempt to learn the joint distribution of our parameters in order to maximize generation of a certain drum category. 
+\item Genetic Search: We treat our parameters as genes and attempt to use evolutionary search algorithms to find programs that the ear deems most fit.\\
+\end {enumerate} 
+\todo[inline,color=blue!30]{As seen in Figure \ref{fig:rank portions}, there is a bias in random generation towards making higher ranking hats and kicks and lower ranking shakers, claps.
+Is this bias because of Synth structure or a problem with the ear?
+Will analyse further after updating ear}
 \begin{figure}[h!]
@@
 We are interested in the small percentages of random generations that trick the ear due to coincidentally being similar to actual drums (i.e those who received a rank of 1) }
-\todo[inline, color=green!30]{When looking for the best sounds of each category, could use ranks 2 and 3 etc. as well, however:
+\todo[inline, color=blue!30]{When looking for the best sounds of each category, could use ranks 2 and 3 etc. as well, however:
 \unexpanded{\unexpanded{
@@
     \item The task requires even more confidence in ear,
-    \item Generation is fast enough that we don't need to use ranks higher than 1. We have more than enough data if we don't want to deal with this task.
 \end{itemize} 
@@
 \section{Novel Generations}
+\label{gens}
 \subsection{Goal}

### 2020-01-02 NIME_PAPER/paper.tex
section 2

@@
 As our synthesizer outputs are deterministic for all programs, allowing us to associate the categorical probabilities of each sound with the program that generated it; navigating our synthesis towards parameters which give us the desired sonic output.\\
-% \begin{figure}[H]
-% \centering
-% \includegraphics[width=\textwidth]{images/SSS_ear.png}
-% \caption{Evaluation Using the Ear}
-% \label{fig:SSS generator}
-% \end{figure}
+
 %  The most basic representation of a piece of digital audio is via list of numbers and a sampling-rate.
@@
 After updating ear, I will make them look presentable and add them.}
+%
+% How Can The Synth and Ear Interact?
+%
 \subsection{How Can The Synth and Ear Interact?}
+
+\begin{figure*}[htbp]
+	\centering
+		\includegraphics[width=0.7\textwidth]{images/SSS_gen.png}
+	\caption{\colorbox{green!=40}{ This graph is bad in many ways.} but would it be worthwhile to have a \textbf{good} flowchart of 
+	the generation pipeline in the paper? }
+	\label{fig:BlockDiagram2}
+\end{figure*}
+\label{fig:generation}
+
 With our Synth and Ear in place, we can quickly generate programs for our Synth, create the corresponding audio sample and get the scores for the audio sample.
@@
 \includegraphics[width=1\linewidth]{images/random_ranks.png}
-\caption{Figure showing proportions of categorical ranks for around 50,000 randomly generated sounds.
+\caption{\colorbox{green!=40}{will update and make labels bigger} Showing proportions of categorical ranks for around 50,000 randomly generated sounds.
 Only showing ranks 1-5.
@@
 \label{gens}
-\subsection{Goal}
+\subsection{The Goal}
  Given a category, our aim is to use random generations to guide an algorithm towards novel generation of drums for that category.
 
-\subsection{Guided Generation Attempts}
+\subsection{Methodologies}
+\subsubsection{Random Generation}
 

### 2020-01-03 paper.tex
section 3 + 4

--- 2020-01-02 NIME_PAPER/paper.tex
@@
 Is this the appropriate place for that?
-I'd like the read to know these definionts before reading the intro.
+I'd like the reader to know these definitions before reading the intro.
 I can try to keep it brief and engaging}
@@
 Numerous deep, neural network models have been proposed and utilized for the purpose of signal generation in recent years.
-WaveGans and WaveNet have been subject to significant improvements and experiments since their proposal \cite{nsynth2017}\colorbox{green!=40}{will add more references} and recently, Variational AutoEncoders (VAE's) have been utilized for generation of short percussive samples \cite{aouameur2019neural,ramires2019timbfeat}.
+WaveGans and WaveNet have been subject to significant improvements and experiments since their proposal \colorbox{green!=40}{\cite{nsynth2017} + Many more references to be added.} Even more recently, Variational AutoEncoders (VAE's) have been utilized for generation of short percussive samples \cite{aouameur2019neural,ramires2019timbfeat}.
 In this work however, we opt to use digital signal processing methods to create a virtual synthesizer for the generation of audio signals, as it provides several unique advantages:
@@
   \item Fast, offline rendering of audio with no relience on GPU, currently not possible with state of the art models such as parallel WaveGan \cite{yamamoto2019parallel} and parallell WaveNet \cite{oord2017parallel}.
-  \item Rendering at high sampling rates with little performance issues: Performance speed being a common issue, the standard sampling rate in most audio generation work utilizing neural networks appears to be under 24 khz \cite{yamamoto2019parallel,oord2017parallel,aouameur2019neural,ramires2019timbfeat}.
+  \item Rendering at high sampling rates: Performance speed being a common issue, the standard sampling rate in most audio generation work utilizing neural networks appears to be under 24 khz \cite{yamamoto2019parallel,oord2017parallel,aouameur2019neural,ramires2019timbfeat}.
 However, a significant number of untrained human ears can detect a change in quality of audio between sampling rates of 192 khz and the industry standard of 44.1 khz \cite{reiss2016meta}, with a dramatic increase in quality detection after training.
@@
 Some models such as VAE's can learn an underlying latent space of parameters and capture the "essence" of the different labels in a dataset.
-However, these spaces are learned in an unsupervised manner and must be manually analysed, perhaps extensively, before they can be understood \cite{esling2018generative}.
+However, these spaces are learned in an unsuperv manner and must be manually analysed, perhaps extensively, before they can be understood \cite{esling2018generative}.
 The use of a virtual synthesizer for audio generation makes our parameters readily understandable and easily modifiable.
@@
 As our synthesizer outputs are deterministic for all programs, allowing us to associate the categorical probabilities of each sound with the program that generated it; navigating our synthesis towards parameters which give us the desired sonic output.\\
-% \begin{figure}[H]
-% \centering
-% \includegraphics[width=\textwidth]{images/SSS_ear.png}
-% \caption{Evaluation Using the Ear}
-% \label{fig:SSS generator}
-% \end{figure}
 %  The most basic representation of a piece of digital audio is via list of numbers and a sampling-rate.
@@
 After updating ear, I will make them look presentable and add them.}
+%
+% How Can The Synth and Ear Interact?
+%
+\begin{figure}[H]
+\centering
+\includegraphics[width=1\linewidth]{images/random_ranks.png}
+\caption{\colorbox{green!=40}{labels bigger + show other stack sizes} Showing proportions of categorical ranks for around 50,000 randomly generated sounds.
+Only showing ranks 1-5.
+About 90\% received the rank of 1 (blue portion of the bar) for the "synth" category, meaning that the ear correctly gave the highest probability to the sound being from a synth combination.
+We are interested in the small percentages of random generations that trick the ear due to coincidentally being similar to actual drums (i.e those who received a rank of 1) }
+\todo[inline, color=blue!30]{When looking for the best sounds of each category, could use ranks 2 and 3 etc. as well, however:
+\unexpanded{\unexpanded{
+\begin{itemize}
+    \item We must figure out how to penalize their parameters
+    \item The task requires even more confidence in ear,
+\end{itemize} 
+}}}
+
+\label{fig:rank portions}
+\end{figure}
 \subsection{How Can The Synth and Ear Interact?}
+
+\begin{figure*}[htbp]
+	\centering
+		\includegraphics[width=0.7\textwidth]{images/SSS_gen.png}
+	\caption{\colorbox{green!=40}{ This graph is bad in many ways.} but would it be worthwhile to have a \textbf{good} flowchart of 
+	the generation pipeline in the paper? }
+	\label{fig:BlockDiagram2}
+\end{figure*}
+\label{fig:generation}
+
 With our Synth and Ear in place, we can quickly generate programs for our Synth, create the corresponding audio sample and get the scores for the audio sample.
@@
 Will analyse further after updating ear}
-\begin{figure}[h!]
-\centering
-\includegraphics[width=1\linewidth]{images/random_ranks.png}
-\caption{Figure showing proportions of categorical ranks for around 50,000 randomly generated sounds.
-Only showing ranks 1-5.
-About 90\% received the rank of 1 (blue portion of the bar) for the "synth" category, meaning that the ear correctly gave the highest probability to the sound being from a synth combination.
-We are interested in the small percentages of random generations that trick the ear due to coincidentally being similar to actual drums (i.e those who received a rank of 1) }
-\todo[inline, color=blue!30]{When looking for the best sounds of each category, could use ranks 2 and 3 etc. as well, however:
-\unexpanded{\unexpanded{
-\begin{itemize}
-    \item We must figure out how to penalize their parameters
-    \item The task requires even more confidence in ear,
-\end{itemize} 
-}}}
 
-\label{fig:rank portions}
-\end{figure}
 \section{Novel Generations}
 \label{gens}
-\subsection{Goal}
+\subsection{The Goal}
  Given a category, our aim is to use random generations to guide an algorithm towards novel generation of drums for that category.
-
-\subsection{Guided Generation Attempts}
-
+We evaluate each method by measuring how many samples of categories \textit{kick,snare} and \textit{hat} can be produced in under a minute.
+Finally we show results of a survey conducted to measure the quality of these samples.
+\subsection{General Methods}
+\subsubsection{Random Generation}
+To establish a benchmark, we seek to establish the likelihood of generating samples of each category if we generate programs for various stack sizes by random selection of parameters. \\
+\begin{figure}[H]
+\centering
+\begin{subfigure}[b]{\linewidth}
+\includegraphics[width=0.48\linewidth]{example-image-a}
+\includegraphics[width=0.48\linewidth]{example-image-a}
+\label{fig:1stack}
+\setcounter{subfigure}{2}%
+\end{subfigure}
+\caption{\colorbox{green!=40}{todo}Graphs showing the effectiveness of this method for producing chosesn categories in under a minute}
+\label{fig:rand-graphs}
+\end{figure}
 \subsubsection{Multivariate Normal}
 Some success and extremely fast and scalable once the parameter space is calculated.
+A well known issue with this apporach is that the parameter space for virtual synthesizers are often neither differenciable nor gaussian \cite{esling2019universal} (a couple more papers also talked about this, I have to find them).
 Currently our parameters are array indices mapping to different values for Synth components.
 This makes the assumption that our discrete parameter space is normally distributed or differentiable in-appropriate and prone to errors.
+\\
+\begin{figure}[H]
+\centering
+\begin{subfigure}[b]{\linewidth}
+\includegraphics[width=0.48\linewidth]{example-image-b}
+\includegraphics[width=0.48\linewidth]{example-image-b}
+\label{fig:1stack}
+\setcounter{subfigure}{2}%
+\end{subfigure}
+\caption{\colorbox{green!=40}{todo}Graphs showing the effectiveness of this method for producing chosesn categories in under a minute}
+\label{fig:multi-graphs}
+\end{figure}
 
@@
 The new generation consists of the top 80\% of the offspring generation and 20\% new individuals to quicken gene diversity.
-If the new individuals are coming directly from previously measured high scoring parameter sets, we ensure that they cannot be directly added to HOF without going through mutations and crossovers first.
+If the new individuals are coming directly from previously measured high scoring parameter sets, we ensure that they cannot be directly added to HOF without going through mutations and crossovers first.\\
 
+\begin{figure}[H]
+\centering
+\begin{subfigure}[b]{\linewidth}
+\includegraphics[width=0.48\linewidth]{example-image-c}
+\includegraphics[width=0.48\linewidth]{example-image-c}
+\label{fig:1stack}
+\setcounter{subfigure}{2}%
+\end{subfigure}
+\caption{\colorbox{green!=40}{todo}Graphs showing the effectiveness of this method for producing chosesn categories in under a minute}
+\label{fig:evo-graphs}
+\end{figure}
+\subsubsection{Survey of Generated Drums}
+\label{survey}
+\colorbox{green!=30}{Finalize ear,generate,make survey.} The survey will be sent out. I know a few producers who are willing to do this.
+3 algorithms, 3 categories, 10 samples for each algorithm and category pair, 2 seconds to listen to each sample-> 3 minutes for listening
+I imagine survey will be around 5-6 minutes long.
+\subsubsection{Contrasting Ear Scores With Survey Results}
+\colorbox{green!=30}{pending section \ref{survey}}
+\section{Code and Database}
+\colorbox{green!=30}{One last thing to do, will take a 1 day}\\
+\colorbox{blue!=30}{Should this section be at the start of the paper?Appendix?}\\
+talk about  categories, sources, dataprocessing. 
+Code for the data processing is written, I need to download the no-copyright sounds, run the code and host the results. 
+Give link for people to download it, show where to find the scripts for database expansion.
+\section{Summary and Conclusions}
+\colorbox{green!=30}{Points I want to make:}
+\begin{itemize}
+    \item Our methodology was successful in generating novel examples of some percussion categories.
+    \item With the right implementation of DSP methods to create a synth, Genetic search is viable for finding  desired programs and parameters.
+    \item When possible, using DSP methods instead of NNs is preferable in many ways(speed,computation,hardware requirements).\\
+    \colorbox{green!=30}{Include some speed measurements in appendix?}
+    \item ...
+\end{itemize}
+\section{Future Work}
+\colorbox{blue!=30}{Should really think this through}
+\begin{itemize}
+    \item Potential for other generative methods (e.g reinforcement learning)
+    \item Making the synth's sound range more diverse while maintaining speed and efficiency
+\end{itemize}
 \bibliographystyle{abbrv}

### 2020-01-03 TEMPLATE/nime-template.tex
Updates from Overleaf

% Template for NIME 2020
%
% Modified by Joe Wright 14 December 2019
% Modified by Niccolò Granieri 10 October 2018 
% Modified by Angelo Fraietta 23 December 2018
% Modified by Angelo Fraietta 22 November 2018
% Modified by Rodrigo Schramm on 22 September 2018
% Modified by Luke Dahl on 17 October 2-17
% Modified by Cumhur Erkut on <2016-10-11 Tue>
% Modified by Edgar Berdahl on 5 November 2014
% Modified by Baptiste Caramiaux on 25 November 2013
% Modified by Kyogu Lee on 7 October 2012
% Modified by Georg Essl on 7 November 2011
%
% Based on "sig-alternate.tex" V1.9 April 2009
% This file should be compiled with "nime-alternate.cls"

\documentclass{nime-alternate} % Uncomment when publishing final version

% Uncomment only one of the ones below
\usepackage{anonymize} 		   %Uncomment this line to publish
% \usepackage[blind]{anonymize}%Uncomment this line for blind review

% Package that enables the use of accents and non 
% standard characters
\usepackage[utf8]{inputenc}

\begin{document}

% --- Author Metadata here ---
%\conferenceinfo{NIME'17,}{May 15-19, 2017, Aalborg University Copenhagen, Denmark.}
%\conferenceinfo{NIME'18,}{June 3-6, 2018, Blacksburg, Virginia, USA.}
%\conferenceinfo{NIME'19,}{June 3-6, 2019, Federal University of Rio Grande do Sul, ~~~~~~  Porto Alegre,  Brazil.}
\conferenceinfo{NIME'20,}{July 21-25, 2020, Royal Birmingham Conservatoire, ~~~~~~~~~~~~ Birmingham City University, Birmingham, United Kingdom.}
\title{NIME Proceedings Template for LaTeX}

% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
\label{key}% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{8} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
\anonymize{Ben Trovato}\titlenote{\anonymize{Dr.~Trovato insisted his name be first.}}\\
       \affaddr{\anonymize{Institute for Clarity in Documentation}}\\
       \affaddr{\anonymize{1932 Wallamaloo Lane}}\\
       \affaddr{\anonymize{Wallamaloo, New Zealand}}\\
       \email{\anonymize{trovato@corporation.com}}
% 2nd. author
\alignauthor
\anonymize{G.K.M. Tobin}\titlenote{\anonymize{The secretary disavows
any knowledge of this author's actions.}}\\
       \affaddr{\anonymize{Institute for Clarity in Documentation}}\\
       \affaddr{\anonymize{P.O. Box 1212}}\\
       \affaddr{\anonymize{Dublin, Ohio 43017-6221}}\\
       \email{\anonymize{webmaster@marysville-ohio.com}}
% 3rd. author
\alignauthor \anonymize{Lars Th{\o}rv{\"a}ld}\titlenote{This author is the
one who did all the really hard work.}\\
       \affaddr{\anonymize{The Th{\o}rv{\"a}ld Group}}\\
       \affaddr{\anonymize{1 Th{\o}rv{\"a}ld Circle}}\\
       \affaddr{\anonymize{Hekla, Iceland}}\\
       \email{l\anonymize{arst@affiliation.org}}
\and  % use '\and' if you need 'another row' of author names
% 4th. author
\alignauthor \anonymize{Lawrence P. Leipuner}\\
       \affaddr{\anonymize{Brookhaven Laboratories}}\\
       \affaddr{\anonymize{Brookhaven National Lab}}\\
       \affaddr{\anonymize{P.O. Box 5000}}\\
       \email{\anonymize{lleipuner@researchlabs.org}}
% 5th. author
\alignauthor \anonymize{Sean Fogarty}\\
       \affaddr{\anonymize{NASA Ames Research Center}}\\
       \affaddr{\anonymize{Moffett Field}}\\
       \affaddr{\anonymize{California 94035}}\\
       \email{\anonymize{fogartys@amesres.org}}
% 6th. author
\alignauthor \anonymize{Anon Nymous}\\
       \affaddr{\anonymize{Redacted }}\\
       \affaddr{\anonymize{8600 Datapoint Drive}}\\
       \affaddr{\anonymize{San Antonio, Texas 78229}}\\
       \email{\anonymize{cpalmer@prl.com}}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
\additionalauthors{Additional authors: \anonymize{John Smith (The Th{\o}rv{\"a}ld Group,}
email: {\texttt{\anonymize{jsmith@affiliation.org}}}) and \anonymize{Julius P.~Kumquat 
(K. Consortium,} email: {\texttt{\anonymize{jpkumquat@consortium.net}}}).}
\date{30 July 1999}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

% For your initial submission you MUST ANONYMIZE the authors.

\maketitle
\begin{abstract}
This paper provides a sample of a \LaTeX\ document for the NIME conference series. It conforms,
somewhat loosely, to the formatting guidelines for
ACM SIG Proceedings. It is an {\em alternate} style which produces
a {\em tighter-looking} paper and was designed in response to
concerns expressed, by authors, over page-budgets.
It complements the document \textit{Author's (Alternate) Guide to
Preparing ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}.
This source file has been written with the intention of being
compiled under \LaTeX$2_\epsilon$\ and BibTeX.

To make best use of this sample document, run it through \LaTeX\
and BibTeX, and compare this source code with your compiled PDF file. A compiled PDF version is available to help you with the `look and feel.'  \textbf{The paper submitted to the NIME conference must be stored in an \underline{A4}-sized PDF file, so North Americans should take care not to inadvertently generate \underline{letter} paper-sized PDF files.}  This paper template should prevent that from happening if the \texttt{pdflatex} program is used to generate the PDF file.

The abstract should preferably be between 100 and 200 words.
\end{abstract}

\keywords{NIME, proceedings, \LaTeX, template}

% ------- CCS Concepts
% Here is where you enter the CCS Concepts for your paper.
%
% It is strongly recommended that authors view the submission form
% prior to starting to write the paper, which includes information 
% on the CCS Concepts. 
% 
% The 2012 ACM Computing Classification System (CCS) replaces the
% traditional 1998 version, which has served as the de facto 
% standard classification system for the computing field. It is
% being integrated into the search capabilities and visual topic 
% displays of the ACM Digital Library. Please enter the CCS XML code 
% for the classification terms that describe your paper. To get the 
% XML code, please use the following procedure, which is
% demonstrated using three NIME-related example terms: Applied
% computing~Sound and music computing, Applied computing~Performing
% arts, and Information systems~Music retrieval.
%
% 1) Browse to the website http://dl.acm.org/ccs_flat.cfm.
% 2) Select one to three classification terms from the website that
%    describe your paper (e.g. for the example paper Applied
%    computing~Sound and music computing, Applied 
%    computing~Performing arts, and Information systems~Music
%    retrieval.).
% 3) For each classification you need to select the relevance
%    (e.g. for this example, Sound and music computing is "high",
%    Performing arts is "low", and Music retrieval is "Medium")
% 4) Once you have selected the last term, click on "view CCS Tex
%    Code". This will generate some code, which includes some CCSXML
%    and some lines beginning with \ccsdesc.
% 5) Keep all of this code, as you will need it for entering into
%    the Precision Conference System paper submission form.
% 6) For this document, keep only the \ccsdesc lines. Here is what
%    you would paste for the classification example:

\ccsdesc[500]{Applied computing~Sound and music computing}
\ccsdesc[100]{Applied computing~Performing arts}
\ccsdesc[300]{Information systems~Music retrieval}

% this line creates the CCS Concepts section.
\printccsdesc

\textbf{Please read the comments starting on line 140 of the nime-template.tex file to see how to create the CCS Concept Classifications!} % Remove this line in your paper!

\section{Introduction}
The \textit{proceedings} are the records of a conference.
ACM seeks to give these conference by-products a uniform,
high-quality appearance.  To do this, ACM has some rigid
requirements for the format of the proceedings documents: there
is a specified format (balanced  double columns), a specified
set of fonts (Arial or Helvetica and Times Roman) in
certain specified sizes (for instance, 9 point for body copy).

The good news is, with only a handful of manual
settings,\footnote{Two of these, the {\texttt{\char'134 numberofauthors}}
and {\texttt{\char'134 alignauthor}} commands, you have
already used; another, {\texttt{\char'134 balancecolumns}}, will
be used in your very last run of \LaTeX\ to ensure
balanced column heights on the last page.} the \LaTeX\ document
class file handles all of this for you.

The remainder of this document is concerned with showing, in
the context of an ``actual'' document, the \LaTeX\ commands
specifically available for denoting the structure of a
proceedings paper, rather than with giving rigorous descriptions
or explanations of such commands.

\section{The {\secit Body} of The Paper}
Typically, the body of a paper is organized
into a hierarchical structure, with numbered or unnumbered
headings for sections, subsections, sub-subsections, and even
smaller sections.  The command \texttt{{\char'134}section} that
precedes this paragraph is part of such a
hierarchy.\footnote{This is the second footnote.  It
starts a series of three footnotes that add nothing
informational, but just give an idea of how footnotes work
and look. It is a wordy one, just so you see
how a longish one plays out.} \LaTeX\ handles the numbering
and placement of these headings for you, when you use
the appropriate heading commands around the titles
of the headings.  If you want a sub-subsection or
smaller part to be unnumbered in your output, simply append an
asterisk to the command name.  Examples of both
numbered and unnumbered headings will appear throughout the
balance of this sample document.

Because the entire article is contained in
the \textbf{document} environment, you can indicate the
start of a new paragraph with a blank line in your
input file; that is why this sentence forms a separate paragraph.

\subsection{Type Changes and {\subsecit Special} Characters}
We have already seen several typeface changes in this sample.  You
can indicate italicized words or phrases in your text with
the command \texttt{{\char'134}textit}; emboldening with the
command \texttt{{\char'134}textbf}
and typewriter-style (for instance, for computer code) with
\texttt{{\char'134}texttt}.  But remember, you do not
have to indicate typestyle changes when such changes are
part of the \textit{structural} elements of your
article; for instance, the heading of this subsection will
be in a sans serif\footnote{A third footnote, here.
Let's make this a rather short one to
see how it looks.} typeface, but that is handled by the
document class file. Take care with the use
of\footnote{A fourth, and last, footnote.}
the curly braces in typeface changes; they mark
the beginning and end of
the text that is to be in the different typeface.

You can use whatever symbols, accented characters, or
non-English characters you need anywhere in your document;
you can find a complete list of what is
available in the \textit{\LaTeX\
User's Guide} \cite{Lamport:LaTeX}.

\subsection{Tables}
Because tables cannot be split across pages, the best
placement for them is typically the top of the page
nearest their initial cite.  To
ensure this proper ``floating'' placement of tables, use the
environment \textbf{table} to enclose the table's contents and
the table caption.  The contents of the table itself must go
in the \textbf{tabular} environment, to
be aligned properly in rows and columns, with the desired
horizontal and vertical rules.  Again, detailed instructions
on \textbf{tabular} material
is found in the \textit{\LaTeX\ User's Guide}.

Immediately following this sentence is the point at which
Table~\ref{tab:frequency} is included in the input file; compare the
placement of the table here with the table in the printed
dvi output of this document.

To get correct numbering of tables, please use the \textbf{label} command inside the \textbf{table} environment and a corresponding \textbf{ref} in the text.

\begin{table}
\centering
\caption{Frequency of Special Characters}
\begin{tabular}{|c|c|l|} \hline
Non-English or Math&Frequency&Comments\\ \hline
\O & 1 in 1,000& For Swedish names\\ \hline
$\pi$ & 1 in 5& Common in math\\ \hline
\$ & 4 in 5 & Used in business\\ \hline
$\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
\hline\end{tabular}
\label{tab:frequency}
\end{table}

To set a wider table, which takes up the whole width of
the page's live area, use the environment
\textbf{table*} to enclose the table's contents and
the table caption.  As with a single-column table, this wide
table will ``float" to a location deemed more desirable.
Immediately following this sentence is the point at which
Table 2 is included in the input file; again, it is
instructive to compare the placement of the
table here with the table in the printed dvi
output of this document.

\begin{table*}[htbp]
\centering
\caption{Some Typical Commands}
\begin{tabular}{|c|c|l|} \hline
Command&A Number&Comments\\ \hline
\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
\texttt{{\char'134}table}& 300 & For tables\\ \hline
\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
\end{table*}
% end the environment with {table*}, NOTE not {table}!

\subsection{Figures}
Like tables, figures cannot be split across pages; the best placement for them is typically the top or the bottom of the page nearest their initial cite. To ensure this proper ``floating'' placement of figures, use the environment \textbf{figure} to enclose the figure and its caption. Optionally, for small figures that you want to place inline with the text, you can use the \textbf{htbp} options to \textbf{figure} to see whether there is space for placing it inline with the text.

This sample document contains examples of \textbf{.pdf} (Figure~\ref{fig:BlockDiagram1}) and \textbf{.jpg} files to be displayable with \LaTeX. More details on each of these is found in the \textit{Author's Guide}.

\begin{figure}[htbp]
	\centering
		\includegraphics[width=1\columnwidth]{BlockDiagram1}
	\caption{A sample image in PDF format.}
	\label{fig:BlockDiagram1}
\end{figure}

As was the case with tables, you may want a figure that spans two columns (Figure~~\ref{fig:BlockDiagram2}). To do this, and still to ensure proper ``floating'' placement of tables, use the environment \textbf{figure*} to enclose the figure and its caption. And don't forget to end the environment with {figure*}, not {figure}!

9\begin{figure*}[htbp]
	\centering
		\includegraphics[width=1\textwidth]{BlockDiagram2}
	\caption{A sample black and white graphic (.jpg format) that needs to span two columns of text.}
	\label{fig:BlockDiagram2}
\end{figure*}

\subsection{Math Equations}
You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of
the three are discussed in the next sections.

\subsubsection{Inline (In-text) Equations}
A formula that appears in the running text is called an
inline or in-text formula.  It is produced by the
\textbf{math} environment, which can be
invoked with the usual \texttt{{\char'134}begin. . .{\char'134}end}
construction or with the short form \texttt{\$. . .\$}. You
can use any of the symbols and structures,
from $\alpha$ to $\omega$, available in
\LaTeX \cite{Lamport:LaTeX}; this section will simply show a
few examples of in-text equations in context. Notice how
this equation: \begin{math}\lim_{n\rightarrow \infty}x=0\end{math},
set here in in-line math style, looks slightly different when
set in display style.  (See next section).

\subsubsection{Display Equations}
A numbered display equation -- one set off by vertical space
from the text and centered horizontally -- is produced
by the \textbf{equation} environment. An unnumbered display
equation is produced by the \textbf{displaymath} environment.

Again, in either environment, you can use any of the symbols
and structures available in \LaTeX; this section will just
give a couple of examples of display equations in context.
First, consider the equation, shown as an inline equation above:
\begin{equation}\lim_{n\rightarrow \infty}x=0\end{equation}
Notice how it is formatted somewhat differently in
the \textbf{displaymath}
environment.  Now, we'll enter an unnumbered equation:
\begin{displaymath}\sum_{i=0}^{\infty} x + 1\end{displaymath}
and follow it with another numbered equation:
\begin{equation}\sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f\end{equation}
just to demonstrate \LaTeX's able handling of numbering.

\subsection{Theorem-like Constructs}
Other common constructs that may occur in your article are
the forms for logical constructs like theorems, axioms,
corollaries and proofs.  There are
two forms, one produced by the
command \texttt{{\char'134}newtheorem} and the
other by the command \texttt{{\char'134}newdef}; perhaps
the clearest and easiest way to distinguish them is
to compare the two in the output of this sample document:

This uses the \textbf{theorem} environment, created by
the\linebreak\texttt{{\char'134}newtheorem} command:
\newtheorem{theorem}{Theorem}
\begin{theorem}
Let $f$ be continuous on $[a,b]$.  If $G$ is
an antiderivative for $f$ on $[a,b]$, then
\begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
\end{theorem}

The other uses the \textbf{definition} environment, created
by the \texttt{{\char'134}newdef} command:
\newdef{definition}{Definition}
\begin{definition}
If $z$ is irrational, then by $e^z$ we mean the
unique number which has
logarithm $z$: \begin{displaymath}{\log e^z = z}\end{displaymath}
\end{definition}

Two lists of constructs that use one of these
forms is given in the
\textit{Author's  Guidelines}.

There is one other similar construct environment, which is
already set up
for you; i.e. you must \textit{not} use
a \texttt{{\char'134}newdef} command to
create it: the \textbf{proof} environment.  Here
is a example of its use:
\begin{proof}
Suppose on the contrary there exists a real number $L$ such that
\begin{displaymath}
\lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
\end{displaymath}
Then
\begin{displaymath}
l=\lim_{x\rightarrow c} f(x)
= \lim_{x\rightarrow c}
\left[ g{x} \cdot \frac{f(x)}{g(x)} \right ]
= \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
\frac{f(x)}{g(x)} = 0,
\end{displaymath}
which contradicts our assumption that $l\neq 0$.
\end{proof}

Complete rules about using these environments and using the
two different creation commands are in the
\textit{Author's Guide}; please consult it for more
detailed instructions.  If you need to use another construct,
not listed therein, which you want to have the same
formatting as the Theorem
or the Definition \cite{salas:calculus} shown above,
use the \texttt{{\char'134}newtheorem} or the
\texttt{{\char'134}newdef} command,
respectively, to create it.

\subsection{A {\secit Caveat} for the \TeX\ Expert}
Because you have just been given permission to
use the \texttt{{\char'134}newdef} command to create a
new form, you might think you can
use \TeX's \texttt{{\char'134}def} to create a
new command: \textit{Please refrain from doing this!}
Remember that your \LaTeX\ source code is primarily intended
to create camera-ready copy, but may be converted
to other forms -- e.g. HTML. If you inadvertently omit
some or all of the \texttt{{\char'134}def}s recompilation will
be, to say the least, problematic.

\subsection{Citations}
Citations to articles \cite{bowman:reasoning,
clark:pct, braams:babel, herlihy:methodology},
conference proceedings \cite{clark:pct} or
books \cite{salas:calculus, Lamport:LaTeX} listed
in the Bibliography section of your
article will occur throughout the text of your article.
You should use BibTeX to automatically produce this bibliography;
you simply need to insert one of several citation commands with
a key of the item cited in the proper location in
the \texttt{.tex} file \cite{Lamport:LaTeX}.
The key is a short reference you invent to uniquely
identify each work; in this sample document, the key is
the first author's surname and a
word from the title.  This identifying key is included
with each item in the \texttt{.bib} file for your article.

The details of the construction of the \texttt{.bib} file
are beyond the scope of this sample document, but more
information can be found in the \textit{Author's Guide},
and exhaustive details in the \textit{\LaTeX\ User's
Guide} \cite{Lamport:LaTeX} and in various online source.\footnote{See e.g. \url{http://www.bibtex.org/}.}

This article shows only the plainest form
of the citation command, using \texttt{{\char'134}cite}.
This is what is stipulated in the SIGS style specifications.
No other citation format is endorsed or supported.

\subsection{Blind Review}
A convenient flag has been provided that will allow you to easily mask any text or reference that could be used to identify you as the author. To enable the feature, comment the line \texttt{\textbackslash usepackage{anonymize}} and uncomment the \texttt{\textbackslash usepackage[blind]{anonymize}} lines near the top of the file. When \texttt{\textbackslash usepackage[blind]{anonymize}} is enabled, anonymized text will be blackened out and masked bibliography names and titles will be anonymised. For example, the following will cause the package to generate a blind review version of the manuscript.\\

\texttt{\% \textbackslash usepackage{anonymize}}  \\
\texttt{\textbackslash usepackage[blind]{anonymize}} \\

The following configuration will cause the manuscript to disable masking text and produce the version of the manuscript for publication.

\texttt{\textbackslash usepackage{anonymize}} \\
\texttt{\%\textbackslash usepackage[blind]{anonymize}} \\

\subsubsection{Masking text}
To mask text that may identify you, place the text you want to hide inside the \textbackslash anonymize function. If you have enabled the blind review feature, \anonymize{you will not be able to read this text}. Change back to the non-blind mode when you are ready to publish.

\subsubsection{Masking publications}
In order to mask your publications,  you will need to make a copy of your personal references, using the second version with a key name adding \texttt{-hidden}. For example, if your reference key is \texttt{myotherpublication}, make a copy called \texttt{myotherpublication-hidden} that has text displayed how you would like it displayed in blind review mode.  Wrap your reference name with the \textit{anoncite} function. For example, to make \texttt{{\char'134}cite\{mypublication\}} anonymous in the blind version, use the following instead.\\
\texttt{{\char'134}cite\{{\char'134}anoncite\{mypublication\}\}}.
You will note that \cite{\anoncite{mypublication}} and \cite{\anoncite{myotherpublication}} were written by me, so in blind mode, the identifying parts will be suppressed.

\subsection{Links}

Links to URLs can be included using the \texttt{{\char'134}url} command. This will generate a clickable link like this: \url{https://www.nime2020.bcu.ac.uk}.

\section{Conclusions}
This paragraph will end the body of this sample document.
Remember that you might still have Acknowledgments or
Appendices; brief samples of these
follow.  There is still the Bibliography to deal with; and
we will make a disclaimer about that here: with the exception
of the reference to the \LaTeX\ book, the citations in
this paper are to articles which have nothing to
do with the present subject and are used as
examples only.
%\end{document}  % This is where a 'short' article might terminate

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
This section is optional; it is a location for you
to acknowledge grants, funding, editing assistance and
what have you.  In the present case, for example, the
authors would like to thank Gerald Murray of ACM for
his help in codifying this \textit{Author's Guide}
and the \textbf{.cls} and \textbf{.tex} files that it describes.

\section{Ethical Standards}
To ensure objectivity and transparency in research and to ensure that accepted principles of ethical and professional conduct have been followed, authors should include a section “Ethical Standards” before the References, including (if relevant): information regarding sources of funding, potential conflicts of interest (financial or non-financial), informed consent if the research involved human participants, statement on welfare of animals if the research involved animals.

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}

	\bibliography{nime-references}

% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
\appendix
%Appendix A
\section{Headings in Appendices}
The rules about hierarchical headings discussed above for
the body of the article are different in the appendices.
In the \textbf{appendix} environment, the command
\textbf{section} is used to
indicate the start of each Appendix, with alphabetic order
designation (i.e. the first is A, the second B, etc.) and
a title (if you include one).  So, if you need
hierarchical structure
\textit{within} an Appendix, start with \textbf{subsection} as the
highest level. Here is an outline of the body of this
document in Appendix-appropriate form:
\subsection{Introduction}
\subsection{The Body of the Paper}
\subsubsection{Type Changes and  Special Characters}
\subsubsection{Math Equations}
\paragraph{Inline (In-text) Equations}
\paragraph{Display Equations}
\subsubsection{Citations}
\subsubsection{Tables}
\subsubsection{Figures}
\subsubsection{Theorem-like Constructs}
\subsubsection*{A Caveat for the \TeX\ Expert}
\subsection{Conclusions}
\subsection{Acknowledgments}
\subsection{Additional Authors}
This section is inserted by \LaTeX; you do not insert it.
You just add the names and information in the
\texttt{{\char'134}additionalauthors} command at the start
of the document.
\subsection{References}
Generated by bibtex from your ~.bib file.  Run latex,
then bibtex, then latex twice (to resolve references)
to create the ~.bbl file.  Insert that ~.bbl file into
the .tex source file and comment out
the command \texttt{{\char'134}thebibliography}.

% This next section command marks the start of
% Appendix B, and does not continue the present hierarchy
\section{More Help for the Hardy}
The sig-alternate.cls file itself is chock-full of succinct
and helpful comments.  If you consider yourself a moderately
experienced to expert user of \LaTeX, you may find reading
it useful but please remember not to change it.

%%% Place this command where you want to balance the columns on the last page. 
%\balancecolumns

% That's all folks!
\end{document}

### 2020-01-03 paper.tex
Updates from Overleaf

@@
 \colorbox{green!=30}{Finalize ear,generate,make survey.} The survey will be sent out. I know a few producers who are willing to do this.
-3 algorithms, 3 categories, 10 samples for each algorithm and category pair, 2 seconds to listen to each sample-> 3 minutes for listening
-I imagine survey will be around 5-6 minutes long.
+3 algorithms, 3 categories, 10 samples for each algorithm and category pair, 2 seconds to listen to each sample-> 3 minutes for listening\\
+With those numbers I imagine survey will be around 5-6 minutes long.
 \subsubsection{Contrasting Ear Scores With Survey Results}
@@
 \colorbox{blue!=30}{Should this section be at the start of the paper?Appendix?}\\
-talk about  categories, sources, dataprocessing. 
+talk about  categories, sources, data processing. 
 Code for the data processing is written, I need to download the no-copyright sounds, run the code and host the results. 
@@
 \section{Future Work}
-\colorbox{blue!=30}{Should really think this through}
+\colorbox{blue!=30}{Need to think about this more}
 \begin{itemize}
@@
     \item Making the synth's sound range more diverse while maintaining speed and efficiency
+    \item Can our approach be used for VSTs?
 \end{itemize}
+%ACKNOWLEDGMENTS are optional
+\section{Acknowledgments}
+This section is optional; it is a location for you
+to acknowledge grants, funding, editing assistance and
+what have you.  In the present case, for example, the
+authors would like to thank Gerald Murray of ACM for
+his help in codifying this \textit{Author's Guide}
+and the \textbf{.cls} and \textbf{.tex} files that it describes.
+\section{Ethical Standards}
+To ensure objectivity and transparency in research and to ensure that accepted principles of ethical and professional conduct have been followed, authors should include a section “Ethical Standards” before the References, including (if relevant): information regarding sources of funding, potential conflicts of interest (financial or non-financial), informed consent if the research involved human participants, statement on welfare of animals if the research involved animals.
+
+\appendix
+%Appendix A
+\section{section A}
+In case I need an appendix
+\subsection{Example Subsection}
+\section{Section B}
+The sig-alternate.cls file itself is chock-full of succinct
+and helpful comments
+
+%%% Place this com
 \bibliographystyle{abbrv}

### 2020-01-03 paper.tex
Updates from Overleaf

@@
 \end{table}
-
+\subsection{Data And Project Replication}
+\colorbox{green!=30}{One last thing to do, will take a 1 day}\\
+\colorbox{green!=30}{need to finalize database}\\
+\colorbox{blue!=30}{Should this section be at the start of the paper?The End? Appendix?}\\
+talk about  categories, sources, data processing. 
+Code for the data processing is written, I need to download the no-copyright sounds, run the code and host the results. 
+Give link for people to download it, show where to find the scripts for database expansion.
 \section{Implementation}
@@
 \includegraphics[width=0.8\linewidth]{images/cnn_ear.png}
-\caption{Model working well on a test set}
+\caption{confusion matrix of the model working well on a test set. \colorbox{green!=30}{will be updated with new ear.}}
 \label{fig:ok ear}
@@
 \subsection{General Methods}
+\colorbox{green!=30}{The next 3 sections will be modified heavily after the ear is updated.}
 \subsubsection{Random Generation}
-To establish a benchmark, we seek to establish the likelihood of generating samples of each category if we generate programs for various stack sizes by random selection of parameters. \\
+To establish a benchmark, we seek to establish the likelihood of generating samples of each category if we generate programs for various stack sizes by random selection of parameters.
+We have observed a bias in generations as indicated in figure \ref{gens}.\\
 \begin{figure}[H]
@@
 \end{figure}
-\subsubsection{Multivariate Normal}
+\subsubsection{Multivariate Distribution Sampling}
 Some success and extremely fast and scalable once the parameter space is calculated.
@@
 \colorbox{green!=30}{pending section \ref{survey}}
-\section{Code and Database}
-\colorbox{green!=30}{One last thing to do, will take a 1 day}\\
-\colorbox{blue!=30}{Should this section be at the start of the paper?Appendix?}\\
-talk about  categories, sources, data processing. 
-Code for the data processing is written, I need to download the no-copyright sounds, run the code and host the results. 
-Give link for people to download it, show where to find the scripts for database expansion.
+
 \section{Summary and Conclusions}
@@
     \item Our methodology was successful in generating novel examples of some percussion categories.
-    \item With the right implementation of DSP methods to create a synth, Genetic search is viable for finding  desired programs and parameters.
+    \item Reiterate the importance of ear.
+    \item There are potential benefits (e.g: pedagogical, software engineering, efficiency, data search, generality of solution, etc.) to separate some audio generation tasks into multiple parts, rather than throwing everything at some neural net.
+    \item With the right implementation of DSP methods to create a synth, Genetic search (viewed as too slow by previous work) is viable for finding  desired programs and parameters.
+    \item Neural nets are function approximators. You don't need them if the actual function is understandable and simple...(but is our task simple enough? how do I prove it?)
     \item When possible, using DSP methods instead of NNs is preferable in many ways(speed,computation,hardware requirements).\\

### 2020-01-13 paper.tex
Updates from Overleaf

@@
 \conferenceinfo{NIME'20,}{July 21-25, 2020, Royal Birmingham Conservatoire, ~~~~~~~~~~~~ Birmingham City University, Birmingham, United Kingdom.}
-\title{Rapid, (semi-?)Supervised Generation of Novel Percussive Sounds With A Tractable Virtual Synthesizer}
+\title{Rapid, (semi-?)Supervised Generation of Novel Percussive Sounds with a Tractable Virtual Synthesizer}
 
@@
 We have implemented several methods of feature extraction and successfully separated different drum categories in interesting ways. 
-\todo[inline, color=green!30]{is this the right place to show off some t-sne graphs of how various feature extraction methods seperated drum categories?}
+\todo[inline, color=green!30]{is this the right place to show off some t-sne graphs of how various feature extraction methods separated drum categories?
+Or take the probability vector assigned to samples by the ear and t-sne that?
+it might be a cool way to visualize show how well the ear is performing}
 A common pitfall of most feature extraction methods implemented is that they do not consider the temporal trends within the audio, making them highly susceptible to errors when evaluating audio that should not belong to any of the categories.\\
@@
 \subsubsection{Multivariate Distribution Sampling}
-Some success and extremely fast and scalable once the parameter space is calculated.
-A well known issue with this apporach is that the parameter space for virtual synthesizers are often neither differenciable nor gaussian \cite{esling2019universal} (a couple more papers also talked about this, I have to find them).
+\colorbox{green!=40}{go over the math quick}\\
+\colorbox{green!=40}{add some graphs showing learned params}\\
+\colorbox{green!=40}{add graphs of learned parameters showing why it's not perfect}\\
+This method is extremely fast and scalable once the parameter space is calculated.
+But success is limited due to well known issues with this approach.
+Notably that the parameter space for virtual synthesizers are often neither differentiable nor Gaussian.
+\cite{esling2019universal} (a couple more papers also talked about this, \colorbox{green!=40}{I have to look them up}).
 Currently our parameters are array indices mapping to different values for Synth components.
@@
 \end{subfigure}
-\caption{\colorbox{green!=40}{todo}Graphs showing the effectiveness of this method for producing chosesn categories in under a minute}
+\caption{\colorbox{green!=40}{todo}Graphs showing the effectiveness of this method for producing chosen categories in under a minute}
 \label{fig:multi-graphs}
@@
 \subsubsection{Evolutionary Search}
-Implemented evolutionary search using DEAP \citep{DEAP_JMLR2012}.
+We implemented evolutionary search using DEAP \citep{DEAP_JMLR2012}.
 A parameter set is assumed to be an individual with each parameter being its genes.

### 2020-01-31 paper.tex
Updates from Overleaf

@@
 % Uncomment only one of the ones below
-\usepackage{anonymize} 		   %Uncomment this line to publish
-% \usepackage[blind]{anonymize}%Uncomment this line for blind review
+% \usepackage{anonymize} 		   %Uncomment this line to publish
+\usepackage[blind]{anonymize}%Uncomment this line for blind review
 \usepackage[utf8]{inputenc}
@@
 \conferenceinfo{NIME'20,}{July 21-25, 2020, Royal Birmingham Conservatoire, ~~~~~~~~~~~~ Birmingham City University, Birmingham, United Kingdom.}
-\title{Rapid, (semi-?)Supervised Generation of Novel Percussive Sounds with a Tractable Virtual Synthesizer}
+\title{Percussive Sound Generation with Virtual Listeners and Modular Synthesizers}
 
@@
 \begin{abstract}
-With the generation of novel, high quality, one shot percussive sounds as our end goal, we implemented a set of modular software components utilized to form a pipeline for guided generation of sounds.
-The most crucial of these components are a "virtual ear" capable of evaluating a sound's proximity to different drum types and an efficient, tractable "virtual synthesizer" with a rich set of parameters capable of generating a wide range of sounds.\\
-We aimed to design our software such that we can utilize our components in various experimental ways; hence, in order to established an adequate level of confidence in our components, we discuss the implementation, limitations, and evaluations of the \textit{virtual synthesizer} and \textit{virtual ear}.
-Next, we present our findings and assessments in regards to the three different methodologies utilized for the generative process of percussive sounds:  \begin {enumerate*} [label=(\roman*)]
-\item random generation \item multivariate distribution sampling and \item evolutionary search.\\
-\end {enumerate*} 
-Additionally, as we observed a general lack of copyright-free percussive sample-packs as well as a lack of unified approach for obtaining such a data-set by fellow researchers \cite{aouameur2019neural,ramires2019timbfeat}, we aim to ameliorate the issue by presenting a copyright free sample-pack of categorized percussion sounds.
-Furthermore, we have included in our project source code \footnote{\url{https://github.com/imilas/Synths_Stacks_Search}} a set of scripts to further expand the sample pack via royalty free sources.
+Digital sound artists often require a variety of percussive samples for their music.
+We observed a lack of copyright-free one-shot percussive sample-packs for purposes of research and music creation.
+Yet for more than two decades, research involving digital synthesis, genetic search, and neural networks has been used to invent and approximate novel sounds.
+Our goal is to generate one-shot percussive samples by leveraging modern AI technologies alongside scalable signal generation methods.
+Could we generate novel drum sounds through machine learning, heuristic search and modular synthesizers?
+We centered our approach around the combination of two central components: \begin {enumerate*} [label=(\roman*)] \item a "virtual ear" capable of learning key features of various sound groups and evaluating the proximity of unheard sounds to desired sets and \item a dynamic virtual synthesizer with a rich set of tractable parameters\end{enumerate*}.
+We present a generative pipeline that utilizes robust digital signal processing methods and is guided by supervised learning and genetic search towards generation of novel, high-quality, one-shot percussive sounds.
+We present our findings and measurements of the various approaches taken towards the implementation of the virtual ear, virtual synthesizer, and generative pipeline; hoping to expose the advantages and shortcomings of the employed methodologies and their practicality in future works via a clear demonstration of their capabilities relative to our stated goal.
+We also discuss and share our curated dataset of sounds along with our codebase \footnote{\url{https://github.com/imilas/Synths_Stacks_Search}} which can be used for its further expansion.
+
 \keywords{drum, percussion, synthesis, MIR, ML, genetic, search}
@@
 \end{itemize}
-Following the Unix Philosophy \cite{gancarz2003linux}, our components are designed with modularity and parallelizability in mind.
-This allows each component to be debugged, modified and improved without requiring modifications in other components; while additionally increasing the scalability and speed of experiments.
+Our components are designed with modularity and parallelizability in mind.
+This allows each component to be debugged, modified and improved without requiring modifications in other components; additionally increasing the scalability and speed of experiments.
 Section \ref{impl} contains further discussion of the components as well as the code that glues the project together.\\ 
@@
 As stated before, our work presents a rapid approximation of percussion sounds with no previous knowledge about the sonic capabilities of our virtual synthesizer, exploring the actual parameter space rather than its latent representation.
+
+\subsection{Data And Project Replication}
+\label{data}
+\colorbox{green!=30}{One last thing to do, will take a 1 day}\\
+\colorbox{green!=30}{need to finalize database}\\
+\colorbox{blue!=30}{Should this section be at the start of the paper?The End? Appendix?}\\
+talk about  categories, sources, data processing. 
+Code for the data processing is written, I need to download the no-copyright sounds, run the code and host the results. 
+Give link for people to download it, show where to find the scripts for database expansion.
+\section{Implementation}
+\label{impl}
+\subsection{Virtual Synthesizer}
+We used the python based Pippi library for sound generation\footnote{https://github.com/luvsound/pippi}.
+This library uses a C back-end and focuses on fast offline generation of audio signals.
+In our implementation, a synthesizer can have any number of submodules.
+The parameters that deterministically dictate the output signal of the submodule as well as the range of values each paramter can take are shown in table 1 \ref{table:1} We call this number the \textit{stack size}.
+For the range of parameters each submodule can take.
+We call the sets of parameters that characterize a Synth's submodules a \textit{program} (analogous to a preset).
+Each submodule can make an audio signal with the length of 0.1-1 second.
+If a Synth has a stack size of more than 1, these audio signals are overlapped and the total amplitude is normalized.\\
 \begin{table}[h!]
@@
 HP filter Cuttoff & 0-20000 & -\\
-LP filter Cuttoff & HP-20000 & never lower than HP cutoff\\
+LP filter Cuttoff & 20000-HP & never lower than HP cutoff\\
 Filter Order & 4,8,16 & butterworth filter order \\
@@
 \end{tabular}}
-\caption{Synthesizer Submodule Parameters}
+\caption{Synthesizer Submodule Parameters.
+Despite the simplicity of the paramters and our efforts at constraining the ranges, the number of paramters that can be randomly chosen for each submodule is in the order of $10^{15}$ }
 \label{table:1}
 \end{table}
-\subsection{Data And Project Replication}
-\colorbox{green!=30}{One last thing to do, will take a 1 day}\\
-\colorbox{green!=30}{need to finalize database}\\
-\colorbox{blue!=30}{Should this section be at the start of the paper?The End? Appendix?}\\
-talk about  categories, sources, data processing. 
-Code for the data processing is written, I need to download the no-copyright sounds, run the code and host the results. 
-Give link for people to download it, show where to find the scripts for database expansion.
-\section{Implementation}
-\label{impl}
-
-\subsection{Virtual Synthesizer}
-We used the python based Pippi library for sound generation\footnote{https://github.com/luvsound/pippi}.
-This library uses a C back-end and focuses on fast offline generation of audio signals.
-In our implementation, a synthesizer can have any number of submodules.
-We call this number the \textit{stack size}.
-See table \ref{table:1} for the range of parameters each submodule can take.
-We call the sets of parameters that characterize a Synth's submodules a \textit{program} (analogous to a preset).
-Each submodule can make an audio signal with the length of 0.1-1 second.
-If a Synth has a stack size of more than 1, these audio signals are overlapped and the total amplitude is normalized.\\
-
 \begin{figure}[h!]
@@
 \subsection{The Ear}
-We defined an ear as any method of evaluating a piece of audio, capable of "listening" to a piece of audio and giving it a score (or a list of scores) based on how well it satisfies certain criteria.
-Since in this work we are mainly focused on percussive generation, what we require from the ear is to give us probabilities of an audio sample belonging to various sound (drum and none-drum) categories.
-As our synthesizer outputs are deterministic for all programs, allowing us to associate the categorical probabilities of each sound with the program that generated it; navigating our synthesis towards parameters which give us the desired sonic output.\\
-%  The most basic representation of a piece of digital audio is via list of numbers and a sampling-rate.
-For simplicity, we fix the sampling rate to 41,000 per second across all components of this project.
-An array representation of audio is the representation of the audio within the time domain.
-More commonly, the frequency domain is used for MIR tasks.
-We have implemented several methods of feature extraction and successfully separated different drum categories in interesting ways. 
-\todo[inline, color=green!30]{is this the right place to show off some t-sne graphs of how various feature extraction methods separated drum categories?
-Or take the probability vector assigned to samples by the ear and t-sne that?
-it might be a cool way to visualize show how well the ear is performing}
-A common pitfall of most feature extraction methods implemented is that they do not consider the temporal trends within the audio, making them highly susceptible to errors when evaluating audio that should not belong to any of the categories.\\
-Analysis of the frequency content of a piece of audio using windowing functions is a common MIR procedure.
-Care must be taking such that information critical to percussion categorization such as envelope and temporal changes are not lost in this process.
-For example, we do not want a reversed kick sample to be labeled as a kick, or even a drum, even if it has the correct frequency content.
-There are two interconnected temporal trends to consider:
-\begin{itemize}
-    \item Change in amplitude within each frequency bin. Harder to measure and utilize and possibly not as important for our purposes, considering the short length of our samples.
-    \item Overall amplitude change within a sample. Closely linked to ADSR\\. 
-\end{itemize}{}
-Temporal trends may be deduced from a spectrum representation of sound.
-A convolution net trained on our drum dataset, combined with an algorithm ADSR extraction algorithm led to an ear which can reliably reject junk data and samples with inappropriate wave-shapes.
-\todo[inline,color=green!30]{This paragraph is lying, I haven't done the ADSR algorithm part yet.
-Highest priority after writing this paper.}
+What we refer to as an "ear" is any method of evaluating a piece of audio, capable of "listening" to a piece of audio and giving it a score (or a list of scores) based on how well it satisfies certain criteria.
+Since in this work we are mainly focused on percussive generation, what we require from the ear is to give us probabilities of an audio sample belonging to various categories.
+As our synthesizer outputs are deterministic for all programs, the ear's evaluations would allow us to associate the categorical probabilities of each sound with the program that generated it.
+In section \ref{gens} we discuss how these scores were used for navigation of our synthesis towards parameters which give us the desired sonic output.\\
+ With our dataset \ref{data} of labeled drum sounds, we can confidently categorized unlabeled drum sounds, given that we know they are drum sounds.
+However, a major hurdle towards the implementation of a "drum from non-drum" recognizing ear is that the set of sounds that are not percussive is infinite.
+Since we can represent different drum groups using our categorized data (closed set), but effective aggregation and feature extraction of non-drum sound data is not practical.
+We hypothesize that $Task\,1$ falls within the domain of "Open Set Recognition"\cite{scheirer2012toward}.
+"Open Set Recognition" problem arises when a set that is being categorized has practically infinite diversity, often making learning-by-example impossible without further domain knowledge.
+While ML techniques can be effective with classification of a closed set of examples, the classification of an infinite set cannot be reliably achieved with current ML methodologies\cite{geng2018recent,mundt2019open}.
+\\
+  In our case, as discussed in section \ref{survey}, the majority of sounds generated by the synth do not resemble percussion.
+Even if we only consider 1 second long sounds made with a single stacked synth, the set of synthesizer parameters (and we assume, the sound generated by these paramters) is extremely large.
+In our case, we determined that there are 2 steps necessary to effectively extract percussive sounds from the randomly generated noise from the virtual synthesizer:
+  \begin{enumerate}
+   \item  $Task\,1$: Binary separation of sounds with percussive features from non-percussive sounds.
+   \item $Task\,2$: Given confidence that of the sound being categorized is percussive, categorizing the type of drum.
+ \end{enumerate}
+We are interested in extracting generalize features that can be applied in other audio domains.
+In this work we rely entirely on Fast Fourier Transform (FFT) and by extension Short-time Fourier Transforms (STFT) for feature extraction.
+Using FFT, a signal can be represented by a vector with each index corresponding to a frequency-bin (a range of frequencies too close to be distinguishable) and the value of the index corresponding to the combined-magnitude of the frequencies within the bin.
+STFT can be employed when a more accurate representation is desired via the application of the FFT to a sliding time-window on the signal to create a matrix (a list of vectors).
+This matrix can effectively represent the frequencies present in the signal at each time step, given the right window-length and hop-size (how much the window is shifted at each time-step).\\
+Various works have demonstrated effective reconstruction of signals given their STFT \cite{nawab1983signal,griffin1984signal}.
+The loss of phase information may be an issue in some domains \cite{sturmel2011signal}, however phase information has little impact on the human auditory experience.
+If the original signal can be otherwise accurately reconstructed from its STFT, perhaps further transformation and analysis of the STFT may be relied on as source of fundamental features necessary for audible signal categorization.
+Following this and in the interest of keeping the feature space small and fundamental, other methods of feature extraction which have proven effective at instrument and percussion categorization such as Spectral-Centroids \cite{schubert2004spectral} and Zero-Crossing Rates \cite{gouyon2000use} are not utilized.\\
+Using only the STFT of signals as source of feature extraction, we defined 3 transformation functions which we believe to capture important, unique attributes of percussive sounds.
+These functions were applied at training time to 1 second audio samples before being sent to a classifier.
+\begin{enumerate}
+\item Envelope Transformation: The goal of this feature is to capture the changes in loudness for the duration of the signal.
+Using STFT, we generate a matrix $M_{i \times j}$ with rows $i$ and columns $j$ corresponding to time steps and frequency bins respectively.
+With values $v_{i \times j}$ indicating the magnitude of the frequency bin $j$ at each time-step $i$.
+Information about the envelope of the signal can be extracted by summing the values of $M$ for each time-step (or row $i$), giving us a feature vector $v_i$.
+This vector is then normalized to the range of 0 to 1.
+The information contained in this vector is similar to that of a Root-Mean-Square measurement.
+\item Frequency Transformation: A static, normalized snap-shot of the the frequencies present within the audio.
+The calculation of this feature vector is similar to the envelope's, but the summation is along the frequency axis.
+Another important distinction is that since capturing an adequate frequency resolution is important for this transformation, we utilized shorter hop-sizes and wider windows.
+A Mel Scale transformation was also applied in hopes that the captured features better represent human perception of frequencies.
+\item Spectrum Transformation: This function is simply a Mel Scaled STFT with its values normalized from 0-1.
+Since this features is a 2D matrix rather than a vector, it captures more information about our signal, but requires heavier, more complex computational methods to be utilized.
+\end{enumerate}
+
 \begin{figure}[H]

### 2020-01-31 paper.tex
Updates from Overleaf

@@
 \end{table}
-\begin{figure}[h!]
+\begin{figure*}[h]
 \centering
+
 \begin{subfigure}[b]{\linewidth}
-\includegraphics[width=0.3\linewidth]{example-image-a}
-\includegraphics[width=0.3\linewidth]{example-image-b}
-\includegraphics[width=0.3\linewidth]{example-image-c}
-\caption{64 stack}\label{fig:64stack}
-\setcounter{subfigure}{0}%
+\includegraphics[width=1\linewidth]{images/ff1.pdf}
+\caption{Organic hat sample}\label{fig:64stack}
+\setcounter{subfigure}{1}%
+\includegraphics[width=1\linewidth]{images/ff2.pdf}
+\caption{Randomly generated audio with percussive qualities, resembling a tight snare}\label{fig:64stack}
+\setcounter{subfigure}{2}%
+\includegraphics[width=1\linewidth]{images/ff3.pdf}
+\caption{A randomly generated noise with a percussive envelop but non-percussive frequency features (modulated pitch)}\label{fig:64stack}
+\setcounter{subfigure}{2}%
 \end{subfigure}
 
-\begin{subfigure}[b]{\linewidth}
-\includegraphics[width=0.3\linewidth]{example-image-a}
-\includegraphics[width=0.3\linewidth]{example-image-b}
-\includegraphics[width=0.3\linewidth]{example-image-c}
-\caption{8 stacks}\label{fig:8stacl}
-\setcounter{subfigure}{1}%
-\end{subfigure}
-
-\begin{subfigure}[b]{\linewidth}
-\includegraphics[width=0.3\linewidth]{images/specplot.png}
-\includegraphics[width=0.3\linewidth]{images/specplot.png}
-\includegraphics[width=0.3\linewidth]{images/specplot.png}
-\caption{1 stack}\label{fig:1stack}
-\setcounter{subfigure}{2}%
-\end{subfigure}
-\caption{Examples of mel-spectrum representations of randomly generated samples.
-Bigger stacks give us more complex signals, but we find that even stacks of size 1 can be powerful with the right parameters.
-\colorbox{green!=40}{update this with actual spectrums}}
+\caption{Graphed representation of features extracted for 3 different samples.
+Sample $a$ is an organic hat from our database.
+sample $b$ is an example of randomly generated noise with percussive qualities that we found suitably similar to a snare sound.
+Sample $c$ is an example of a randomly generated noise where the spectrum features are necessary for proper classification.}
 \label{fig:stackspectrums}
-\end{figure}
+\end{figure*}
 
@@
 \item Frequency Transformation: A static, normalized snap-shot of the the frequencies present within the audio.
-The calculation of this feature vector is similar to the envelope's, but the summation is along the frequency axis.
+The calculation of this feature vector is similar to the envelope, but the summation is done along the frequency axis.
 Another important distinction is that since capturing an adequate frequency resolution is important for this transformation, we utilized shorter hop-sizes and wider windows.
@@
 We are interested in the small percentages of random generations that trick the ear due to coincidentally being similar to actual drums (i.e those who received a rank of 1) }
-\todo[inline, color=blue!30]{When looking for the best sounds of each category, could use ranks 2 and 3 etc. as well, however:
-\unexpanded{\unexpanded{
-\begin{itemize}
-    \item We must figure out how to penalize their parameters
-    \item The task requires even more confidence in ear,
-\end{itemize} 
-}}}
-
 \label{fig:rank portions}
 \end{figure}
+
 \subsection{How Can The Synth and Ear Interact?}
-
-\begin{figure*}[htbp]
-	\centering
-		\includegraphics[width=0.7\textwidth]{images/SSS_gen.png}
-	\caption{\colorbox{green!=40}{ This graph is bad in many ways.} but would it be worthwhile to have a \textbf{good} flowchart of 
-	the generation pipeline in the paper? }
-	\label{fig:BlockDiagram2}
-\end{figure*}
-\label{fig:generation}
-
 With our Synth and Ear in place, we can quickly generate programs for our Synth, create the corresponding audio sample and get the scores for the audio sample.
@@
 \end{figure}
-\subsubsection{Multivariate Distribution Sampling}
-\colorbox{green!=40}{go over the math quick}\\
-\colorbox{green!=40}{add some graphs showing learned params}\\
-\colorbox{green!=40}{add graphs of learned parameters showing why it's not perfect}\\
-This method is extremely fast and scalable once the parameter space is calculated.
+% \subsubsection{Multivariate Distribution Sampling}
+% This method is extremely fast and scalable once the parameter space is calculated.
 But success is limited due to well known issues with this approach.
@@
 A weighted minkowski distance \footnote{https://docs.scipy.org/doc/scipy/reference/generated/scipy.spatial.distance.minkowski.html} between the genes of an offspring and the HOF individuals may be a good measurement.\\
-A generation of $N$ individuals are initialized(randomly or using already existing ranked parameters).
+A generation of $N$ individuals are initialized randomly.
 To create the offspring generation, each generation goes through mutations and in-place gene crossovers.
@@
 If the new individuals are coming directly from previously measured high scoring parameter sets, we ensure that they cannot be directly added to HOF without going through mutations and crossovers first.\\
-
-\begin{figure}[H]
-\centering
-\begin{subfigure}[b]{\linewidth}
-\includegraphics[width=0.48\linewidth]{example-image-c}
-\includegraphics[width=0.48\linewidth]{example-image-c}
-\label{fig:1stack}
-\setcounter{subfigure}{2}%
-\end{subfigure}
-\caption{\colorbox{green!=40}{todo}Graphs showing the effectiveness of this method for producing chosesn categories in under a minute}
-\label{fig:evo-graphs}
-\end{figure}
 \subsubsection{Survey of Generated Drums}
 \label{survey}
-\colorbox{green!=30}{Finalize ear,generate,make survey.} The survey will be sent out. I know a few producers who are willing to do this.
-3 algorithms, 3 categories, 10 samples for each algorithm and category pair, 2 seconds to listen to each sample-> 3 minutes for listening\\
-With those numbers I imagine survey will be around 5-6 minutes long.
-\subsubsection{Contrasting Ear Scores With Survey Results}
-\colorbox{green!=30}{pending section \ref{survey}}
+To measure the quality of the samples produced by our pipeline, we randomly generated around 50-60 samples in the following categories: "snare","kick","hat","clap" and "other" (combination of rims,shakers, and unusal percussive sounds").
+These samples were determined to be percussive and then categorized by 4 different models (FC,CNNLSTM,E+F and AVG).
+We ensured a balanced division between samples of stack sizes 1,2 and 4 (each stack is responsible for a third samples under each category).
+Both writers then categorized these samples without knowledge of other categorizations (human or computation models).
+It's important to note that:
+\begin{itemize}
+    \item Humans had an additional category of "bad" for samples that they deemed not appropriate. 
+    \item Human's had the same categorization in 47\% of cases
+    \item The agreement between the authors and AVG was 44\% and 47\%, not significantly lower than agreement with each other. 
+    \item Of 257 samples, both authors agreed with FC, CNNLSTM, AVG and E+F respectively in 78,76,76 and 46 of cases.
+\end{itemize}
+We assess the reliability of agreement between humans and categorization models via the Fleiss' kappa coefficient.
+The value of 0 or less for this coefficient indicates no agreement beyond random chance, and the value of 1 indicating perfect agreement.
+Our kappa measurements \ref{kappa_table} lie in within the 3.5-4.5 range, indicating mild to moderate agreement between humans and machines.
+We again measure this coefficient after dropping samples that were categorized as "bad" by the authors, as samples that humans deem to be "bad" indicate a failure in phase 1 and arguably should not have been categorized by the models at all.
+Dropping of samples that both authors deemed "bad" causes 8\% reduction of our data (21 samples) and a small increase in kappa score.
+Dropping samples either reviewer deemed bad resulted in a 30\% reduction of samples and relatively large increase in kappa scores.
+\\
+\begin{center}
+\begin{table}
+
+ \begin{tabular}{||c c c c c c||} 
+ \hline
+ DropBad? & Sample Size & HvH & H+FC & H+CNN & H+ALL \\ [0.5ex] 
+ \hline
+ No & 257 &0.37 & 0.35 & 0.35 & 0.36 \\ 
+ \hline
+ Yes(if both)& 236 & 0.31 & 0.37 & 0.37 & 0.38 \\
+ \hline
+ Yes(if either)& 180 & 0.47 & 0.50 & 0.48 & 0.46 \\
+ \hline
+
+\end{tabular}
+\caption{\label{kappa_table}Table of Fleiss' kappa coefficient to measure the degree of agreement between humans (HvH), humans and FC model (H+FC), humans and CNNLSTM model and humans and all models (H+ALL)}
+\end{table}
+
+\end{center}
 
 \section{Summary and Conclusions}
-\colorbox{green!=30}{Points I want to make:}
+
 \begin{itemize}
@@
 \end{itemize}
-%ACKNOWLEDGMENTS are optional
-\section{Acknowledgments}
-This section is optional; it is a location for you
-to acknowledge grants, funding, editing assistance and
-what have you.  In the present case, for example, the
-authors would like to thank Gerald Murray of ACM for
-his help in codifying this \textit{Author's Guide}
-and the \textbf{.cls} and \textbf{.tex} files that it describes.
+
 \section{Ethical Standards}
-To ensure objectivity and transparency in research and to ensure that accepted principles of ethical and professional conduct have been followed, authors should include a section “Ethical Standards” before the References, including (if relevant): information regarding sources of funding, potential conflicts of interest (financial or non-financial), informed consent if the research involved human participants, statement on welfare of animals if the research involved animals.
-
-\appendix
-%Appendix A
-\section{section A}
-In case I need an appendix
-\subsection{Example Subsection}
-\section{Section B}
-The sig-alternate.cls file itself is chock-full of succinct
-and helpful comments
-
-%%% Place this com
+We affirm that our work follows the principles of ethical and professional conduct.
 \bibliographystyle{abbrv}

### 2020-01-31 paper.tex
Updates from Overleaf

@@
 
-\todo[inline, color=green!30]{I think it might be worthwhile to point out the potential in our work for live performance, compared to other works which use 3rd party VSTs, require pre-training and user interaction, would that be appropriate for a scientific paper?
-should it be done here or in related work?}
 \subsection{Methodology}
@@
 \label{data}
-\colorbox{green!=30}{One last thing to do, will take a 1 day}\\
-\colorbox{green!=30}{need to finalize database}\\
-\colorbox{blue!=30}{Should this section be at the start of the paper?The End? Appendix?}\\
+
 talk about  categories, sources, data processing. 
@@
 \subsection{The Ear}
+\subsubsection{Feature Extraction}
 What we refer to as an "ear" is any method of evaluating a piece of audio, capable of "listening" to a piece of audio and giving it a score (or a list of scores) based on how well it satisfies certain criteria.
@@
   In our case, as discussed in section \ref{survey}, the majority of sounds generated by the synth do not resemble percussion.
-Even if we only consider 1 second long sounds made with a single stacked synth, the set of synthesizer parameters (and we assume, the sound generated by these paramters) is extremely large.
+Even if we only consider 1 second long sounds made with a single stacked synth, the set of synthesizer parameters (and we assume, the sound generated by these parameters) is extremely large.
 In our case, we determined that there are 2 steps necessary to effectively extract percussive sounds from the randomly generated noise from the virtual synthesizer:
   \begin{enumerate}
-   \item  $Task\,1$: Binary separation of sounds with percussive features from non-percussive sounds.
-   \item $Task\,2$: Given confidence that of the sound being categorized is percussive, categorizing the type of drum.
+   \item  $Phase1\,1$: Binary separation of sounds with percussive features from non-percussive sounds.
+   \item $Phae2\,2$: Given confidence that the sound being categorized is percussive, categorizing the type of drum or percussion.
  \end{enumerate}
@@
 In this work we rely entirely on Fast Fourier Transform (FFT) and by extension Short-time Fourier Transforms (STFT) for feature extraction.
-Using FFT, a signal can be represented by a vector with each index corresponding to a frequency-bin (a range of frequencies too close to be distinguishable) and the value of the index corresponding to the combined-magnitude of the frequencies within the bin.
-STFT can be employed when a more accurate representation is desired via the application of the FFT to a sliding time-window on the signal to create a matrix (a list of vectors).
+Using FFT, a signal can be represented by a vector with each index corresponding to a frequency-bin (a range of frequencies too close to be distinguishable) and the value at each index corresponding to the combined-magnitude of the frequencies within the bin.
+STFT can be employed when a more accurate representation is desired; via the application of the FFT to a sliding time-window on the signal to create a matrix (a list of vectors).
 This matrix can effectively represent the frequencies present in the signal at each time step, given the right window-length and hop-size (how much the window is shifted at each time-step).\\
@@
 \end{enumerate}   
+\subsubsection{The Models}
+Using the described features, we trained several models for Phase 1 and 2.
+These include Fully-Connected (FC) models, Convolutional Neural Nets (CNNs) and CNN+Long Term Short Memory models (CNNLSTM).
+The task of phase 1 is to separate drums from not-drums (DrumVsNotDrum, or DVN).
+The task of phase to is to categorize drums and percussion (DrumVsDrum, or DVD).
+We kept our feature space small, making it viable to for the task of designing models and picking the right features being done on a trial and error basis.
+A summary of models utilized in our pipeline is given below:
+\begin {enumerate}
+\item FC-DVN: A small fully connected network trained on Envelope features, reaching 97\% accuracy on our test data for phase 1. 
+\item CNNLSTM-DVN: A combination of CNN and LSTM models, where the CNN model extracts higher level features that are fed temporally to an LSTM cell.
+This model is trained on spectrum data and reaches 98\% on our test set for phase 1.
+\item E+F-DVD: A fully connected model trained on a concatenation of envelope and frequency features for phase 2. Reaching 80\% accuracy for 6-way drum categorization.
+\item CNN-DVD: A deep CNN model that reaches used for phase 2. 82\% accuracy in a 6-way drum categorization. Trained on Spectrum features.
+\item FC-DVD: Fully connected 3 layer neural net with 78\% accuracy for 6-way drum categorization. Trained on Spectrum features.
+\end{enumerate}
+The number of parameters for these models were picked rather arbitrarily.
+We'd like to note that based on our anecdotal observations, the minor modifications in features played a much more significant role in the model accuracy than major parameter changes.
+Also as discussed in section \ref{survey}, despite it's marginally lower accuracy rate, the FC-DVD model has a slight but noticeable advantage in regards to matching human categorization of data.
+Likewise, Freq+Env had a much lower degree of agree-ability with humans, despite its better performance on organic drum data.
+Leading us to believe that model accuracy on test data alone cannot be relied upon when the domain of sounds being categorized is switched from organic samples to a virtual synth.
+\\
+With our models showing efficacy at categorizing organic drums vs randomly generated synth sounds, and categorizing organic drums accurately, we combine models in order to increase the efficacy of each phase and address the "open set" problem for our task.
+For phase 1, we only determine sounds as percussive if both FC-DVN and CNN-LSTM have determined it as such with over 90\% confidence.
+For the majority of our random generations, that is not the case, but if a randomly generated sound is passed this phase, our three categorizers assign their categorizations to this sound.
+These categorizers have a moderate degree of agree-ablity, as seen in \ref{survey}, but often there is not a unanimous decision.
+The Fourth method of categorization, "averaged-cat", is implemented by taking the sum of the softmax outputs of all three categorizers and use this sum to determine the category.
+\\
+These models can be combined and weighted in various ways, the confidence thresholds can be modified in order to implement "ears" with different properties.
+A glaring issue in the current implementation is the treatment of softmax outputs as a reasonable measure of a models confidence.
+For various reasons, some models tend to have much higher confidence in their scores, skewing attempts at finding a consensus.
 
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.8\linewidth]{images/cnn_ear.png}
-\caption{confusion matrix of the model working well on a test set. \colorbox{green!=30}{will be updated with new ear.}}
-\label{fig:ok ear}
-\end{figure}
-\todo[inline,color=green!30]{ will add f-measure calculations and other confidence inducing graphs (for example I have a grid of spectrums with the ear's guess vs the actual label under each spectrum, I can colorize the grid depending on whether the guess was correct or not).
-Code in the notebooks.
-After updating ear, I will make them look presentable and add them.}
-%
 % How Can The Synth and Ear Interact?
@@
 \subsection{General Methods}
-\colorbox{green!=30}{The next 3 sections will be modified heavily after the ear is updated.}
 \subsubsection{Random Generation}
-To establish a benchmark, we seek to establish the likelihood of generating samples of each category if we generate programs for various stack sizes by random selection of parameters.
+To establish a benchmark, we seek to assess the likelihood of generating samples of each category if we generate programs for various stack sizes by random selection of parameters.
 We have observed a bias in generations as indicated in figure \ref{gens}.\\
-\begin{figure}[H]
-\centering
-\begin{subfigure}[b]{\linewidth}
-\includegraphics[width=0.48\linewidth]{example-image-a}
-\includegraphics[width=0.48\linewidth]{example-image-a}
-\label{fig:1stack}
-\setcounter{subfigure}{2}%
-\end{subfigure}
-\caption{\colorbox{green!=40}{todo}Graphs showing the effectiveness of this method for producing chosesn categories in under a minute}
-\label{fig:rand-graphs}
-\end{figure}
+
 % \subsubsection{Multivariate Distribution Sampling}
@@
 \\
-\begin{figure}[H]
-\centering
-\begin{subfigure}[b]{\linewidth}
-\includegraphics[width=0.48\linewidth]{example-image-b}
-\includegraphics[width=0.48\linewidth]{example-image-b}
-\label{fig:1stack}
-\setcounter{subfigure}{2}%
-\end{subfigure}
-\caption{\colorbox{green!=40}{todo}Graphs showing the effectiveness of this method for producing chosen categories in under a minute}
-\label{fig:multi-graphs}
-\end{figure}
 
@@
 \label{survey}
-To measure the quality of the samples produced by our pipeline, we randomly generated around 50-60 samples in the following categories: "snare","kick","hat","clap" and "other" (combination of rims,shakers, and unusal percussive sounds").
+To measure the quality of the samples produced by our pipeline and the power of our models, we randomly generated around 50-60 samples in the following categories: "snare","kick","hat","clap" and "other" (combination of rims,
+shakers and unusal percussive sounds").
 These samples were determined to be percussive and then categorized by 4 different models (FC,CNNLSTM,E+F and AVG).
@@
 \begin{itemize}
-    \item Humans had an additional category of "bad" for samples that they deemed not appropriate. 
-    \item Human's had the same categorization in 47\% of cases
-    \item The agreement between the authors and AVG was 44\% and 47\%, not significantly lower than agreement with each other. 
-    \item Of 257 samples, both authors agreed with FC, CNNLSTM, AVG and E+F respectively in 78,76,76 and 46 of cases.
+    \item Humans had an additional category of "bad" for samples that they deemed not percussive. The "bad" category indicates that the sample should have been skipped in phase 1. 
+    \item With 6 categorization groups, human's had the same categorization in 47\% of cases
+    \item The agreement between the humans and AVG was 44\% and 47\%, not significantly lower than agreement with each other. 
+    \item Of 257 samples, both humans agreed with FC, CNNLSTM, AVG and E+F respectively in 78, 76, 76 and 46 of cases.
 \end{itemize}
-We assess the reliability of agreement between humans and categorization models via the Fleiss' kappa coefficient.
+We assess the reliability of agreement between humans and categorization models via the Fleiss' kappa coefficient \cite{fleiss1971measuring}.
 The value of 0 or less for this coefficient indicates no agreement beyond random chance, and the value of 1 indicating perfect agreement.
-Our kappa measurements \ref{kappa_table} lie in within the 3.5-4.5 range, indicating mild to moderate agreement between humans and machines.
+Our kappa measurements \ref{kappa_table} lie within the 3.5-4.5 range, indicating mild to moderate agreement between humans and machines.
 We again measure this coefficient after dropping samples that were categorized as "bad" by the authors, as samples that humans deem to be "bad" indicate a failure in phase 1 and arguably should not have been categorized by the models at all.
@@
 \\
+
+Possible takeaways from this survey:
+\begin{itemize}
+    \item The survey brings into question the reliability of our phase 1 models, as 30\% of the generated samples were deemed not percussive by at least 1 reviewer and 8\% by both reviewers
+    \item The task of categorizing synthetic drums is difficult.
+Survey shows that the scale of agreement within humans as well as between humans and various model combinations is moderate at best, even after removal of "bad" samples.
+While the same models can easily achieve 98+ percent accuracy when tested on organic drum samples.
+This may be a manifestation of the "open set recognition" problem.
+    \item While there is much room for improvement, our pipeline can generate and categorize drums and percussive sounds with a promising degree of success. 
+\end{itemize}
 \begin{center}
+
 \begin{table}
-
- \begin{tabular}{||c c c c c c||} 
+ \resizebox{\linewidth}{!}{\begin{tabular}{||c c c c c c c||} 
  \hline
- DropBad? & Sample Size & HvH & H+FC & H+CNN & H+ALL \\ [0.5ex] 
+ Drop Bad? & Size & HvH & H+FC & H+CNN & H+ALL & 3 models \\ [0.5ex] 
  \hline
- No & 257 &0.37 & 0.35 & 0.35 & 0.36 \\ 
+ No & 257 &0.37 & 0.35 & 0.35 & 0.36 & 33\\ 
  \hline
- Yes(if both)& 236 & 0.31 & 0.37 & 0.37 & 0.38 \\
+ if both & 236 & 0.31 & 0.37 & 0.37 & 0.38 & 33 \\
  \hline
- Yes(if either)& 180 & 0.47 & 0.50 & 0.48 & 0.46 \\
+ if either& 180 & 0.47 & 0.50 & 0.48 & 0.46 &  0.37 \\
  \hline
-
-\end{tabular}
-\caption{\label{kappa_table}Table of Fleiss' kappa coefficient to measure the degree of agreement between humans (HvH), humans and FC model (H+FC), humans and CNNLSTM model and humans and all models (H+ALL)}
+\end{tabular}}
+\caption{\label{kappa_table}Table of Fleiss' kappa coefficient to measure the degree of agreement between humans (HvH), humans with FC model (H+FC), humans with CNNLSTM model, humans with all models (H+ALL), and the 3 models }
 \end{table}
-
 \end{center}
@@
 \section{Future Work}
-\colorbox{blue!=30}{Need to think about this more}
 \begin{itemize}
@@
 \section{Ethical Standards}
-We affirm that our work follows the principles of ethical and professional conduct.
+We affirm that our work follows the principles of ethical and professional conduct. No drums were harmed in the making of this paper.
 \bibliographystyle{abbrv}

### 2020-01-31 paper.tex
Updates from Overleaf

@@
 We observed a lack of copyright-free one-shot percussive sample-packs for purposes of research and music creation.
-Yet for more than two decades, research involving digital synthesis, genetic search, and neural networks has been used to invent and approximate novel sounds.
+Yet for more than two decades research involving digital synthesis, genetic search, and neural networks has been used to invent and approximate novel sounds.
 Our goal is to generate one-shot percussive samples by leveraging modern AI technologies alongside scalable signal generation methods.
@@
 The rise of Digital Audio Workstations (DAW) \cite{leider2004digital} and Virtual Studio Technology (VST) based plug-ins \cite{tanev2013virtual} have rapidly transformed the sonic and material landscape of music production in the recent years.
-Coupled with this rise in popularity is a vast array of commercial products and services dedicated to satiating the need of amateur and professional music producers for unique sounds; most commonly via audio samples: one-shot drum samples, long sustained notes (commonly referred to as pads or textures), and loops(percussive or melodic) are common deliverables.
+Coupled with this rise in popularity is a vast array of commercial products and services dedicated to satiating the need of amateur and professional music producers for unique sounds; most commonly via audio samples: one-shot drum samples, long sustained notes (commonly referred to as pads or textures), and loops (percussive or melodic) are common deliverables.
 Two notable examples of these commercial services are \textit{loopmasters}\footnote{loopmasters.com} and \textit{splice.com}\footnote{splice.com}.
-Furthermore, VST plug-ins can emulate complex audio synthesizers and effects, which some producers may find daunting or time consuming to work with from scratch.
-In many cases, VST plug-in vendors or unaffiliated enthusiasts sell additional presets for these plugins, targeted towards producers who do not have the time or interest in creating their own.
+Furthermore, VST plug-ins can emulate complex audio synthesizers and effects which some producers may find daunting or time consuming to work with from scratch.
+In many cases VST plug-in vendors or unaffiliated enthusiasts sell additional presets for these plugins, targeted towards producers who do not have the time or interest in creating their own.
 Producers may further modify these presets until their desired sound is reached.\\
@@
 Primarily with generation of novel, one-shot audio samples but also with automated search and creation of presets for virtual synthesizers that a producer might find  interesting.
-Using the generation of short, percussive audio samples as a starting point, this project is a proof of concept for promising avenues towards our motivational goal.\\
+Using the generation of short, percussive audio samples as a starting point this project is a proof of concept for promising avenues towards our motivational goal.\\
 
@@
 \begin{itemize}
-    \item \textit{Virtual Synthesizer}:A flexible, deterministic, and tractable generator which can create audio.
+    \item \textit{Virtual Synthesizer}: A flexible, deterministic, and tractable generator which can create audio.
 The core of our implementation made use of pippi, \footnote{https://github.com/luvsound/pippi} a fast, offline focused python DSP library with a C backend.
-We additionally used the scipy \cite{jones2001scipy} library a few audio effects that we found lacking in pippi.
+We additionally used the scipy\cite{jones2001scipy} library a few audio effects that we found lacking in pippi.
     \item \textit{Virtual Ear}: An ear that returns an evaluation of an audio sample; estimating the effectiveness of an audio sample's fulfillment of a producers requirements.
-The ear's evalutations guides the generation process towards a desired path, making the implementation and training of the ear crucial to the sounds which are generated.
+The ear's evaluation guides the generation process towards a desired path, making the implementation and training of the ear crucial to the sounds which are generated.
 A particularly effective implementation was done by using a labeled set of percussive and non-percussive audio files to train a custom model (combination of a simple Convolutional Neural Net (CNN) and a custom envelope estimation algorithm), giving us a "virtual drum detector ear".
@@
 Our components are designed with modularity and parallelizability in mind.
-This allows each component to be debugged, modified and improved without requiring modifications in other components; additionally increasing the scalability and speed of experiments.
+This allows each component to be debugged, modified, and improved without requiring modifications in other components; additionally increasing the scalability and speed of experiments.
 Section \ref{impl} contains further discussion of the components as well as the code that glues the project together.\\ 
-While the main focus of this project is the generation of novel percussive sounds, our methodology indicates promising results with regards to creation of new presets for any virtual synth without the need for a-priori knowledge of the functions of its parameters (i.e the effect of parameter modulation on the sonic output).
+While the main focus of this project is the generation of novel percussive sounds our methodology indicates promising results with regards to creation of new presets for any virtual synth without the need for a-priori knowledge of the functions or its parameters (i.e the effect of parameter modulation on the sonic output).
 We also demonstrate the viability of a few lesser explored avenues for the purposes of audio synthesis and Music Information Retrieval (MIR), notably:
@@
 \item Heuristic search methods for the creation of new presets for virtual synthesizers.
-More concretely, we observed that given a virtual ear which could reliably score pieces of audio based on its resemblance to a desired category (e.g:kicks,snares,piano), we were able to rapidly search the parameters of a virtual synthesizer and create numerous parameter-sets (i.e presets) which resemble our desired category of sounds.
+More concretely, we observed that given a virtual ear which could reliably score pieces of audio based on its resemblance to a desired category (e.g: kicks, snares, piano) we were able to rapidly search the parameters of a virtual synthesizer and create numerous parameter-sets (i.e presets) which resemble our desired category of sounds.
 \item The viability of virtual synthesizers based on Digital Signal Processing (DSP) methods for fast, unsupervised creation of novel audio, discussed in more detail in section \ref{related}. \\
@@
 Numerous deep, neural network models have been proposed and utilized for the purpose of signal generation in recent years.
-WaveGans and WaveNet have been subject to significant improvements and experiments since their proposal \colorbox{green!=40}{\cite{nsynth2017} + Many more references to be added.} Even more recently, Variational AutoEncoders (VAE's) have been utilized for generation of short percussive samples \cite{aouameur2019neural,ramires2019timbfeat}.
-In this work however, we opt to use digital signal processing methods to create a virtual synthesizer for the generation of audio signals, as it provides several unique advantages:
+WaveGans and WaveNet have been subject to significant improvements and experiments since their proposal \colorbox{green!=40}{\cite{nsynth2017} + Many more references to be added.} Even more recently Variational AutoEncoders (VAE's) have been utilized for generation of short percussive samples \cite{aouameur2019neural,ramires2019timbfeat}.
+In this work however, we opt to use digital signal processing methods to create a virtual synthesizer for the generation of audio signals as it provides several unique advantages:
 \begin{enumerate}[label=\roman*]
-  \item Fast, offline rendering of audio with no relience on GPU, currently not possible with state of the art models such as parallel WaveGan \cite{yamamoto2019parallel} and parallell WaveNet \cite{oord2017parallel}.
+  \item Fast, offline rendering of audio with no reliance on GPU: Currently not possible with state of the art models such as parallel WaveGan \cite{yamamoto2019parallel} and parallel WaveNet \cite{oord2017parallel}.
   \item Rendering at high sampling rates: Performance speed being a common issue, the standard sampling rate in most audio generation work utilizing neural networks appears to be under 24 khz \cite{yamamoto2019parallel,oord2017parallel,aouameur2019neural,ramires2019timbfeat}.
-However, a significant number of untrained human ears can detect a change in quality of audio between sampling rates of 192 khz and the industry standard of 44.1 khz \cite{reiss2016meta}, with a dramatic increase in quality detection after training.
-Therefore we can safely assume that most producers would prefer their audio samples have sampling rates of 44.1 khz or higher.
+However, a significant number of untrained human ears can detect a change in quality of audio between sampling rates of 192 khz and the industry standard of 44.1 khz \cite{reiss2016meta} with a dramatic increase in quality detection after training.
+Therefore we can safely assume that most producers would prefer their audio samples to have sampling rates of 44.1 khz or higher.
   \item Neural networks are often viewed as unexplainable black box solutions.
 Some models such as VAE's can learn an underlying latent space of parameters and capture the "essence" of the different labels in a dataset.
-However, these spaces are learned in an unsuperv manner and must be manually analysed, perhaps extensively, before they can be understood \cite{esling2018generative}.
+However, these spaces are learned in an unsupervised manner and must be manually analysed, perhaps extensively, before they can be understood \cite{esling2018generative}.
 The use of a virtual synthesizer for audio generation makes our parameters readily understandable and easily modifiable.
@@
 \cite{yee2018automatic} used LSTM and genetic algorithms to find the exact parameters used to create a group of sounds.
-The sounds approximated were made by the same virtual synthesizer, not an external source; making the eventual replication certain, even with random search.
-Since this work more focused on pads and textures rather than drums, feature matching in this also appears to not be concerned with the envelope of the sounds, but rather the frequency content within arbitrary time windows.
+The sounds approximated were made by the same virtual synthesizer, not an external source; making the eventual replication certain even with random search.
+Since this work more focused on pads and textures rather than drums, feature matching in this also appears to not be concerned with the envelope of the sounds but rather the frequency content within arbitrary time windows.
 Yet another recent, impressive work by Esling et al.
@@
 \label{data}
-
-talk about  categories, sources, data processing. 
-Code for the data processing is written, I need to download the no-copyright sounds, run the code and host the results. 
-Give link for people to download it, show where to find the scripts for database expansion.
+Our data is a large set of drum samples aggregated from personal libraries, free drum kits from sampleswap \footnote{https://sampleswap.org/} which we further processed to suit our categories, and a large set of drum sounds aggregated from royalty free sources such as musicradar \footnote{https://www.musicradar.com/}.
+We will make our dataset of free-drum sounds available for download.
+The scripts used to download and process royalty free samples will also be made available.
+Further information about downloading our dataset can be found on the project's github page.
+\\
+Our drum categories are claps, hats, kicks, rims/other, shakers, snares, mid-toms and high-toms.
+Other categories are chopped guitars, chopped pianos and stacks (randomly generated synth noise), utilized for learning percussive vs not-percussive sounds.
+Some notes about our dataset:
+\begin{itemize}
+\item Of the 6000 drum-sounds utilized in our work, the kick, snare and hat categories have the largest share at around 20\% each, while the shaker and rim (other) categories have the smallest at 5\% combined.
+Due to this we only focused on learning from kicks, snares, toms, claps and hats for Phase 1 of training \ref{sec:ear}.
+\item For Phase 2 of training we only focused on categorizing snares, claps, kicks, hats and other (percussive sounds such as shakers, rims and unusual percussions that we couldn't categorize were grouped into this category).
+\item In order to offset bias from data imbalance during training of our models, the categorical cross entropy loss was weighted by the category sizes. 
+\item For training any given model, 80\% of our data is used for training the models and 20\% is used for testing. 
+\item We limit the size of the stack category to 50\% of the total size of our drum dataset.
+This is done in order to measure whether the features extracted can address the "Open Set Recognition" problem, which will be discussed further in section \ref{sec:ear}.
+\end{itemize}
 \section{Implementation}
@@
 This library uses a C back-end and focuses on fast offline generation of audio signals.
-In our implementation, a synthesizer can have any number of submodules.
-The parameters that deterministically dictate the output signal of the submodule as well as the range of values each paramter can take are shown in table 1 \ref{table:1} We call this number the \textit{stack size}.
-For the range of parameters each submodule can take.
-We call the sets of parameters that characterize a Synth's submodules a \textit{program} (analogous to a preset).
-Each submodule can make an audio signal with the length of 0.1-1 second.
-If a Synth has a stack size of more than 1, these audio signals are overlapped and the total amplitude is normalized.\\
+In our implementation a synthesizer can have any number of sub-modules.
+The parameters that deterministically dictate the output signal of the sub-module as well as the range of values each parameter can take are shown in table 1 \ref{table:1}.
+We call this number the \textit{stack size}.
+For the range of parameters each sub-module can take we call the sets of parameters that characterize a synth's sub-modules a \textit{program} (analogous to a preset).
+Each sub-module can make an audio signal with the length of 0.1-1 second.
+If a Synth has a stack size of more than 1 these audio signals are overlapped and the total amplitude is normalized.\\
 \begin{table}[h!]
@@
 \end{tabular}}
-\caption{Synthesizer Submodule Parameters.
-Despite the simplicity of the paramters and our efforts at constraining the ranges, the number of paramters that can be randomly chosen for each submodule is in the order of $10^{15}$ }
+\caption{Synthesizer Sub-module Parameters.
+Despite the simplicity of the parameters and our efforts at constraining the ranges, the number of parameters that can be randomly chosen for each sub-module is in the order of $10^{15}$ }
 \label{table:1}
@@
 \subsection{The Ear}
+\label{sec:ear}
 \subsubsection{Feature Extraction}
-What we refer to as an "ear" is any method of evaluating a piece of audio, capable of "listening" to a piece of audio and giving it a score (or a list of scores) based on how well it satisfies certain criteria.
-Since in this work we are mainly focused on percussive generation, what we require from the ear is to give us probabilities of an audio sample belonging to various categories.
-As our synthesizer outputs are deterministic for all programs, the ear's evaluations would allow us to associate the categorical probabilities of each sound with the program that generated it.
+What we refer to as an "ear" is any method of evaluating a piece of audio and capable of "listening" to a piece of audio and giving it a score (or a list of scores) based on how well it satisfies certain criteria.
+Since in this work we are mainly focused on percussive generation what we require from the ear is to give us probabilities of an audio sample belonging to various categories.
+As our synthesizer outputs are deterministic for all programs the ear's evaluations would allow us to associate the categorical probabilities of each sound with the program that generated it.
 In section \ref{gens} we discuss how these scores were used for navigation of our synthesis towards parameters which give us the desired sonic output.\\
- With our dataset \ref{data} of labeled drum sounds, we can confidently categorized unlabeled drum sounds, given that we know they are drum sounds.
+ With our dataset \ref{data} of labeled drum sounds we can confidently categorized unlabeled drum sounds given that we know they are drum sounds.
 However, a major hurdle towards the implementation of a "drum from non-drum" recognizing ear is that the set of sounds that are not percussive is infinite.
@@
  \end{enumerate}
-We are interested in extracting generalize features that can be applied in other audio domains.
+We are interested in extracting generalized features that can be applied in other audio domains.
 In this work we rely entirely on Fast Fourier Transform (FFT) and by extension Short-time Fourier Transforms (STFT) for feature extraction.
-Using FFT, a signal can be represented by a vector with each index corresponding to a frequency-bin (a range of frequencies too close to be distinguishable) and the value at each index corresponding to the combined-magnitude of the frequencies within the bin.
+Using FFT a signal can be represented by a vector with each index corresponding to a frequency-bin (a range of frequencies too close to be distinguishable) and the value at each index corresponding to the combined-magnitude of the frequencies within the bin.
 STFT can be employed when a more accurate representation is desired; via the application of the FFT to a sliding time-window on the signal to create a matrix (a list of vectors).
@@
 Various works have demonstrated effective reconstruction of signals given their STFT \cite{nawab1983signal,griffin1984signal}.
-The loss of phase information may be an issue in some domains \cite{sturmel2011signal}, however phase information has little impact on the human auditory experience.
+The loss of phase information may be an issue in some domains \cite{sturmel2011signal}, however, phase information has little impact on the human auditory experience.
 If the original signal can be otherwise accurately reconstructed from its STFT, perhaps further transformation and analysis of the STFT may be relied on as source of fundamental features necessary for audible signal categorization.
 Following this and in the interest of keeping the feature space small and fundamental, other methods of feature extraction which have proven effective at instrument and percussion categorization such as Spectral-Centroids \cite{schubert2004spectral} and Zero-Crossing Rates \cite{gouyon2000use} are not utilized.\\
-Using only the STFT of signals as source of feature extraction, we defined 3 transformation functions which we believe to capture important, unique attributes of percussive sounds.
+Using only the STFT of signals as source of feature extraction we defined 3 transformation functions which we believe to capture important, unique attributes of percussive sounds.
 These functions were applied at training time to 1 second audio samples before being sent to a classifier.
@@
 \item Envelope Transformation: The goal of this feature is to capture the changes in loudness for the duration of the signal.
-Using STFT, we generate a matrix $M_{i \times j}$ with rows $i$ and columns $j$ corresponding to time steps and frequency bins respectively.
-With values $v_{i \times j}$ indicating the magnitude of the frequency bin $j$ at each time-step $i$.
+Using STFT we generate a matrix $M_{i \times j}$ with rows $i$ and columns $j$ corresponding to time steps and frequency bins respectively, and with values $v_{i \times j}$ indicating the magnitude of the frequency bin $j$ at each time-step $i$.
 Information about the envelope of the signal can be extracted by summing the values of $M$ for each time-step (or row $i$), giving us a feature vector $v_i$.
@@
 \item Spectrum Transformation: This function is simply a Mel Scaled STFT with its values normalized from 0-1.
-Since this features is a 2D matrix rather than a vector, it captures more information about our signal, but requires heavier, more complex computational methods to be utilized.
+Since this features is a 2D matrix rather than a vector it captures more information about our signal but requires heavier, more complex computational methods to be utilized.
 \end{enumerate}   
@@
 Using the described features, we trained several models for Phase 1 and 2.
-These include Fully-Connected (FC) models, Convolutional Neural Nets (CNNs) and CNN+Long Term Short Memory models (CNNLSTM).
-The task of phase 1 is to separate drums from not-drums (DrumVsNotDrum, or DVN).
-The task of phase to is to categorize drums and percussion (DrumVsDrum, or DVD).
+These include Fully-Connected (FC) models, Convolutional Neural Nets (CNNs) and CNN + Long Term Short Memory models (CNNLSTM).
+The task of Phase 1 is to separate drums from not-drums (DrumVsNotDrum, or DVN).
+The task of Phase 2 is to categorize drums and percussion (DrumVsDrum, or DVD).
 We kept our feature space small, making it viable to for the task of designing models and picking the right features being done on a trial and error basis.
@@
 \begin {enumerate}
-\item FC-DVN: A small fully connected network trained on Envelope features, reaching 97\% accuracy on our test data for phase 1. 
+\item FC-DVN: A small fully connected network trained on Envelope features, reaching 97\% accuracy on our test data for Phase 1. 
 \item CNNLSTM-DVN: A combination of CNN and LSTM models, where the CNN model extracts higher level features that are fed temporally to an LSTM cell.
-This model is trained on spectrum data and reaches 98\% on our test set for phase 1.
-\item E+F-DVD: A fully connected model trained on a concatenation of envelope and frequency features for phase 2. Reaching 80\% accuracy for 6-way drum categorization.
-\item CNN-DVD: A deep CNN model that reaches used for phase 2. 82\% accuracy in a 6-way drum categorization. Trained on Spectrum features.
+This model is trained on spectrum data and reaches 98\% accuracy on our test set for Phase 1.
+\item E+F-DVD: A fully connected model trained on a concatenation of envelope and frequency features for Phase 2. Reaching 80\% accuracy for 6-way drum categorization.
+\item CNN-DVD: A deep CNN model that reaches used for Phase 2. 82\% accuracy in a 6-way drum categorization. Trained on Spectrum features.
 \item FC-DVD: Fully connected 3 layer neural net with 78\% accuracy for 6-way drum categorization. Trained on Spectrum features.
@@
 The number of parameters for these models were picked rather arbitrarily.
-We'd like to note that based on our anecdotal observations, the minor modifications in features played a much more significant role in the model accuracy than major parameter changes.
+We'd like to note that based on our anecdotal observations the minor modifications in features played a much more significant role in the model accuracy than major parameter changes.
 Also as discussed in section \ref{survey}, despite it's marginally lower accuracy rate, the FC-DVD model has a slight but noticeable advantage in regards to matching human categorization of data.
-Likewise, Freq+Env had a much lower degree of agree-ability with humans, despite its better performance on organic drum data.
-Leading us to believe that model accuracy on test data alone cannot be relied upon when the domain of sounds being categorized is switched from organic samples to a virtual synth.
+Likewise, Freq+Env had a much lower degree of agree-ability with humans despite its better performance on organic drum data, leading us to believe that model accuracy on test data alone cannot be relied upon when the domain of sounds being categorized is switched from organic samples to a virtual synth.
 \\
 With our models showing efficacy at categorizing organic drums vs randomly generated synth sounds, and categorizing organic drums accurately, we combine models in order to increase the efficacy of each phase and address the "open set" problem for our task.
-For phase 1, we only determine sounds as percussive if both FC-DVN and CNN-LSTM have determined it as such with over 90\% confidence.
-For the majority of our random generations, that is not the case, but if a randomly generated sound is passed this phase, our three categorizers assign their categorizations to this sound.
-These categorizers have a moderate degree of agree-ablity, as seen in \ref{survey}, but often there is not a unanimous decision.
+For Phase 1 we only determine sounds as percussive if both FC-DVN and CNN-LSTM have determined it as such with over 90\% confidence.
+For the majority of our random generations that is not the case, but if a randomly generated sound is passed this phase, our three categorizers assign their categorizations to this sound.
+These categorizers have a moderate degree of agree-ability as seen in \ref{survey}, but often there is not an unanimous decision.
 The Fourth method of categorization, "averaged-cat", is implemented by taking the sum of the softmax outputs of all three categorizers and use this sum to determine the category.
 \\
-These models can be combined and weighted in various ways, the confidence thresholds can be modified in order to implement "ears" with different properties.
+These models can be combined and weighted in various ways.
+The confidence thresholds can be modified in order to implement "ears" with different properties.
 A glaring issue in the current implementation is the treatment of softmax outputs as a reasonable measure of a models confidence.
-For various reasons, some models tend to have much higher confidence in their scores, skewing attempts at finding a consensus.
+For various reasons some models tend to have much higher confidence in their scores, skewing attempts at finding a consensus.
 
@@
 %
-\begin{figure}[H]
-\centering
-\includegraphics[width=1\linewidth]{images/random_ranks.png}
-\caption{\colorbox{green!=40}{labels bigger + show other stack sizes} Showing proportions of categorical ranks for around 50,000 randomly generated sounds.
-Only showing ranks 1-5.
-About 90\% received the rank of 1 (blue portion of the bar) for the "synth" category, meaning that the ear correctly gave the highest probability to the sound being from a synth combination.
-We are interested in the small percentages of random generations that trick the ear due to coincidentally being similar to actual drums (i.e those who received a rank of 1) }
-\label{fig:rank portions}
-\end{figure}
-
 \subsection{How Can The Synth and Ear Interact?}
-With our Synth and Ear in place, we can quickly generate programs for our Synth, create the corresponding audio sample and get the scores for the audio sample.
+With our Synth and Ear in place we can quickly generate programs for our Synth, create the corresponding audio sample and get the scores for the audio sample.
 If the ear returns a vector of categorical probabilities, we can assign categorical ranks to the audio sample.
@@
 But how can we use this to create percussion sounds?}\\\\
-We utilize our tools in three different methods of generation, with their specific imlpementation discussed in section \ref{gens}.
+We utilize our tools in three different methods of generation, with their specific implementation discussed in section \ref{gens}.
 \begin {enumerate} [label=(\roman*)]
-\item Random Generation: We randomly create a drum programs until a sound belonging to our category is produced. We hypothesize that due to the speed of our experiments, it is a viable approach.
+\item Random Generation: We randomly create a drum program until a sound belonging to our category is produced. We hypothesize that due to the speed of our experiments it is a viable approach.
 \item Multivariate Distribution Sampling: We attempt to learn the joint distribution of our parameters in order to maximize generation of a certain drum category. 
@@
 \end {enumerate} 
-\todo[inline,color=blue!30]{As seen in Figure \ref{fig:rank portions}, there is a bias in random generation towards making higher ranking hats and kicks and lower ranking shakers, claps.
+\todo[inline,color=blue!30]{As seen in Figure \ref{fig:rank portions}, there is a bias in random generation towards making higher ranking hats and kicks and lower ranking shakers and claps.
 Is this bias because of Synth structure or a problem with the ear?
@@
 \subsection{The Goal}
- Given a category, our aim is to use random generations to guide an algorithm towards novel generation of drums for that category.
-We evaluate each method by measuring how many samples of categories \textit{kick,snare} and \textit{hat} can be produced in under a minute.
-Finally we show results of a survey conducted to measure the quality of these samples.
+ Our goal is to rapidly create high quality, novel drum sounds. In this work we analyze random generations in a build-up towards a guided generation via heuristic search.
 \subsection{General Methods}
 \subsubsection{Random Generation}
-To establish a benchmark, we seek to assess the likelihood of generating samples of each category if we generate programs for various stack sizes by random selection of parameters.
+To establish a benchmark we seek to assess the likelihood of generating samples of each category if we generate programs for various stack sizes by random selection of parameters.
 We have observed a bias in generations as indicated in figure \ref{gens}.\\
-
-% \subsubsection{Multivariate Distribution Sampling}
-% This method is extremely fast and scalable once the parameter space is calculated.
-But success is limited due to well known issues with this approach.
-Notably that the parameter space for virtual synthesizers are often neither differentiable nor Gaussian.
-\cite{esling2019universal} (a couple more papers also talked about this, \colorbox{green!=40}{I have to look them up}).
-Currently our parameters are array indices mapping to different values for Synth components.
-This makes the assumption that our discrete parameter space is normally distributed or differentiable in-appropriate and prone to errors.
-\\
-
 \subsubsection{Evolutionary Search}
@@
 A parameter set is assumed to be an individual with each parameter being its genes.
-To measure an individuals fitness, we use the formula $fitness=score-rank$.
-As generations evolve, a Hall-of-Fame list with a fixed size tracks the best individuals to ever live in any given generation, updating itself after each batch of off-springs is evaluated.\\
-To ensure diversity of the HOF individuals, the fitness score should also consider some measure of uniqueness.
+To measure an individuals fitness we use the formula $fitness=score-rank$.
+As generations evolve, a Hall-of-Fame (HOF) list with a fixed size tracks the best individuals to ever live in any given generation, updating itself after each batch of off-springs is evaluated.\\
+To ensure diversity of the HOF individuals the fitness score should also consider some measure of uniqueness.
 A weighted minkowski distance \footnote{https://docs.scipy.org/doc/scipy/reference/generated/scipy.spatial.distance.minkowski.html} between the genes of an offspring and the HOF individuals may be a good measurement.\\
@@
 \label{survey}
+\begin{figure}[H]
+\centering
+\includegraphics[width=1.1\linewidth]{images/cat.pdf}
+\caption{Frequency of assigned labels for the human categorizers and the average categorizer}
+\label{fig:freq-survey}
+\end{figure}
+
 To measure the quality of the samples produced by our pipeline and the power of our models, we randomly generated around 50-60 samples in the following categories: "snare","kick","hat","clap" and "other" (combination of rims,
-shakers and unusal percussive sounds").
-These samples were determined to be percussive and then categorized by 4 different models (FC,CNNLSTM,E+F and AVG).
+shakers and unusual percussive sounds").
+These samples were determined to be percussive and then categorized by 4 different models (FC, CNNLSTM, E+F and AVG).
 We ensured a balanced division between samples of stack sizes 1,2 and 4 (each stack is responsible for a third samples under each category).

### 2020-01-31 paper.tex
Updates from Overleaf

@@
   \begin{enumerate}
-   \item  $Phase1\,1$: Binary separation of sounds with percussive features from non-percussive sounds.
-   \item $Phae2\,2$: Given confidence that the sound being categorized is percussive, categorizing the type of drum or percussion.
+   \item  $Phase1$: Binary separation of sounds with percussive features from non-percussive sounds.
+   \item $Phae2$: Given confidence that the sound being categorized is percussive, categorizing the type of drum or percussion.
  \end{enumerate}
@@
 This model is trained on spectrum data and reaches 98\% accuracy on our test set for Phase 1.
-\item E+F-DVD: A fully connected model trained on a concatenation of envelope and frequency features for Phase 2. Reaching 80\% accuracy for 6-way drum categorization.
-\item CNN-DVD: A deep CNN model that reaches used for Phase 2. 82\% accuracy in a 6-way drum categorization. Trained on Spectrum features.
-\item FC-DVD: Fully connected 3 layer neural net with 78\% accuracy for 6-way drum categorization. Trained on Spectrum features.
+\item E+F-DVD: A fully connected model trained on a concatenation of envelope and frequency features. Reaching 80\% accuracy for 6-way drum categorization in Phase 2.
+\item CNN-DVD: A deep CNN model trained on Spectrum features. Reaching 82\% accuracy in a 6-way drum categorization in Phase 2. 
+\item FC-DVD: Fully connected 3 layer neural net with 78\% accuracy for 6-way drum categorization in Phase 2. 
 \end{enumerate}
@@
 These categorizers have a moderate degree of agree-ability as seen in \ref{survey}, but often there is not an unanimous decision.
-The Fourth method of categorization, "averaged-cat", is implemented by taking the sum of the softmax outputs of all three categorizers and use this sum to determine the category.
+The fourth method of categorization, "averaged-cat", is implemented by taking the sum of the softmax outputs of all three categorizers and use this sum to determine the category.
 \\
-These models can be combined and weighted in various ways.
-The confidence thresholds can be modified in order to implement "ears" with different properties.
+These models can be combined and weighted in various way and the confidence thresholds can be modified in order to implement "ears" with different properties.
 A glaring issue in the current implementation is the treatment of softmax outputs as a reasonable measure of a models confidence.
@@
 
-% How Can The Synth and Ear Interact?
-%
-\subsection{How Can The Synth and Ear Interact?}
-With our Synth and Ear in place we can quickly generate programs for our Synth, create the corresponding audio sample and get the scores for the audio sample.
-If the ear returns a vector of categorical probabilities, we can assign categorical ranks to the audio sample.
-For example, the category with the highest probability will have the rank of 1, second highest would rank 2nd, and the lowest probability will have the rank of n (assuming n categories).\textbf{
-But how can we use this to create percussion sounds?}\\\\
-We utilize our tools in three different methods of generation, with their specific implementation discussed in section \ref{gens}.
-\begin {enumerate} [label=(\roman*)]
-\item Random Generation: We randomly create a drum program until a sound belonging to our category is produced. We hypothesize that due to the speed of our experiments it is a viable approach.
-\item Multivariate Distribution Sampling: We attempt to learn the joint distribution of our parameters in order to maximize generation of a certain drum category. 
-\item Genetic Search: We treat our parameters as genes and attempt to use evolutionary search algorithms to find programs that the ear deems most fit.\\
-\end {enumerate} 
-\todo[inline,color=blue!30]{As seen in Figure \ref{fig:rank portions}, there is a bias in random generation towards making higher ranking hats and kicks and lower ranking shakers and claps.
-Is this bias because of Synth structure or a problem with the ear?
-Will analyse further after updating ear}
-
 \section{Novel Generations}
 \label{gens}
-\subsection{The Goal}
- Our goal is to rapidly create high quality, novel drum sounds. In this work we analyze random generations in a build-up towards a guided generation via heuristic search.
-\subsection{General Methods}
-\subsubsection{Random Generation}
-To establish a benchmark we seek to assess the likelihood of generating samples of each category if we generate programs for various stack sizes by random selection of parameters.
-We have observed a bias in generations as indicated in figure \ref{gens}.\\
-\subsubsection{Evolutionary Search}
-We implemented evolutionary search using DEAP \citep{DEAP_JMLR2012}.
-A parameter set is assumed to be an individual with each parameter being its genes.
-To measure an individuals fitness we use the formula $fitness=score-rank$.
-As generations evolve, a Hall-of-Fame (HOF) list with a fixed size tracks the best individuals to ever live in any given generation, updating itself after each batch of off-springs is evaluated.\\
-To ensure diversity of the HOF individuals the fitness score should also consider some measure of uniqueness.
-A weighted minkowski distance \footnote{https://docs.scipy.org/doc/scipy/reference/generated/scipy.spatial.distance.minkowski.html} between the genes of an offspring and the HOF individuals may be a good measurement.\\
-A generation of $N$ individuals are initialized randomly.
-To create the offspring generation, each generation goes through mutations and in-place gene crossovers.
-The new generation consists of the top 80\% of the offspring generation and 20\% new individuals to quicken gene diversity.
-If the new individuals are coming directly from previously measured high scoring parameter sets, we ensure that they cannot be directly added to HOF without going through mutations and crossovers first.\\
-\subsubsection{Survey of Generated Drums}
+\subsubsection{The Pipeline}
+ With our Synth and Ear in place we can quickly generate random programs for our Synth, create the corresponding audio sample and get the categorizations for the audio sample.
+We randomly create drum programs and generate the corresponding signal.
+This signal is then fed through $Phase 1$ and $Phase 2$ of our ear model to determine if the signal is percussive.
+If so, a category is assigned to our sound.
+This sound can then be saved as an audio file.
+\\
+ With our current model, a signal iteration of this pipeline will take approximately 50 milliseconds for up to 8 stacks.
+This means around 20 iterations can be done per second using a single process.
+This pipeline scales up efficiently with multiprocessing.
+We have not measured the iteration latency for this pipeline when a GPU is leveraged.
+For reference, our CPU measurements are collected on a 2012 Macbook Air running ubuntu 18.04.\\
+ Before we attempt a guided generation via genetic or other heuristic search methods, we attempt a deep analysis of the randomly generated samples and the corresponding scores given by the ear.
+This analysis can expose weaknesses in our methodology which can be improved for future works where various search methods will be attempted.
+
+ \subsubsection{Survey of Randomly Generated Drums}
 \label{survey}
@@
 \end{figure}
-
-To measure the quality of the samples produced by our pipeline and the power of our models, we randomly generated around 50-60 samples in the following categories: "snare","kick","hat","clap" and "other" (combination of rims,
+To measure the quality of the samples produced by our pipeline and the power of our models, we randomly generated around 50-60 samples in the following categories: "snare", "kick", "hat", "clap" and "other" (combination of rims,
 shakers and unusual percussive sounds").
 These samples were determined to be percussive and then categorized by 4 different models (FC, CNNLSTM, E+F and AVG).
-We ensured a balanced division between samples of stack sizes 1,2 and 4 (each stack is responsible for a third samples under each category).
+We ensured a balanced division between samples of stack size 1, 2 and 4 (each stack is responsible for a third of the samples under each category).
 Both writers then categorized these samples without knowledge of other categorizations (human or computation models).
@@
 \begin{itemize}
-    \item Humans had an additional category of "bad" for samples that they deemed not percussive. The "bad" category indicates that the sample should have been skipped in phase 1. 
-    \item With 6 categorization groups, human's had the same categorization in 47\% of cases
+    \item Humans had an additional category of "bad" for samples that they deemed not percussive. The "bad" category indicates that the sample should have been skipped in Phase 1. 
+    \item With 6 categorization groups, humans had the same categorization in 47\% of cases.
     \item The agreement between the humans and AVG was 44\% and 47\%, not significantly lower than agreement with each other. 
-    \item Of 257 samples, both humans agreed with FC, CNNLSTM, AVG and E+F respectively in 78, 76, 76 and 46 of cases.
+    \item Of 257 samples humans agreed with FC, CNNLSTM, AVG and E+F respectively in 78, 76, 76 and 46 of cases.
 \end{itemize}
@@
 Our kappa measurements \ref{kappa_table} lie within the 3.5-4.5 range, indicating mild to moderate agreement between humans and machines.
-We again measure this coefficient after dropping samples that were categorized as "bad" by the authors, as samples that humans deem to be "bad" indicate a failure in phase 1 and arguably should not have been categorized by the models at all.
-Dropping of samples that both authors deemed "bad" causes 8\% reduction of our data (21 samples) and a small increase in kappa score.
+We again measure this coefficient after dropping samples that were categorized as "bad" by the authors, as samples that humans deem to be "bad" indicate a failure in Phase 1 and arguably should not have been categorized by the models at all.
+Dropping of samples that both authors deemed "bad" causes an 8\% reduction of our data (21 samples) and a small increase in kappa score.
 Dropping samples either reviewer deemed bad resulted in a 30\% reduction of samples and relatively large increase in kappa scores.
@@
     \item Neural nets are function approximators. You don't need them if the actual function is understandable and simple...(but is our task simple enough? how do I prove it?)
-    \item When possible, using DSP methods instead of NNs is preferable in many ways(speed,computation,hardware requirements).\\
+    \item When possible, using DSP methods instead of NNs is preferable in many ways (speed, computation, hardware requirements).\\
     \colorbox{green!=30}{Include some speed measurements in appendix?}
@@
 \section{Ethical Standards}
-We affirm that our work follows the principles of ethical and professional conduct. No drums were harmed in the making of this paper.
+We affirm that our work follows the highest principles of ethical and professional conduct. No drums were harmed in the writing of this paper.
 \bibliographystyle{abbrv}

### 2020-01-31 paper.tex
Updates from Overleaf

@@
 \section{Introduction}
-\subsection{Terminology}
-\todo[inline,color=green!30]{I'd like to define terms such as VSTs, audio effects, Synthesizers, paramters and presets here.
-I throw these terms around a lot and I think some might be confused by their meaning.
-Is this the appropriate place for that?
-I'd like the reader to know these definitions before reading the intro.
-I can try to keep it brief and engaging}
+
 \subsection{Background and Motivation}
@@
 In many cases VST plug-in vendors or unaffiliated enthusiasts sell additional presets for these plugins, targeted towards producers who do not have the time or interest in creating their own.
-Producers may further modify these presets until their desired sound is reached.\\
+The flexibility of the VST technology allows producers to further modify these presets until their desired sound is reached.\\
 Our work is motivated by the idea of finding new, convenient methods for the expansion of a music producer's library of sounds.
-Primarily with generation of novel, one-shot audio samples but also with automated search and creation of presets for virtual synthesizers that a producer might find  interesting.
-Using the generation of short, percussive audio samples as a starting point this project is a proof of concept for promising avenues towards our motivational goal.\\
+Primarily with generation of novel, one-shot audio samples but also with automated search and creation of presets for virtual synthesizers.
+Using the generation of short, percussive audio samples as a starting point, this project is a proof of concept for a promising avenue towards our motivational goal.\\
 
 \subsection{Methodology}
-Towards our goal of generating original audio, we found the proper implementation of 2 major components to be crucial:
+Our attempt is centered around a generateive pipeline of audio.
+We want random noises to be created by a tractable source, we also want to evaluate these sounds so we can guide the random noise generator towards desired sounds.
+Following this idea, we found the proper implementation of 2 major components to be crucial:
 \begin{itemize}
     \item \textit{Virtual Synthesizer}: A flexible, deterministic, and tractable generator which can create audio. 
-The core of our implementation made use of pippi, \footnote{https://github.com/luvsound/pippi} a fast, offline focused python DSP library with a C backend.
+    % The core of our implementation made use of pippi, \footnote{https://github.com/luvsound/pippi} a fast, offline focused python DSP library with a C backend.
 We additionally used the scipy\cite{jones2001scipy} library a few audio effects that we found lacking in pippi.
     \item \textit{Virtual Ear}: An ear that returns an evaluation of an audio sample; estimating the effectiveness of an audio sample's fulfillment of a producers requirements.
-The ear's evaluation guides the generation process towards a desired path, making the implementation and training of the ear crucial to the sounds which are generated.
-A particularly effective implementation was done by using a labeled set of percussive and non-percussive audio files to train a custom model (combination of a simple Convolutional Neural Net (CNN) and a custom envelope estimation algorithm), giving us a "virtual drum detector ear".
-\\
+The ear's evaluation guides the generation process towards a desired path, making it a crucial component of our pipeline.
 \end{itemize}
 Our components are designed with modularity and parallelizability in mind.
-This allows each component to be debugged, modified, and improved without requiring modifications in other components; additionally increasing the scalability and speed of experiments.
+This allows each component to be debugged, modified, and improved without requiring modifications in other components while additionally increasing the scalability and speed of experiments.
 Section \ref{impl} contains further discussion of the components as well as the code that glues the project together.\\ 
-While the main focus of this project is the generation of novel percussive sounds our methodology indicates promising results with regards to creation of new presets for any virtual synth without the need for a-priori knowledge of the functions or its parameters (i.e the effect of parameter modulation on the sonic output).
-We also demonstrate the viability of a few lesser explored avenues for the purposes of audio synthesis and Music Information Retrieval (MIR), notably:
-\begin{enumerate}[label=\roman*]
-\item Heuristic search methods for the creation of new presets for virtual synthesizers.
-More concretely, we observed that given a virtual ear which could reliably score pieces of audio based on its resemblance to a desired category (e.g: kicks, snares, piano) we were able to rapidly search the parameters of a virtual synthesizer and create numerous parameter-sets (i.e presets) which resemble our desired category of sounds.
-\item The viability of virtual synthesizers based on Digital Signal Processing (DSP) methods for fast, unsupervised creation of novel audio, discussed in more detail in section \ref{related}. \\
-\end{enumerate}
-
+While the main focus of this project is the generation of novel percussive sounds, our methodology indicates promising results with regards to creation of new presets for any virtual synth without the need for a-priori knowledge of the functions or its parameters (i.e the effect of parameter modulation on the sonic output).
+We also demonstrate the viability of a virtual synthesizers based on Digital Signal Processing (DSP) methods for fast, unsupervised creation of novel audio, discussed in more detail in section \ref{related}.
+\\
 \subsection{Related Work and Contradistinctions}
@@
 Numerous deep, neural network models have been proposed and utilized for the purpose of signal generation in recent years.
-WaveGans and WaveNet have been subject to significant improvements and experiments since their proposal \colorbox{green!=40}{\cite{nsynth2017} + Many more references to be added.} Even more recently Variational AutoEncoders (VAE's) have been utilized for generation of short percussive samples \cite{aouameur2019neural,ramires2019timbfeat}.
+WaveGans and WaveNet have been subject to significant improvements and experiments since their proposal \cite{nsynth2017,yamamoto2019parallel,oord2017parallel}.
+Even more recently Variational AutoEncoders (VAE's) have been utilized for generation of short percussive samples \cite{aouameur2019neural,ramires2019timbfeat}.
 In this work however, we opt to use digital signal processing methods to create a virtual synthesizer for the generation of audio signals as it provides several unique advantages:
@@
 Therefore we can safely assume that most producers would prefer their audio samples to have sampling rates of 44.1 khz or higher.
+In this work, we fix our sampling rate to the 48 khz standard.
   \item Neural networks are often viewed as unexplainable black box solutions.
@@
 More recent work by Yee-King et al.
-\cite{yee2018automatic} used LSTM and genetic algorithms to find the exact parameters used to create a group of sounds.
+\cite{yee2018automatic} used Long short-Term Memory (LSTM) models and genetic algorithms to find the exact parameters used to create a group of sounds.
 The sounds approximated were made by the same virtual synthesizer, not an external source; making the eventual replication certain even with random search.
@@
 used a large dataset of over 10,000 presets for a commercial VST synthesizer to learn a latent parameter space which can be sampled for creation of new audio \cite{esling2019universal}.
-As stated before, our work presents a rapid approximation of percussion sounds with no previous knowledge about the sonic capabilities of our virtual synthesizer, exploring the actual parameter space rather than its latent representation.
+As stated before, our work explores the rapid approximation of percussion sounds with no previous knowledge about the sonic capabilities of our virtual synthesizer, exploring the actual parameter space rather than its latent representation.
 
@@
 \label{data}
-Our data is a large set of drum samples aggregated from personal libraries, free drum kits from sampleswap \footnote{https://sampleswap.org/} which we further processed to suit our categories, and a large set of drum sounds aggregated from royalty free sources such as musicradar \footnote{https://www.musicradar.com/}.
+Our data is a large set of drum samples aggregated from personal libraries, free drum kits from the sample-swap project \footnote{https://sampleswap.org/} which we further processed to suit our categories, and a large set of drum sounds aggregated from royalty free sources such as musicradar \footnote{https://www.musicradar.com/}.
 We will make our dataset of free-drum sounds available for download.
@@
 \item Of the 6000 drum-sounds utilized in our work, the kick, snare and hat categories have the largest share at around 20\% each, while the shaker and rim (other) categories have the smallest at 5\% combined.
-Due to this we only focused on learning from kicks, snares, toms, claps and hats for Phase 1 of training \ref{sec:ear}.
+Due to this we only focused on learning from kicks, snares, toms, claps and hats for Phase 1 of training (along with non-percussive groups of sound) \ref{sec:ear}.
 \item For Phase 2 of training we only focused on categorizing snares, claps, kicks, hats and other (percussive sounds such as shakers, rims and unusual percussions that we couldn't categorize were grouped into this category).
-\item In order to offset bias from data imbalance during training of our models, the categorical cross entropy loss was weighted by the category sizes. 
+Non-percussive datasets were not used for this phase.
+\item In order to offset bias from data imbalance during training of our models, the categorical cross entropy loss was weighted by the group sizes. 
 \item For training any given model, 80\% of our data is used for training the models and 20\% is used for testing. 
@@
 In our implementation a synthesizer can have any number of sub-modules.
-The parameters that deterministically dictate the output signal of the sub-module as well as the range of values each parameter can take are shown in table 1 \ref{table:1}.
+The parameters that deterministically dictate the output signal of the sub-module as well as the range of values each parameter can take are shown in table \ref{table:1}.
 We call this number the \textit{stack size}.
@@
 \centering
-
 \begin{subfigure}[b]{\linewidth}
@@
 \subsubsection{Feature Extraction}
-What we refer to as an "ear" is any method of evaluating a piece of audio and capable of "listening" to a piece of audio and giving it a score (or a list of scores) based on how well it satisfies certain criteria.
-Since in this work we are mainly focused on percussive generation what we require from the ear is to give us probabilities of an audio sample belonging to various categories.
+What we refer to as an "ear" is any method of evaluating a piece of audio, capable of "listening" to a piece of audio and giving it a score (or a list of scores) based on how well it satisfies certain criteria.
+Since in this work we are mainly focused on percussive generation, what we require from the ear is to give us probabilities of an audio sample belonging to various categories.
 As our synthesizer outputs are deterministic for all programs the ear's evaluations would allow us to associate the categorical probabilities of each sound with the program that generated it.
@@
 We ensured a balanced division between samples of stack size 1, 2 and 4 (each stack is responsible for a third of the samples under each category).
-Both writers then categorized these samples without knowledge of other categorizations (human or computation models).
+Both reviewers then categorized these samples without knowledge of other categorizations (human or computation models).
 It's important to note that:
@@
     \item Our methodology was successful in generating novel examples of some percussion categories.
-    \item Reiterate the importance of ear.
+    \item Implementation of an ear that can distinguish sounds from closed sets (kick drums, snare drums etc)
+    \item Our generation is not bullet-proof. Based on our human survay many of the samples generated in our pipeline are non-percussive. 
     \item There are potential benefits (e.g: pedagogical, software engineering, efficiency, data search, generality of solution, etc.) to separate some audio generation tasks into multiple parts, rather than throwing everything at some neural net.

### 2020-02-03 paper.tex
Updates from Overleaf

@@
 \usepackage{subcaption}
-
+\setlength{\bibsep}{0pt plus 0.3ex}
+\usepackage{balance}
 \begin{document}
@@
 We present our findings and measurements of the various approaches taken towards the implementation of the virtual ear, virtual synthesizer, and generative pipeline; hoping to expose the advantages and shortcomings of the employed methodologies and their practicality in future works via a clear demonstration of their capabilities relative to our stated goal.
-We also discuss and share our curated dataset of sounds along with our codebase \footnote{\url{https://github.com/imilas/Synths_Stacks_Search}} which can be used for its further expansion.
+We also discuss and share our curated dataset of sounds along with our codebase \footnote{\url{redacted}} which can be used for its further expansion.
 
@@
 \ccsdesc[500]{Information systems~Music retrieval}
+\ccsdesc[500]{Applied computing~Performing arts}
 \printccsdesc
@@
 
-\subsection{Background and Motivation}
+%\subsection{Background and Motivation}
 The rise of Digital Audio Workstations (DAW) \cite{leider2004digital} and Virtual Studio Technology (VST) based plug-ins \cite{tanev2013virtual} have rapidly transformed the sonic and material landscape of music production in the recent years.
@@
 In many cases VST plug-in vendors or unaffiliated enthusiasts sell additional presets for these plugins, targeted towards producers who do not have the time or interest in creating their own.
-The flexibility of the VST technology allows producers to further modify these presets until their desired sound is reached.\\
+The flexibility of the VST technology allows producers to further modify these presets until their desired sound is reached.
+
+We want to leverage AI technologies, such as heuristic search and random search, to produce new drum samples, by finding synthesizers and their appropriate configurations that can produce various kinds of drum samples.
+Effectively we will combine machine listening and code generation of synthesizers to find drum samples.
+
 Our work is motivated by the idea of finding new, convenient methods for the expansion of a music producer's library of sounds.
 Primarily with generation of novel, one-shot audio samples but also with automated search and creation of presets for virtual synthesizers.
-Using the generation of short, percussive audio samples as a starting point, this project is a proof of concept for a promising avenue towards our motivational goal.\\
+Using the generation of short, percussive audio samples as a starting point, this project is a proof of concept for a promising avenue towards our motivational goal.
 
 \subsection{Methodology}
-Our attempt is centered around a generateive pipeline of audio.
-We want random noises to be created by a tractable source, we also want to evaluate these sounds so we can guide the random noise generator towards desired sounds.
+Our attempt is centered around a generative pipeline of audio.
+We want random sounds to be created by a tractable source, we also want to evaluate these sounds so we can guide the random sounds generator towards desired sounds.
+Instead of learning weights and parameters in an audio-generating neural network, we wish to generate, search, and tune synthesizers to produce percussion sounds.
 Following this idea, we found the proper implementation of 2 major components to be crucial:
+
 \begin{itemize}
-    \item \textit{Virtual Synthesizer}: A flexible, deterministic, and tractable generator which can create audio. 
+    \item \textit{Virtual Synthesizer}: A flexible, deter\-min\-istic, and tract\-able gener\-ator which can create audio. 
     % The core of our implementation made use of pippi, \footnote{https://github.com/luvsound/pippi} a fast, offline focused python DSP library with a C backend.
@@
 \end{itemize}
+
+% AH: Optional. Can be removed or reduced later
 Our components are designed with modularity and parallelizability in mind.
 This allows each component to be debugged, modified, and improved without requiring modifications in other components while additionally increasing the scalability and speed of experiments.
-Section \ref{impl} contains further discussion of the components as well as the code that glues the project together.\\ 
+Section \ref{impl} contains further discussion of the components as well as the code that glues the project together.
+
 While the main focus of this project is the generation of novel percussive sounds, our methodology indicates promising results with regards to creation of new presets for any virtual synth without the need for a-priori knowledge of the functions or its parameters (i.e the effect of parameter modulation on the sonic output).
 We also demonstrate the viability of a virtual synthesizers based on Digital Signal Processing (DSP) methods for fast, unsupervised creation of novel audio, discussed in more detail in section \ref{related}.
-\\
+
 \subsection{Related Work and Contradistinctions}
@@
 The sounds approximated were made by the same virtual synthesizer, not an external source; making the eventual replication certain even with random search.
-Since this work more focused on pads and textures rather than drums, feature matching in this also appears to not be concerned with the envelope of the sounds but rather the frequency content within arbitrary time windows.
+Since this work appears more focused on pads and textures rather than drums, feature matching appears to not be concerned with the envelope of the sounds but rather the frequency content within arbitrary time windows.
 Yet another recent, impressive work by Esling et al.
@@
 The scripts used to download and process royalty free samples will also be made available.
-Further information about downloading our dataset can be found on the project's github page.
-\\
+Further information about downloading our dataset can be found on this project's github page.
+Current URLs are redacted for double-blind purposes.
+
 Our drum categories are claps, hats, kicks, rims/other, shakers, snares, mid-toms and high-toms.
-Other categories are chopped guitars, chopped pianos and stacks (randomly generated synth noise), utilized for learning percussive vs not-percussive sounds.
+Other categories are chopped guitars, chopped pianos and n-stack-synths (random noise generated by the virtual synth with stack size of n, see \ref{vs}), utilized for learning percussive vs non-percussive sounds.
+Stack sizes refers to how many synth functions are connected together in a synthesizer.
 Some notes about our dataset:
+
 \begin{itemize}
@@
 \item In order to offset bias from data imbalance during training of our models, the categorical cross entropy loss was weighted by the group sizes. 
-\item For training any given model, 80\% of our data is used for training the models and 20\% is used for testing. 
-\item We limit the size of the stack category to 50\% of the total size of our drum dataset.
-This is done in order to measure whether the features extracted can address the "Open Set Recognition" problem, which will be discussed further in section \ref{sec:ear}.
+\item For any given model, 80\% of our data is used for training and 20\% is used for testing.
+
+\item We limit the size of the n-stack-synths category to 50\% of the total size of our drum dataset.
+This is done in order to measure whether the features extracted can address the "Open Set Recognition" problem, which will be discussed further in Section \ref{sec:ear}.
 \end{itemize}
@@
 \label{impl}
+
 \subsection{Virtual Synthesizer}
+\label{vs}
 We used the python based Pippi library for sound generation\footnote{https://github.com/luvsound/pippi}.
@@
 For the range of parameters each sub-module can take we call the sets of parameters that characterize a synth's sub-modules a \textit{program} (analogous to a preset).
-Each sub-module can make an audio signal with the length of 0.1-1 second.
-If a Synth has a stack size of more than 1 these audio signals are overlapped and the total amplitude is normalized.\\
+Each sub-module can make an audio signal with the length of
+% AH: Be consistent about synth, synthesizer, virtual synthesizer, Synth
+0.1-1 second. If the synthesizer has a stack size of more than 1 these audio signals are overlapped and the total amplitude is normalized.
+
 \begin{table}[h!]
@@
 \includegraphics[width=1\linewidth]{images/ff1.pdf}
-\caption{Organic hat sample}\label{fig:64stack}
+\caption{Recorded hat sample}\label{fig:64stack}
 \setcounter{subfigure}{1}%
@@
 \caption{Graphed representation of features extracted for 3 different samples.
-Sample $a$ is an organic hat from our database.
+Sample $a$ is a recorded hat from our database.
 sample $b$ is an example of randomly generated noise with percussive qualities that we found suitably similar to a snare sound.
@@
 \subsubsection{Feature Extraction}
-What we refer to as an "ear" is any method of evaluating a piece of audio, capable of "listening" to a piece of audio and giving it a score (or a list of scores) based on how well it satisfies certain criteria.
+What we refer to as an "ear" is any method (such as machine listening) of evaluating a piece of audio, capable of "listening" to a piece of audio and giving it a score (or a list of scores) based on how well it satisfies certain criteria.
 Since in this work we are mainly focused on percussive generation, what we require from the ear is to give us probabilities of an audio sample belonging to various categories.
 As our synthesizer outputs are deterministic for all programs the ear's evaluations would allow us to associate the categorical probabilities of each sound with the program that generated it.
-In section \ref{gens} we discuss how these scores were used for navigation of our synthesis towards parameters which give us the desired sonic output.\\
+In section \ref{gens} we discuss how these scores were used for navigation of our synthesis towards parameters which give us the desired sonic output.
+
  With our dataset \ref{data} of labeled drum sounds we can confidently categorized unlabeled drum sounds given that we know they are drum sounds.
 However, a major hurdle towards the implementation of a "drum from non-drum" recognizing ear is that the set of sounds that are not percussive is infinite.
-Since we can represent different drum groups using our categorized data (closed set), but effective aggregation and feature extraction of non-drum sound data is not practical.
-We hypothesize that $Task\,1$ falls within the domain of "Open Set Recognition"\cite{scheirer2012toward}.
-"Open Set Recognition" problem arises when a set that is being categorized has practically infinite diversity, often making learning-by-example impossible without further domain knowledge.
-While ML techniques can be effective with classification of a closed set of examples, the classification of an infinite set cannot be reliably achieved with current ML methodologies\cite{geng2018recent,mundt2019open}.
-\\
-  In our case, as discussed in section \ref{survey}, the majority of sounds generated by the synth do not resemble percussion.
-Even if we only consider 1 second long sounds made with a single stacked synth, the set of synthesizer parameters (and we assume, the sound generated by these parameters) is extremely large.
-In our case, we determined that there are 2 steps necessary to effectively extract percussive sounds from the randomly generated noise from the virtual synthesizer:
+ % AH: Simplify the sentence. VVVV
+In our case, drum groups are an example of closed sets, since sufficiently large sample pack can effectively describe drum categories.
+However, effective representation of non-drum data is not practical.
+We hypothesize that the implementation of our virtual ear falls within the domain of "Open Set Recognition"\cite{scheirer2012toward}.
+The problem arises when a set that is being categorized has practically infinite diversity,making learning-by-example difficult without further domain knowledge.
+methodologies\cite{geng2018recent,mundt2019open}.
+
+   % AH: is the virtual synthesizer a synth or a synthesizer that makes synthesizer
+  % AH: you should make it 1 instance of a generated synth 
+  In our case, as discussed in Section \ref{survey}, the majority of sounds generated by the synth do not resemble percussion.
+Even if we only consider 1 second long sounds made with a single stacked synth, the set of synthesizer parameters (and we assume, the sound generated by the synth given these parameters) is extremely large.
+In our case, we determined that there are 2 steps necessary to effectively extract percussive sounds
+  from the randomly generated sounds produced by virtual synthesizers: 
   \begin{enumerate}
-   \item  $Phase1$: Binary separation of sounds with percussive features from non-percussive sounds.
-   \item $Phae2$: Given confidence that the sound being categorized is percussive, categorizing the type of drum or percussion.
+   \item  Phase $1$: Binary separation of sounds with percussive features from non-percussive sounds.
+   \item Phase $2$: Given confidence that the sound being categorized is percussive, categorizing its type.
  \end{enumerate}
-We are interested in extracting generalized features that can be applied in other audio domains.
+We are interested in extracting generalizable, domain agnostic features.
 In this work we rely entirely on Fast Fourier Transform (FFT) and by extension Short-time Fourier Transforms (STFT) for feature extraction.
-Using FFT a signal can be represented by a vector with each index corresponding to a frequency-bin (a range of frequencies too close to be distinguishable) and the value at each index corresponding to the combined-magnitude of the frequencies within the bin.
+Using FFT, a signal can be represented by a vector with each index corresponding to a frequency-bin (a range of frequencies too close to be distinguishable) and the value at each index corresponding to the combined-magnitude of the frequencies within the bin.
 STFT can be employed when a more accurate representation is desired; via the application of the FFT to a sliding time-window on the signal to create a matrix (a list of vectors).
-This matrix can effectively represent the frequencies present in the signal at each time step, given the right window-length and hop-size (how much the window is shifted at each time-step).\\
+This matrix can effectively represent the frequencies present in the signal at each time step, given the right window-length and hop-size (how much the window is shifted at each time-step).
+
+% AH: If you need space shorten this paragraph to we use STFT which has worked in past and we use spectral-cenbtroids and zero-crossings
 Various works have demonstrated effective reconstruction of signals given their STFT \cite{nawab1983signal,griffin1984signal}.
-The loss of phase information may be an issue in some domains \cite{sturmel2011signal}, however, phase information has little impact on the human auditory experience.
-If the original signal can be otherwise accurately reconstructed from its STFT, perhaps further transformation and analysis of the STFT may be relied on as source of fundamental features necessary for audible signal categorization.
-Following this and in the interest of keeping the feature space small and fundamental, other methods of feature extraction which have proven effective at instrument and percussion categorization such as Spectral-Centroids \cite{schubert2004spectral} and Zero-Crossing Rates \cite{gouyon2000use} are not utilized.\\
+For our purpose, if the original signal can be faithfully reconstructed from its STFT, analysis of the STFT may be relied on as source of fundamental features necessary for audible signal categorization.
+In the interest of keeping the feature space small and fundamental, other methods of feature extraction such as Spectral-Centroids \cite{schubert2004spectral} and Zero-Crossing Rates \cite{gouyon2000use} are not utilized.
+
 Using only the STFT of signals as source of feature extraction we defined 3 transformation functions which we believe to capture important, unique attributes of percussive sounds.
-These functions were applied at training time to 1 second audio samples before being sent to a classifier.
+These functions were applied at training time to 1 second audio samples before being sent to a classifier; transforming a signal into a set of features which we hope can capture the necessary information for our categorization task.
+
 \begin{enumerate}
@@
 \end{enumerate}
+
 \subsubsection{The Models}
-Using the described features, we trained several models for Phase 1 and 2.
-These include Fully-Connected (FC) models, Convolutional Neural Nets (CNNs) and CNN + Long Term Short Memory models (CNNLSTM).
+Using the described features, we trained several neural network models for Phase 1 and 2 in the Pytorch environment.
 The task of Phase 1 is to separate drums from not-drums (DrumVsNotDrum, or DVN).
 The task of Phase 2 is to categorize drums and percussion (DrumVsDrum, or DVD).
-We kept our feature space small, making it viable to for the task of designing models and picking the right features being done on a trial and error basis.
-A summary of models utilized in our pipeline is given below:
+We kept our feature space small, making it viable for feature selection and model design to be done on a trial and error basis.
+For all models, accuracy is calculated by prediction of all test dataset labels and the loss function and optimizer are Categorical-CrossEntropy and Adam respectively.
+Training continues until no reduction in loss and accuracy is observed in 10 epochs.
+All activation functions are PReLU:
 \begin {enumerate}
-\item FC-DVN: A small fully connected network trained on Envelope features, reaching 97\% accuracy on our test data for Phase 1. 
+\item FC-DVN: Fully connected network trained on Envelope features, reaching 97\% accuracy on our test data for Phase 1. With size of 10x5x10.
 \item CNNLSTM-DVN: A combination of CNN and LSTM models, where the CNN model extracts higher level features that are fed temporally to an LSTM cell.
-This model is trained on spectrum data and reaches 98\% accuracy on our test set for Phase 1.
-\item E+F-DVD: A fully connected model trained on a concatenation of envelope and frequency features. Reaching 80\% accuracy for 6-way drum categorization in Phase 2.
-\item CNN-DVD: A deep CNN model trained on Spectrum features. Reaching 82\% accuracy in a 6-way drum categorization in Phase 2. 
-\item FC-DVD: Fully connected 3 layer neural net with 78\% accuracy for 6-way drum categorization in Phase 2. 
+This model is trained on spectrum data and reaches 98\% accuracy on our test set.
+Its structure is the combination of a CNN with 2 output channels and kernel size $(7,3)$; Followed by an LSTM model of hidden size 800 and a fully connected layer of size 20x2.
+\item E+F-DVD: A fully connected model trained on a concatenation of envelope and frequency features. Reaching 80\% accuracy for 6-way drum categorization in Phase 2. Size of 50x10x2x6.
+\item CNN-DVD: A CNN model trained on Spectrum features.
+Reaching 82\% accuracy in a 6-way drum categorization in Phase 2.
+A combination of a CNN model with output channel size of 4, kernel of size of 5, another CNN model with output channel size of 8 and kernel of size 3.
+Followed by a fully connected network of shape 100x20x6.
+\item FC-DVD: Fully connected 3 layer neural net with 78\% accuracy for 6-way drum categorization in Phase 2. Size of 400x200x50.
 \end{enumerate}
-The number of parameters for these models were picked rather arbitrarily.
-We'd like to note that based on our anecdotal observations the minor modifications in features played a much more significant role in the model accuracy than major parameter changes.
-Also as discussed in section \ref{survey}, despite it's marginally lower accuracy rate, the FC-DVD model has a slight but noticeable advantage in regards to matching human categorization of data.
-Likewise, Freq+Env had a much lower degree of agree-ability with humans despite its better performance on organic drum data, leading us to believe that model accuracy on test data alone cannot be relied upon when the domain of sounds being categorized is switched from organic samples to a virtual synth.
-\\
-With our models showing efficacy at categorizing organic drums vs randomly generated synth sounds, and categorizing organic drums accurately, we combine models in order to increase the efficacy of each phase and address the "open set" problem for our task.
+The parameters are hand-picked and un-tuned.
+As discussed in section \ref{survey}, higher accuracy rates in these models do not translate to higher agreeableness with humans.
+leading us to believe that model accuracy on test data alone cannot be relied upon when the domain of sounds
+being categorized is switched from original percussion samples to virtual synth sounds.
+
+With our models showing high accuracy on testing data, we combine models in order to increase the efficacy of each phase and address the "open set problem" for our task.
 For Phase 1 we only determine sounds as percussive if both FC-DVN and CNN-LSTM have determined it as such with over 90\% confidence.
-For the majority of our random generations that is not the case, but if a randomly generated sound is passed this phase, our three categorizers assign their categorizations to this sound.
-These categorizers have a moderate degree of agree-ability as seen in \ref{survey}, but often there is not an unanimous decision.
-The fourth method of categorization, "averaged-cat", is implemented by taking the sum of the softmax outputs of all three categorizers and use this sum to determine the category.
-\\
-These models can be combined and weighted in various way and the confidence thresholds can be modified in order to implement "ears" with different properties.
-A glaring issue in the current implementation is the treatment of softmax outputs as a reasonable measure of a models confidence.
-For various reasons some models tend to have much higher confidence in their scores, skewing attempts at finding a consensus.
+For the majority of our random generations that is not the case, but if a randomly generated sound has passed this phase, our three categorizers assign their categorizations to this sound.
+These categorizers have a moderate degree of agree-ability as seen in \ref{survey}, but often the decision is not unanimous.
+The fourth method of categorization, "averaged-cat", is implemented by taking the sum of the softmax outputs of all three categorizers, using it to determine the category.
+
+These models can be combined and weighted in various ways and the confidence thresholds can be modified in order to implement "virtual ears" with different properties.
+A glaring issue in the current implementation is the treatment of softmax outputs as a reasonable measure of a model's confidence.
+Ignoring that some models may have unwarranted higher confidence in their scores, skewing attempts at finding a consensus.
 
@@
 \label{gens}
-\subsubsection{The Pipeline}
- With our Synth and Ear in place we can quickly generate random programs for our Synth, create the corresponding audio sample and get the categorizations for the audio sample.
-We randomly create drum programs and generate the corresponding signal.
+\subsection{The Pipeline}
+ With our \emph{synth generator} and \emph{virtual ear} in place we can quickly generate random virtual synthesizer programs.
+Once we render the virtual synthesizers with these programs and create the corresponding audio sample, we can categorize the audio sample.
+Simply put, we randomly create drum programs and generate and the corresponding signal.
 This signal is then fed through $Phase 1$ and $Phase 2$ of our ear model to determine if the signal is percussive.
 If so, a category is assigned to our sound.
-This sound can then be saved as an audio file.
-\\
- With our current model, a signal iteration of this pipeline will take approximately 50 milliseconds for up to 8 stacks.
+This sound can then be saved as an audio file, and its virtual synthesizer can also be saved.
+
+ With our current model, a single iteration of this pipeline will take approximately 50 milliseconds for Synthesizers with stack sizes of 8 or less.
 This means around 20 iterations can be done per second using a single process.
@@
 We have not measured the iteration latency for this pipeline when a GPU is leveraged.
-For reference, our CPU measurements are collected on a 2012 Macbook Air running ubuntu 18.04.\\
- Before we attempt a guided generation via genetic or other heuristic search methods, we attempt a deep analysis of the randomly generated samples and the corresponding scores given by the ear.
-This analysis can expose weaknesses in our methodology which can be improved for future works where various search methods will be attempted.
+For reference, our CPU measurements are collected on a 2012 Macbook Air running Ubuntu 18.04.
+ In future work we will attempt guided generation via genetic and other heuristic search methods.
+Here we attempt a deep analysis of the randomly generated samples and the corresponding scores given by the ear.
+This analysis can expose weaknesses in our methodology which can be improved for future works where various search methods will be evaluated.
 
- \subsubsection{Survey of Randomly Generated Drums}
+ \subsection{Survey of Randomly Generated Drums}
 \label{survey}
@@
 Both reviewers then categorized these samples without knowledge of other categorizations (human or computation models).
-It's important to note that:
+It's important to note:
 \begin{itemize}
@@
 \end{itemize}
+
 We assess the reliability of agreement between humans and categorization models via the Fleiss' kappa coefficient \cite{fleiss1971measuring}.
@@
 Dropping of samples that both authors deemed "bad" causes an 8\% reduction of our data (21 samples) and a small increase in kappa score.
-Dropping samples either reviewer deemed bad resulted in a 30\% reduction of samples and relatively large increase in kappa scores.
-\\
-
+Dropping samples deemed bad by either reviewer resulted in a 30\% reduction of samples and relatively large increase in kappa scores.
 Possible takeaways from this survey:
@@
 Survey shows that the scale of agreement within humans as well as between humans and various model combinations is moderate at best, even after removal of "bad" samples.
-While the same models can easily achieve 98+ percent accuracy when tested on organic drum samples.
+While the same models can easily achieve 98+ percent accuracy when tested on recorded drum samples.
 This may be a manifestation of the "open set recognition" problem.
@@
 
-\section{Summary and Conclusions}
+\section{Summary}
+
+\balance
+
+In summary we were capable of generating many new and novel drum samples that were agreed upon by human-raters and machines. Lessons learned included:
 
@@
     \item Our methodology was successful in generating novel examples of some percussion categories.
-    \item Implementation of an ear that can distinguish sounds from closed sets (kick drums, snare drums etc)
-    \item Our generation is not bullet-proof. Based on our human survay many of the samples generated in our pipeline are non-percussive. 
-    \item There are potential benefits (e.g: pedagogical, software engineering, efficiency, data search, generality of solution, etc.) to separate some audio generation tasks into multiple parts, rather than throwing everything at some neural net.
-    \item With the right implementation of DSP methods to create a synth, Genetic search (viewed as too slow by previous work) is viable for finding desired programs and parameters.
-    \item Neural nets are function approximators. You don't need them if the actual function is understandable and simple...(but is our task simple enough? how do I prove it?)
-    \item When possible, using DSP methods instead of NNs is preferable in many ways (speed, computation, hardware requirements).\\
-    \colorbox{green!=30}{Include some speed measurements in appendix?}
-    \item ...
-\end{itemize}
-\section{Future Work}
-\begin{itemize}
-    \item Potential for other generative methods (e.g reinforcement learning)
-    \item Making the synth's sound range more diverse while maintaining speed and efficiency
-    \item Can our approach be used for VSTs?
+    \item Generating virtual synthesizers allows for the fast generation and evaluation of audio created from a complex synth.
+Our implementation enables classification of the virtual synthesizer and sounds into percussive categories, enabling not only the creation of new libraries of percussion sounds, but new libraries of percussion synthesizers.
+    \item Despite our careful feature extraction and training, our generative pipe-line is not bullet-proof. Based on our human survey many of the samples generated in our pipeline are non-percussive.
+    \item Implementation of an virtual ear that can distinguish sounds from closed sets (kick drums, snare drums etc) from an infinitely large set (non-percussive sounds) is difficult. 
 \end{itemize}
 
+Based on our observations, the biggest hurdle towards generation of novel percussive sounds is an ear that can distinguish non-percussive sounds from percussive sounds.
+
+\subsection{Future Work}
+
+In future work, we will continue our attempt at effective, domain agnostic separation of noise from drums.
+Our focus will be on extraction of generalizable features which can help us with classification problems regardless of the audio domain i.e source of audio.
+
+We will seek solutions from the state of the art methods in regards to open set recognition.
+We plan to utilize genetic search and other heuristic methods for guided generation of sound rather than random search applied to a heuristic.
+We will also introduce new features into our virtual synthesizer to add diversity to generated samples.
+
 \section{Ethical Standards}
-We affirm that our work follows the highest principles of ethical and professional conduct. No drums were harmed in the writing of this paper.
+This work was funded by ------ (redacted for double blind).
+There are no conflicts of interest.
+All human-raters were informed and consenting authors of this paper.
+No animals were involved in this research.
+No drums were harmed in the writing of this paper.
 \bibliographystyle{abbrv}
